% chktex-file 35
% Chapter Template

% Main chapter title
% Change X to a consecutive number; for referencing 
% this chapter elsewhere, use~\ref{ChapterX}
\chapter{Preliminaries}\label{ChapterPreliminaries} 

% Change X to a consecutive number; this is for the header 
% on each page - perhaps a shortened title
\lhead{Chapter 1. \emph{Preliminaries}} 

In what follows, we present some parts in parallel fashion by listing the
respective options in order, enclosed and separate like this:
$\langle$~$\ldots$ / $\ldots$~$\rangle$. For example: a real number $x$ is
$\langle$~positive / non-negative~$\rangle$ if $\langle$~$x>0$ / $x\geq
0$~$\rangle$. Sometimes one of the parts might be empty. We use symbol $:=$ for
equality by definition.

We use the following standard notation for some commonly used sets of numbers:
$\mathbb{C}$ denotes the complex numbers, $\mathbb{R}$ denotes the real numbers,
$\mathbb{Z}$ denotes the integers, $\mathbb{N}$ denotes the natural numbers,
$\mathbb{N}_n$ denotes the set of first $n$ natural numbers, $\mathbb{R}_+$
denotes the set of non-negative real numbers, $\mathbb{T}$ denotes the set of
complex numbers of modulus $1$, finally, $\mathbb{D}$ denotes the set of complex
numbers with modulus less than $1$. For $z\in\mathbb{C}$ the symbol
$\overline{z}$ stands for the complex conjugate number.

For a given map $f:M\to M'$ and subset $\langle$~$N\subset M$ / $N'\subset M'$
such that $\operatorname{Im}(f)\subset N'$~$\rangle$ by $\langle$~$f|_N$ /
$f|^{N'}$~$\rangle$ we denote the  $\langle$~restriction of $f$ onto $N$ /
corestriction of $f$ onto $N'$~$\rangle$, that is $\langle$~$f|_N:N\to
M',\,x\mapsto f(x)$ / $f|^{N'}:M\to N',\, x\mapsto f(x)$~$\rangle$. The indicator
function of a subset $N$ of the set $M$ is denoted by $\chi_{N}$, so that
$\chi_N(x)=1$ for $x\in N$ and $\chi_N(x)=0$ for $x\in M\setminus N$. We also
use the shortcut $\delta_x=\chi_{ \{x \}}$ where $x\in M$. By $\mathcal{P}(M)$
we denote the set of all subsets of $M$, and $\mathcal{P}_{f}(M)$ stands for the
set of all finite subsets of $M$. The symbol $M^N$ stands for the set of all
functions from $N$ to $M$. By $\operatorname{Card}(M)$ we denote the cardinality
of $M$. By $\aleph_0$ we denote the cardinality of $\mathbb{N}$.

%-------------------------------------------------------------------------------
%    Broad foundations
%-------------------------------------------------------------------------------

\section{
  Broad foundations}\label{SectionBroadFoundations} 

%-------------------------------------------------------------------------------
%    Categorical language
%-------------------------------------------------------------------------------

\subsection{
  Categorical language}\label{SubSectionCategoricalLanguage}

Here we recall some basic facts and definitions from category theory and fix
notation we shall use. We assume that our reader is familiar with such basics of
category theory as category, functor, morphism. Otherwise, see
[\cite{HelLectAndExOnFuncAn}, chapter 0] for a quick introduction or
[\cite{KashivShapCatsAndSheavs}, chapter 1] for more details.

For a given category $\mathbf{C}$ by $\operatorname{Ob}(\mathbf{C})$ we denote
the class of its objects. The symbol $\mathbf{C}^o$ stands for the opposite
category. For given objects $X$ and $Y$ by 
$\operatorname{Hom}_{\mathbf{C}}(X, Y)$ 
we denote the set of morphisms from $X$ to $Y$. Often we shall write
$\phi:X\to Y$ instead of $\phi\in\operatorname{Hom}_{\mathbf{C}}(X,Y)$. A
morphism $\phi:X\to Y$ is called $\langle$~retraction / coretraction~$\rangle$
if it has a $\langle$~right / left~$\rangle$ inverse morphism. A morphism 
is called an isomorphism if it is both a retraction and a coretraction. Usually we shall
express existence of isomorphism between $X$ and $Y$ as $X\isom{\mathbf{C}} Y$.
We say that two morphisms $\phi:X_1\to Y_1$ and $\psi:X_2\to Y_2$ are equivalent
in $\mathbf{C}$ if there exist isomorphisms $\alpha:X_1\to X_2$ and
$\beta:Y_1\to Y_2$ such that $\beta\phi=\psi\alpha$.

The first obvious example of a category that comes to mind is the category of
all sets and all maps between them. We denote this category by $\mathbf{Set}$.
Other examples will be given later. Two main examples of functors that any
category has are functors of morphisms. For a fixed
$X\in\operatorname{Ob}(\mathbf{C})$ we define covariant and contravariant
functors
$$
\operatorname{Hom}_{\mathbf{C}}(X,-)
:\mathbf{C}\to\mathbf{Set},\,
Y\mapsto \operatorname{Hom}_{\mathbf{C}}(X,Y), 
\phi\mapsto(\psi\mapsto \phi\psi),
$$
$$
\operatorname{Hom}_{\mathbf{C}}(-,X)
:\mathbf{C}\to\mathbf{Set},\,
Y\mapsto \operatorname{Hom}_{\mathbf{C}}(Y,X), 
\phi\mapsto(\psi\mapsto \psi\phi).
$$
This construction has its reminiscent analogs in many categories of mathematics
with slight modification of categories between which these functors act.

We say that two covariant functors $F:\mathbf{C}\to\mathbf{D}$,
$G:\mathbf{C}\to\mathbf{D}$ are isomorphic if there exists a class of
isomorphisms $ \{\eta_X:X\in\operatorname{Ob}(\mathbf{C}) \}$ in $\mathbf{D}$
(called natural isomorphisms), such that $G(f)\eta_X=\eta_Y F(f)$ for all morphisms
$f:X\to Y$. In this case we simply write $F\cong G$. A $\langle$~covariant /
contravariant~$\rangle$ functor $F:\mathbf{C}\to\mathbf{D}$ is called
representable by object $X$ if
$\langle$~$F\cong\operatorname{Hom}_{\mathbf{C}}(X,-)$ /
$F\cong\operatorname{Hom}_{\mathbf{C}}(-,X)$~$\rangle$. If a functor is
representable, then its representing object is unique up to an isomorphism in
$\mathbf{C}$.

Constructions of categorical product and coproduct shall play an important role
in this book. We say that $X$ is a $\langle$~product / coproduct~$\rangle$
of the family of objects $ \{X_\lambda:\lambda\in\Lambda \}$ if the functor
$\langle$~$
\prod_{\lambda\in\Lambda}\operatorname{Hom}_{\mathbf{C}}(-,X_{\lambda})
:\mathbf{C}\to\mathbf{Set}$
/
$
\prod_{\lambda\in\Lambda}\operatorname{Hom}_{\mathbf{C}}(X_{\lambda},-)
:\mathbf{C}\to\mathbf{Set}$~$\rangle$
is representable by object $X$. As a consequence we get that a
$\langle$~product / coproduct~$\rangle$, if it exists, is unique up to an
isomorphism. Later we shall give examples of the $\langle$~products /
coproducts~$\rangle$ in different categories of functional analysis. 


%-------------------------------------------------------------------------------
%    Topology
%-------------------------------------------------------------------------------

\subsection{
  Topology}\label{SubSectionTopology}

Let $(S,\tau)$ be a topological space. Elements of $\tau$ are called open sets,
and their complements are called closed sets. Let $E$ be an arbitrary subset of
$S$. By $\operatorname{cl}_S(E)$ we denote the closure of $E$ in $S$, that is
the smallest closed set that contains $E$. Similarly, by
$\operatorname{int}_S(E)$ we denote the interior of $E$, that is the largest
open set that contained in $E$. We say that $E$ is a neighborhood of point 
$s\in S$ if $s\in \operatorname{int}_S(E)$. We say that a set $E$ is dense 
in a set $F\subset S$ if $F\subset\operatorname{cl}_S(E)$. Note that $E$ can 
be regarded as a topological space, if we endow it with the subspace topology 
which equals $\{U\cap E:U\in\tau \}$. Topological space is called Hausdorff if any two
distinct points have disjoint open neighborhoods. In this book we shall work
with Hausdorff spaces only.

A map $f:X\to Y$ between topological spaces is called continuous if preimage
under $f$ of any open set is open. By $\mathbf{Top}$ we denote the category of
topological spaces with continuous maps in the role of morphisms. Isomorphisms
in $\mathbf{Top}$ are called homeomorphisms. The category $\mathbf{Top}$ admits
products. For a given family of topological spaces $
\{S_\lambda:\lambda\in\Lambda \}$ their product is the Tychonoff product
$\prod_{\lambda\in\Lambda}S_\lambda$, that is the Cartesian product of the
family $ \{S_\lambda:\lambda\in\Lambda \}$ with the coarsest topology making all
natural projections $p_\lambda:\prod_{\lambda\in\Lambda}S_\lambda\to S_\lambda$
continuous. The coproduct in $\mathbf{Top}$ is defined in a straightforward way.
Let $(S_\lambda)_{\lambda\in\Lambda}$ be a family of topological spaces, then their
coproduct $\coprod_{\lambda\in\Lambda} S_\lambda$ is the disjoint union 
$\bigsqcup_{\lambda\in\Lambda} S_\lambda$ with the strongest topology making all
natural inclusions $i_\lambda:S_\lambda\to \coprod_{\lambda\in\Lambda}S_\lambda$ 
continuous.

Now we need to recall the notion of a cover.
Let $\mathcal{E}$ be a family of subsets of topological space $S$. We say that
$\mathcal{E}$ is a cover if its union equals $S$. We say that cover is open if
all its elements are open sets. A cover is called locally finite if any point of
$S$ has a neighborhood that intersects with only finitely many elements of the cover.
We say that cover $\mathcal{E}_1$ is inscribed into cover $\mathcal{E}_2$ if any
element of $\mathcal{E}_1$ is a subset of some element of $\mathcal{E}_2$. A
cover $\mathcal{E}_1$ is called a subcover of $\mathcal{E}_2$ if
$\mathcal{E}_1\subset\mathcal{E}_2$. Finally, a topological space is called 
\begin{enumerate}[label = (\roman*)]
  \item compact if any open cover admits a finite open subcover; 

  \item paracompact if any open cover is inscribed into some locally finite
  open cover;
  
  \item pseudocompact if any locally finite family of open sets is finite;

  \item locally compact if any point has a compact neighborhood;

  \item extremely disconnected spaces if the closure of any open set is
  open;

  \item Stonean if it is an extremely disconnected Hausdorff compact space.
\end{enumerate}

The property of being $\langle$~compact / paracompact / locally
compact~$\rangle$ space is preserved by $\langle$~closed / closed / open and
closed~$\rangle$ subspaces. A topological space is pseudocompact iff any
continuous function on this space is bounded. Any non-compact locally compact
Hausdorff space $S$ can be regarded as dense subspace of some compact Hausdorff
space, which is called a compactification of $S$. There is the smallest and 
the largest such compactification. The smallest
one is called the Alexandroff's compactification $\alpha S$.  By definition
$\alpha S:=S\cup  \{S \}$. A subset of $\alpha S$ is called open if it is an
open subset of $S$ or has the form $ \{S \}\cup S\setminus K$ for some compact
set $K\subset S$. The largest compactification $\beta S$ is called the
Stone-Cech compactification. It can be represented as the image of the embedding
$j:S\to\prod_{f\in C}[0,1]:s\mapsto \prod_{f\in C}f(s)$, where $C$ is a set of
all continuous maps from $S$ to $[0,1]$. The Stone-Cech compactification is highly
non-constructive. Even $\beta\mathbb{N}$ has no explicit description, though it
is known that $\beta\mathbb{N}$ is an extremely disconnected Hausdorff compact.

Occasionally we shall apply the Urysohn's lemma to locally compact Hausdorff
spaces. It states that for any compact subset $K$ of an open set $V$ in a locally
compact Hausdorff space $S$ there exists a continuous function $f:S\to [0,1]$
such that $f|_K=1$ and $f|_{S\setminus V}=0$. 

For more details on topological spaces see comprehensive
treatise~\cite{EngelGenTop}. 

%-------------------------------------------------------------------------------
%    Filters, nets and limits
%-------------------------------------------------------------------------------

\subsection{
  Filters, nets and limits}\label{SubSectionFiltersNetsAndLimits} 

We will use two generalizations of the notion of a sequence and a limit of
a sequence.

Let $M$ be an arbitrary set. A family $\mathfrak{F}$ of subsets of the set $M$ 
is called a filter on $M$ if $\mathfrak{F}$ doesn't contain the empty set, 
$\mathfrak{F}$ is closed under finite intersections and $\mathfrak{F}$ contains 
all supersets of its elements. In general filters are too large to be described 
explicitly. To overcome this difficulty we shall use filter bases. A non-empty 
family $\mathfrak{B}$ of subsets of the set $M$ is called a filter base on 
a set $M$ if $\mathfrak{B}$ doesn't contain the empty set and intersection of 
any two elements of $\mathfrak{B}$ contains some element of $\mathfrak{B}$. 
Given a filter base $\mathfrak{B}$ we can construct a filter by adding 
to $\mathfrak{B}$ all supersets of elements of $\mathfrak{B}$.

We say that filter $\mathfrak{F}_1$ dominates filter $\mathfrak{F}_2$ if
$\mathfrak{F}_2\subset\mathfrak{F}_1$. Therefore, the set of all filters on a
given set a is partially ordered set. Filters that are maximal with respect to
this order are called ultrafilters. An easy application of Zorn's lemma gives
that any filter is dominated by some ultrafilter.

Let $\mathfrak{F}$ be a filter on the set $M$, and $\phi:M\to S$ be a map from
$M$ to the Hausdorff topological space $S$. We say that $x$ is a limit of $\phi$
along $\mathfrak{F}$ and write $x=\lim_{\mathfrak{F}} \phi(m)$ if for every open
neighborhood $U$ of $x$ holds $\phi^{-1}(U)\in\mathfrak{F}$. Directly from the
definition it follows that if $\phi$ has a limit along $\mathfrak{F}$ then it
has the same limit along any filter that dominates $\mathfrak{F}$. 

Limit along filter preserve order structure of $\mathbb{R}$. More precisely: if
two functions $\phi:M\to\mathbb{R}$ and $\psi:M\to\mathbb{R}$ have limits along
filter $\mathfrak{F}$ and $\phi\leq\psi$, then 
$
\lim_{\mathfrak{F}}\phi(m)\leq\lim_{\mathfrak{F}}\psi(m).
$

Limits along filters respect continuous functions. Rigorously this formulates as
follows. Assume for each $\lambda\in\Lambda$ a function $\phi_\lambda:M\to
S_\lambda$ has a limit along filter $\mathfrak{F}$, then for any continuous
function $g:\prod_{\lambda\in\Lambda}S_\lambda\to Y$ holds
$$
\lim_{\mathfrak{F}}g\left(
  \prod_{\lambda\in\Lambda}\phi_\lambda(m)
\right)
=g\left(\prod_{\lambda\in\Lambda}\lim_{\mathfrak{F}}\phi_\lambda(m)\right).
$$
In particular, limits along filters are linear and multiplicative. Just like
ordinary sequences.

The most important feature of filters and the reason of our interest is the
following: if $\mathfrak{U}$ is an ultrafilter on the set $M$ and $\phi:M\to K$
is a function with values in the compact Hausdorff space $K$, then
$\lim_{\mathfrak{U}}\phi(m)$ exists. In particular, we always can speak of
limits along ultrafilters of bounded scalar valued functions.

Another approach to the generalization of the notion of the limit is a limit of
a net. A directed set is a partially ordered set $(N,\leq)$ in which any two
elements have an upper bound. Every directed set gives rise to the so-called
section filter, whose filter base consists of so-called sections $
\{\nu':\nu\leq\nu' \}$ for some $\nu\in N$. Any function $x:N\to X$ from a
directed set $(N,\leq)$ into a topological space $X$ is called a net. Usually
it is denoted as ${(x_\nu)}_{\nu\in N}$ to allude to sequences. 
A limit of the net $x:N\to X$ is a limit of the function $x$ along section
filter of the directed set $N$. It is denoted $\lim_\nu x_\nu$. We shall exploit
both notions of the limit.

More on this matters can be found in [\cite{BourbElemMathGenTopLivIII}, section
7].


%-------------------------------------------------------------------------------
%    Measure theory basics
%-------------------------------------------------------------------------------

\subsection{
  Measure theory}\label{SubSectionMeasureTheory}

A family $\Sigma$ of subsets of the set $\Omega$ is called a $\sigma$-algebra if
it contains an empty set, complements of all its elements and is closed
under countable unions. If $\Sigma$ is a $\sigma$-algebra of subsets of $\Omega$
we call $(\Omega,\Sigma)$ a measurable space. Elements of $\Sigma$ are called
measurable sets. 

A function $\mu:\Sigma\to[0,+\infty]$ such that:  
\begin{enumerate}[label = (\roman*)]
  \item $\mu(\varnothing)=0$; 

  \item $\mu\left(\bigcup\limits_{n\in\mathbb{N}} E_n\right)
  =\sum\limits_{n\in\mathbb{N}}\mu(E_n)$ for any family of disjoint sets
  ${(E_n)}_{n\in\mathbb{N}}$ in $\Sigma$; 
\end{enumerate}

is called a measure. The triple $(\Omega,\Sigma,\mu)$ is called a measure space.
If $\mu$ attains only finite values we may drop the first condition. The second
condition is essential and called the $\sigma$-additivity. The simplest example
of measure space is an  arbitrary set $\Lambda$ with $\sigma$-algebra of all
subsets and so-called counting measure
$\mu_c:\mathcal{P}(\Lambda)\to[0,+\infty]$. By definition $\mu_c(E)$ equals
$\operatorname{Card}(E)$ if $E$ is finite and $+\infty$ otherwise. If $E$ is a
measurable set, by $\Sigma|_E$ we denote the $\sigma$-algebra $ \{F\cap
E:F\in\Sigma \}$ and by $\mu|_E$ we denote the restriction of $\mu$ to
$\Sigma|_E$. A set $E$ in $\Omega$ is called negligible if there exists a
measurable set $F$ of measure $0$ that contains $E$. Similarly, a set $E$ in
$\Omega$ is conegligible if $\Omega\setminus E$ is negligible. Let $P$ be some
property that depends on points of $\Omega$. We say that $P$ holds almost
everywhere if the set where $P$ is violated is negligible. A measure space is
called $\sigma$-finite if there exists a countable family of measurable sets of
finite measure whose union is the whole space. The class of $\sigma$-finite
spaces is enough for most applications, but we shall encounter a more generic
measure spaces.

A measurable space $(\Omega,\Sigma,\mu)$ is called strictly localizable if there
exists a family of disjoint measurable sets 
$ \{E_\lambda:\lambda\in\Lambda \}$ of finite measure such that: 
\begin{enumerate}[label = (\roman*)]
  \item $\bigcup_{\lambda\in\Lambda}E_\lambda=\Omega$;

  \item $E$ is measurable iff $E\cap E_\lambda$ is measurable for all
  $\lambda\in\Lambda$;

  \item for any measurable set $E$ holds 
  $\mu(E)=\sum_{\lambda\in\Lambda}\mu(E\cap E_\lambda)$. 
\end{enumerate}
  
The class of strictly localizable measure spaces is huge. It includes all
$\sigma$-finite measure spaces, their arbitrary unions, Haar measures of
locally compact groups, counting measures and much more. In what follows we
shall consider only strictly localizable measure spaces.

We shall exploit a more detailed classification of measure spaces. We say that a
measurable set $E$ is an atom if $\mu(E)>0$ and for any measurable subset $F$ of
$E$ either $F$ or $E\setminus F$ is negligible. Directly from the definition it
follows that that all atoms of strictly localizable measure spaces are of finite
measure. In general an atom may not be a mere singleton.

We say that a measure space is non-atomic if there are no atoms for its measure.
A measure space is called purely atomic if every measurable set of positive
measure contains an atom. A straightforward application of Zorn's lemma gives
that a purely atomic measure space can be represented as disjoint union of some
family of atoms. This family is countable if measure space is $\sigma$-finite.
These facts allow us to say that the structure of purely atomic measure space is
well understood. The structure of strictly localizable non-atomic measure spaces
is given by Maharam's theorem [\cite{FremMeasTh}, 332B]. 

For completeness, we shall say a few words on constructions with measures. 
By $\mu_1\times \mu_2$ we denote the product measure of two measure spaces 
$(\Omega_1,\Sigma_1,\mu_1)$ and $(\Omega_2,\Sigma_2,\mu_2)$. Formal definition of
product measure for localizable measure spaces is rather involved
[\cite{FremMeasTh}, definition 251F] and we don't give it here.  For our
purposes it is enough to know that the product of two strictly localizable
measure spaces is again strictly localizable [\cite{FremMeasTh}, proposition
251N]. By direct sum of measure spaces $ \{(\Omega_\lambda, \Sigma_\lambda,
\mu_\lambda):\lambda\in\Lambda \}$ we denote the disjoint union of sets 
$\{\Omega_\lambda:\lambda\in\Lambda \}$ with $\sigma$-algebra defined as 
$\Sigma= \{
  E\subset \Omega: E\cap E_\lambda\in\Sigma_\lambda
  \mbox{ for all }\lambda\in\Lambda
 \}$ 
and measure given by the formula 
$\mu(E)=\sum_{\lambda\in\Lambda}\mu_\lambda(E\cap E_\lambda)$. It is clear now
that strictly localizable measure space are exactly direct sums of finite
measure spaces.

Assume $(\Omega,\Sigma,\mu)$ is a $\sigma$-finite measure space, then there
exists a purely atomic measure $\mu_1:\Sigma\to[0,+\infty]$ and a non-atomic
measure $\mu_2:\Sigma\to[0,+\infty]$ such that $\mu=\mu_1+\mu_2$. Even more
there exist measurable sets $\Omega_a^{\mu}$ and
$\Omega_{na}^{\mu}=\Omega\setminus \Omega_a^{\mu}$ such that
$\mu_1(\Omega_{na}^{\mu})=\mu_2(\Omega_a^{\mu})=0$. The sets $\Omega_a^{\mu}$
and $\Omega_{na}^{\mu}$ are called respectively the atomic and the non-atomic
parts of the measure space $(\Omega,\Sigma,\mu)$.

By measurable function we always mean a complex or real valued function on
measurable space, with the property that preimage of every open set is
measurable. We say that two measurable functions are equivalent if the set where
they are different is negligible. If $f:\Omega\to\mathbb{R}$ is an  integrable
function on $(\Omega,\Sigma,\mu)$, then we may define a new measure 
$$
f\mu:\Sigma\to[0,+\infty],\,E\mapsto\int_{E}f(\omega)d\mu(\omega).
$$

The notion of measure can be extended by changing the range of values that a
measure can attain. Any $\sigma$-additive function $\mu:\Sigma\to\mathbb{C}$ on
a measurable space $(\Omega,\Sigma)$ is called a complex measure. Any complex
measure $\mu$ can be represented as $\mu=\mu_1-\mu_2+i(\mu_3-\mu_4)$, where
$\mu_1,\mu_2,\mu_3,\mu_4$ --- are finite measures. As a consequence every
complex measure is finite, and therefore we have a well-defined total variation
measure:
$$
|\mu|:\Sigma\to\mathbb{R}_+,\,
E\mapsto\sup\left \{\sum_{n\in\mathbb{N}}|\mu(E_n)|
: \{E_n:n\in\mathbb{N} \}\subset\Sigma,\,\, E=\bigsqcup\limits_{n\in\mathbb{N}} E_n\right \}
$$

Let $\mu$ and $\nu$ be two measures on a measurable space $(\Omega,\Sigma)$. We
say that $\mu$ and $\nu$ are mutually singular and write $\mu\perp\nu$ if there
exists a measurable set $E$ such that $\mu(E)=\nu(\Omega\setminus E)=0$. A somewhat 
opposite property is the absolute continuity. We say that $\nu$ is absolutely
continuous with respect to $\mu$ and write $\nu\ll\mu$ if $\nu(E)=0$ for every
measurable set $E$ with $\mu(E)=0$. In general, two measures may neither be
absolutely continuous nor singular with respect to each other. We have the
Lebesgue decomposition theorem for this case. For a given two $\sigma$-finite
measures $\mu$ and $\nu$ on a measurable space $(\Omega,\Sigma)$ there exists a
measurable function $\rho_{\nu,\mu}:\Omega\to\mathbb{C}$, a $\sigma$-finite
measure $\nu_s:\Sigma\to[0,+\infty]$ and two measurable sets
$\Omega_s^{\nu,\mu}$, $\Omega_c^{\nu,\mu}=\Omega\setminus\Omega_s^{\nu,\mu}$
such that $\nu=\rho_{\nu,\mu}\mu+\nu_s$ and
$\mu(\Omega_s^{\nu,\mu})=\nu_s(\Omega_c^{\nu,\mu})=0$, i.e. $\mu\perp\nu_s$.

Finally, we shall say a few words on measures defined on topological spaces. We
shall call these measures the topological measures. Given a topological space $S$ we may 
consider the minimal $\sigma$-algebra containing all open subsets of $S$. 
It is called the Borel $\sigma$-algebra of $S$ and denoted by $Bor(S)$. 
Measures and complex measures defined on Borel $\sigma$-algebras are supported 
with adjective Borel.

The support of a complex Borel measure $\mu$ is the set of all points
$s\in S$ for which every open neighborhood of $s$ has a positive measure. We
denote the set of such points by $\operatorname{supp}(\mu)$. The support is
always closed. A Borel measure $\mu$ is called
\begin{enumerate}[label = (\roman*)]
  \item strictly positive if $\operatorname{supp}(\mu)=S$;

  \item a measure with full support 
  if $\mu(S\setminus\operatorname{supp}(\mu))=0$;

  \item locally finite if every point has an open neighborhood of finite measure; 

  \item inner regular with respect to a
  class $\mathcal{C}$ of Borel sets if for any Borel set $E$ holds 
  $$
  \mu(E)=\sup \{\mu(K): K\subset E, K\in\mathcal{C} \};
  $$

  \item outer regular with respect to a 
  class $\mathcal{C}$ of Borel sets if for any Borel set $E$ holds 
  $$
  \mu(E)=\inf \{\mu(K): K\subset E, K\in\mathcal{C} \};
  $$

  \item residual if $\mu(E)=0$ for any Borel nowhere dense set $E$;

  \item normal if its residual and has full support.
\end{enumerate}

Usually we consider regularity of measures with respect to classes of open and
compact sets. Now recall a few facts on topological measures. All compact sets 
have finite measure if measure is locally finite. Any finite inner compact 
regular measure is outer open regular. Any finite inner compact regular and
inner open regular measure is normal. 

We say that a complex Borel measure $\mu$ defined on a 
locally compact Hausdorff space $S$ is regular if it is inner compact regular.  

Most of the results and definitions in this section can be found in the first,
second and the fourth volumes of~\cite{FremMeasTh}.

%-------------------------------------------------------------------------------
%    Banach spaces, algebras and modules
%-------------------------------------------------------------------------------

\section{
  Banach structures}\label{SectionBanachStructures}

%-------------------------------------------------------------------------------
%    Banach spaces
%-------------------------------------------------------------------------------

\subsection{
  Banach spaces}\label{SubSectionBanachSpaces}

We assume that our reader is familiar with fundamentals of functional analysis
and its constructions, otherwise consult~\cite{HelLectAndExOnFuncAn}
or~\cite{ConwACoursInFuncAn}. In this book we will highly rely on results about
geometry of Banach spaces.
See~\cite{CarothShortCourseBanSp},~\cite{KalAlbTopicsBanSpTh}
or~\cite{FabHabBanSpTh} for a quick introduction. All Banach spaces are
considered over the complex field, unless otherwise stated. 

By $\langle$~$B_E$ / $B_E^\circ$~$\rangle$ we denote the $\langle$~closed /
open~$\rangle$ unit ball of a Banach space $E$ with center at zero. For a given 
set $S\subset E$ by $\operatorname{span}(S)$ we denote its linear span. 

By $E^{cc}$ we denote a Banach space with the same set of vectors as in $E$, the
same addition but with new multiplication by conjugate scalars:  $\alpha
\overline{x}:=\overline{\overline{\alpha}x}$ for $\alpha\in\mathbb{C}$ 
and $x\in E$. Note: elements of $E^{cc}$ we denote by $\overline{x}$. Clearly,
${(E^{cc})}^{cc}=E$.

If $F$ is a closed subspace of the Banach space $E$, then $E/F$ stands for 
linear quotient Banach space. Its norm defined by equality 
$$
\Vert x+F\Vert=\inf \{\Vert x+y\Vert: y\in F \},
$$
where $x+F\in E/F$.

Now fix two Banach spaces $E$ and $F$. A map $T:E\to F$ is called conjugate
linear if the respective map $T:E^{cc}\to F$ is linear. A linear operator
$T:E\to F$ is called:
\begin{enumerate}[label = (\roman*)]
  \item bounded if its norm $\Vert T\Vert:=\sup \{\Vert T(x)\Vert:x\in B_E \}$ 
  is finite;

  \item contractive if its norm is at most $1$;

  \item compact if $T(B_E)$ is relatively compact in $F$;

  \item nuclear if it can be represented as an absolutely convergent series of
  rank one operators.
\end{enumerate}

Any nuclear operator is compact. Any compact operator is
bounded, any bounded operator is continuous. By $\langle$~$\mathcal{B}(E,F)$ /
$\mathcal{K}(E,F)$ / $\mathcal{N}(E,F)$~$\rangle$ we denote the Banach space of
$\langle$~bounded / compact / nuclear~$\rangle$ linear operators from $E$ to
$F$. If $F=E$ we use the shortcut $\langle$~$\mathcal{B}(E)$ / $\mathcal{K}(E)$
/ $\mathcal{N}(E)$~$\rangle$ for this space. The norms in $\mathcal{B}(E,F)$ and
$\mathcal{K}(E,F)$ are just the usual operator norm. The norm of a nuclear
operator $T$ is defined by equality
$$
\Vert T\Vert
:=\inf\left \{
  \sum_{n=1}^\infty\Vert S_n\Vert
  :T=\sum_{n=1}^\infty S_n,\quad 
  {(S_n)}_{n\in\mathbb{N}} - \mbox{ rank one operators}
\right \}.
$$

By $\mathbf{Ban}$ we shall denote the category of Banach spaces with bounded
linear operators in the role of morphisms, while $\mathbf{Ban}_1$ stands for the
category of Banach spaces with contractive operators in the role of morphisms.
As a consequence, $\operatorname{Hom}_{\mathbf{Ban}}(E,F)$ is just another
name for $\mathcal{B}(E,F)$.

Two Banach spaces $E$ and $F$ are $\langle$~isometrically isomorphic /
topologically isomorphic~$\rangle$ as Banach spaces if there exists a bounded
linear operator $T:E\to F$ which is both $\langle$~isometric and surjective /
topologically injective and topologically surjective~$\rangle$. The fact that
$E$ and $F$ are $\langle$~isometrically isomorphic / topologically
isomorphic~$\rangle$ Banach spaces means that
$\langle$~$E\isom{\mathbf{Ban}_1}F$ / $E\isom{\mathbf{Ban}}F$~$\rangle$. The
Banach-Mazur distance between $E$ and $F$ is defined by the formula 
$$
d_{BM}(E,F):=\inf \{
  \Vert T\Vert\Vert T^{-1}\Vert
  :T \in \mathcal{B}(E,F) \mbox{ --- a topological isomorphism}
 \}.
$$ 
If $E$ and $F$ are not topologically isomorphic the Banach-Mazur distance
between them is infinite.


By $E^*$ we denote the space of bounded linear functionals on $E$, that is
$E^*=\mathcal{B}(E, \mathbb{C})$. It is called a dual space of $E$. Similarly,
one can define the second and higher duals of $E$. An important corollary of the
Hahn-Banach theorem says that the bounded linear operator 
$$
\iota_E:E\to E^{**},\,x\mapsto (f\mapsto f(x))
$$ 
is isometric. We call this operator the natural embedding of $E$ into its 
second dual $E^{**}$.

For a given bounded linear operator $T:E\to F$ its adjoint is bounded linear 
operator 
$$
T^*:F^*\to E^*,\,f\mapsto (x\mapsto f(T(x))).
$$
Again from the Hahn Banach 
theorem it follows that $\Vert T^*\Vert=\Vert T\Vert$. One can easily check 
that $T^{**}\iota_E=\iota_F T$.  

For a given subspace $F$ of $\langle$~$E$ / $E^*$~$\rangle$ we define 
its $\langle$~right / left~$\rangle$ annihilator 
$\langle$~$F^\perp$ / ${}^\perp F$~$\rangle$ as 
$\langle$~$ \{ f\in E^*: f(x)=0 \mbox{ for all } x\in F \}$ / 
$ \{ x\in E : f(x)=0 \mbox{ for all } f\in F \}$~$\rangle$. 
Clearly, $E^{\perp} = \{ 0\}$, $0^{\perp}=E^*$ 
and ${}^{\perp}E^*= \{ 0\}$, ${}^{\perp}0= E$. Annihilators are closely related
with quotient spaces. One can show that 
operators 
$$
i: F^*\to E^*/F^{\perp},\, f\mapsto f|_F+F^\perp,
\quad\quad 
q:{(E/F)}^*\to F^{\perp},\, f\mapsto (x\mapsto f(x + F))
$$ 
are isometric isomorphisms.

A few words on classification of bounded linear operators. A bounded linear
operator $T:E\to F$ is called:
\begin{enumerate}[label = (\roman*)]
  \item topologically injective if it performs homeomorphism on its image;

  \item topologically surjective if it is an open map;

  \item coisometric if it maps open unit ball onto open unit ball;

  \item strictly coisometric if it maps closed unit ball onto closed unit ball; 

  \item $c$-topologically injective, if $\Vert x\Vert\leq c\Vert  T(x)\Vert$ for
  all $x\in E$;

  \item $c$-topologically surjective, if $cT(B_E^\circ)\supset B_F^\circ$;

  \item strictly $c$-topologically surjective, if $cT(B_E)\supset B_F$.
\end{enumerate}

Note that $T$ is topologically $\langle$~injective / surjective~$\rangle$ iff it
is $c$-topologically $\langle$~injective / surjective~$\rangle$ for some $c>0$.
Obviously $\langle$~coisometric / strictly coisometric~$\rangle$ operators are
exactly contractive $\langle$~$1$-topologically surjective / strictly
$1$-topologically surjective~$\rangle$ operators. These classes of operators 
behave nicely with respect to taking adjoints:

\begin{enumerate}[label = (\roman*)]
  \item if $ T$ is $c$-topologically surjective or strictly $c$-topologically 
  surjective, then $ T^*$ is $c$-topologically injective;

  \item if $ T$ $c$-topologically injective, then $ T^*$ is strictly
  $c$-topologically surjective;

  \item if $ T^*$ $c$-topologically surjective or strictly $c$-topologically 
  surjective, then $ T$ is $c$-topologically injective;

  \item if $T^*$ $c$-topologically injective and $E$ is complete, then $T$ 
  is $c$-topologically surjective.
\end{enumerate}

Let us discuss relations between Banach spaces and their subspaces. A bounded 
linear operator $T:E\to F$ is called a $\langle$~$c$-retraction /
$c$-coretraction~$\rangle$ if there exist a bounded linear operator $S:F\to E$
such that $\langle$~$T S=1_F$ / $S T=1_E$~$\rangle$ 
and $\Vert T\Vert\Vert S\Vert\leq c$. In this case we say 
that $\langle$~$F$ / $E$~$\rangle$ has a
$c$-complemented copy in $E$ via topologically $\langle$~injective /
surjective~$\rangle$ operator $T$. If the natural embedding of a subspace $F$
into the ambient space $E$ is a $c$-coretraction, then we say that $F$ is
$c$-complemented in $E$. Complemented subspaces can be described in terms of so-called 
projections. A bounded linear operator $P:E\to E$ is called a projection 
of $E$ onto $F$ if $P^2=P$, $\operatorname{Im}(P)=F$. One can show that 
$F$ is $c$-complemented in $E$ iff there is a projection $P$ from $E$ onto $F$ 
with $\Vert P\Vert\leq c$. We say that $F$ is weakly $c$-complemented in $E$
if $F^*$ is $c$-complemented in $E^*$ via the map $i^*$, which is the adjoint of
the natural embedding. If $F$ is $c$-complemented in $E$ then it is 
weakly $c$-complemented in $E$.  The term ``contractively complemented'' will 
be a synonym for $1$-complemented. Sometimes we will omit a constant $c$ and 
simply say that one Banach space $\langle$~has a complemented copy / 
is complemented~$\rangle$ inside another. Then we can say that a 
subspace $F$ of a Banach space $E$ is complemented if there exists a 
closed subspace $G$ in $E$ such that $E\isom{\mathbf{Ban}}F\bigoplus_1 G$.

All finite dimensional subspaces are complemented, but not necessarily
contractively complemented. An interesting example of a contractively 
complemented subspace is the following: consider arbitrary Banach space $E$, 
then $E^*$ is contractively complemented in $E^{***}$ via Dixmier 
projection $P=\iota_{E^*}{(\iota_E)}^*$. A canonical example of uncomplemented 
subspace is $c_0(\mathbb{N})$ 
inside $\mathbb{\ell_\infty}(\mathbb{N})$ [\cite{KalAlbTopicsBanSpTh}, theorem 2.5.5].
Nevertheless, $c_0(\mathbb{N})$ is weakly complemented in
$\ell_\infty(\mathbb{N})$ by Dixmier projection.

Let $E$, $F$ and $G$ be three Banach spaces, then a bilinear operator
$\Phi:E\times F\to G$ is called bounded if its norm 
$$
\Vert \Phi\Vert:=\sup \{\Vert \Phi(x,y)\Vert:x\in B_E, y\in B_F \}
$$ 
is finite. 
The Banach space of all bounded bilinear operators on $E\times F$ with 
values in $G$ is denoted by $\mathcal{B}(E\times F,G)$.

Now consider the algebraic tensor product $E\otimes F$ of Banach spaces $E$ and
$F$. This linear space can be endowed with different norms, but the most
important is the projective norm. For $u\in E\otimes F$ we define its projective
norm as
$$
\Vert u\Vert
:=\inf\left \{
  \sum_{i=1}^n \Vert x_i\Vert\Vert y_i\Vert
  :u=\sum_{i=1}^n x_i\otimes y_i, 
  {(x_i)}_{i\in\mathbb{N}_n}\subset E, 
  {(y_i)}_{i\in\mathbb{N}_n}\subset F
\right \}.
$$
It is indeed a norm, but not complete in general. The symbol $E\projtens F$
stands for the completion of $E\otimes F$ under the projective norm. We call the
resulting completion the projective tensor product of Banach spaces $E$ and $F$.
The resulting bilinear operator 
$\theta:E\times F\to E\projtens F,\,(x,y)\mapsto x\otimes y$ is contractive.
Let $T:E_1\to E_2$ and $S:F_1\to F_2$ be two bounded linear operators between
Banach spaces, then there exists a unique bounded linear operator 
$$
T\projtens S:E_1\projtens F_1\to E_2\projtens F_2
$$ 
such that  $(T\projtens S)(x\projtens y)=T(x)\projtens S(y)$ 
for all $x\in E_1$ and $y\in F_1$. 
Even more $\Vert T\projtens S\Vert=\Vert T\Vert\Vert S\Vert$. The main feature 
of projective tensor product which makes it so important is the following 
universal property: for any Banach spaces $E$, $F$ and $G$ there is a 
natural isometric isomorphism:
$$
\mathcal{B}(E\projtens F,G)\isom{\mathbf{Ban}_1}\mathcal{B}(E\times F,G)
$$
In other words, projective tensor product linearizes bounded bilinear operators.
Also, we have the following two (natural in $E$, $F$ and $G$) isometric
isomorphisms:
$$
\mathcal{B}(E\projtens F,G)
\isom{\mathbf{Ban}_1}\mathcal{B}(E,\mathcal{B}(F,G))
\isom{\mathbf{Ban}_1}\mathcal{B}(F,\mathcal{B}(E,G))
$$
The last isomorphism is called the law of adjoint associativity. There are many
other tensor norms on the algebraic tensor product of Banach spaces. Their
thorough treatment can be found in~\cite{DiestMetTheoryOfTensProd}.

Now we are able to craft four very important functors:
$$
\mathcal{B}(-,E):\mathbf{Ban}\to\mathbf{Ban}
\qquad\qquad
\mathcal{B}(E,-):\mathbf{Ban}\to\mathbf{Ban}
$$
$$
-\projtens E:\mathbf{Ban}\to\mathbf{Ban}
\qquad\qquad
E\projtens -:\mathbf{Ban}\to\mathbf{Ban}.
$$
We shall often encounter them. For example, the well known adjoint functor
${}^*$ is nothing more than $\mathcal{B}(-,\mathbb{C})$. All these functors have
their obvious analogs on $\mathbf{Ban}_1$.

Now we  proceed to classical examples of Banach spaces. 

An important source of examples of Banach spaces are $L_p$-spaces, also known as
Lebesgue spaces. A detailed discussion of basic properties of $L_p$-spaces can
be found in~\cite{CarothShortCourseBanSp}.  Let $(\Omega,\Sigma,\mu)$ be a
measure space.  For $1\leq p<\infty$, as usually, the symbol $L_p(\Omega,\mu)$
stands for the Banach space of equivalence classes of functions
$f:\Omega\to\mathbb{C}$ such that $|f|^p$ is Lebesgue integrable with respect to
measure $\mu$. The norm of such function is defined by
$$
\Vert f\Vert
:={\left(
  \int\limits_{\Omega}{|f(\omega)|}^p d\mu(\omega)
\right)}^{1/p}.
$$ 
By $L_\infty(\Omega,\mu)$ we denote the Banach space of equivalence classes of
bounded measurable functions with norm defined as 
$$
\Vert f\Vert:=\inf\left \{
  \sup_{\omega\in\Omega\setminus N}|f(\omega)|
  :N\subset\Omega - \mbox{is negligible}
\right \}.
$$
For simplicity, we shall speak of functions in $L_p(\Omega,\mu)$ instead of their
equivalence classes. All equalities and inequalities about functions of
$L_p$-spaces are understood up to negligible sets. It is well-known that
${L_p(\Omega,\mu)}^*\isom{\mathbf{Ban}_1}L_{p^*}(\Omega,\mu)$ for 
$1\leq p<+\infty$ [\cite{FremMeasTh}, theorems 243G, 244K]. 
One more well known fact is that, $L_p$-spaces are reflexive for 
$1<p<+\infty$. Here we exploited the standard 
notation $p^*=+\infty$ if $p=1$ and $p^*=p/(p-1)$ if $1<p<+\infty$.
Clearly, $p^{**}=p$ for $1<p<+\infty$.

The most well known classes of Banach spaces are related to continuous
functions. Let $S$ be a locally compact Hausdorff space. We say that a function
$f:S\to\mathbb{C}$ vanishes at infinity  if for any $\epsilon>0$ there exists a
compact $K\subset S$ such that $|f(s)|\leq\epsilon$ for all $s\in S\setminus K$.
The linear space of continuous functions on $S$ vanishing at infinity is denoted
by $C_0(S)$. When endowed with $\sup$-norm $C_0(S)$ becomes a Banach space. Any
set $\Lambda$ with discrete topology may be regarded as a locally compact space
and following the traditional notation we shall write $c_0(\Lambda)$ instead of
$C_0(\Lambda)$. If $K$ is a compact Hausdorff space then all functions on $K$
vanish at infinity. We use the notation $C(K)$ for $C_0(K)$ to indicate that $K$
is compact. Some Banach spaces in fact are $C(K)$-spaces in disguise. For
example, if we are given a measure space $(\Omega,\Sigma,\mu)$, then
$B(\Omega,\Sigma)$ --- the space of bounded measurable functions with
$\sup$-norm or $L_\infty(\Omega,\mu)$ are $C(K)$ spaces for some compact
Hausdorff space $K$ [\cite{KalAlbTopicsBanSpTh}, remark 4.2.8]. 
By $M(S)$ we denote the Banach space of
complex finite Borel regular measures on $S$. The norm of measure $\mu\in M(S)$
is defined by equality $\Vert\mu\Vert=|\mu|(S)$, where $|\mu|$ is a total
variation measure of measure $\mu$. By Riesz-Markov-Kakutani theorem
[\cite{ConwACoursInFuncAn}, section C.18] we have
${C_0(S)}^*\isom{\mathbf{Ban}_1}M(S)$. In fact $M(S)$ is an $L_1$-space, see
discussion after [\cite{DalLauSecondDualOfMeasAlg}, proposition 2.14]. 

We shall also mention one important specific case of $L_p$-spaces. For a given
index set $\Lambda$ and a counting measure
$\mu_c:\mathcal{P}(\Lambda)\to[0,+\infty]$ the respective $L_p$-space is denoted
by $\ell_p(\Lambda)$. For this type of measure spaces we have one more important
isomorphism ${c_0(\Lambda)}^*\isom{\mathbf{Ban}_1}\ell_1(\Lambda)$. By definition, 
we take $c_0(\varnothing)=\ell_p(\varnothing)= \{0 \}$ for 
$1\leq p\leq+\infty$. This example motivates the following construction.

Let $ \{E_\lambda:\lambda\in\Lambda \}$ be an arbitrary family of Banach spaces.
For each $x\in \prod_{\lambda\in\Lambda} E_\lambda$ we define 
$\Vert x\Vert_p
=\Vert{
  (\Vert x_\lambda\Vert)}_{\lambda\in\Lambda}
\Vert_{\ell_p(\Lambda)}$
for $1\leq p\leq +\infty$ and 
$\Vert x\Vert_0
=\Vert
  {(\Vert x_\lambda\Vert)}_{\lambda\in\Lambda}
\Vert_{c_0(\Lambda)}$. 
Then the Banach space
$\left \{
  x\in \prod_{\lambda\in\Lambda} E_\lambda
  :\Vert x\Vert_p<+\infty
\right \}$ 
with the norm $\Vert\cdot\Vert_p$ is denoted by $\bigoplus_p
\{E_\lambda:\lambda\in\Lambda \}$. We call these objects $\bigoplus_p$-sums of
Banach spaces $ \{E_\lambda:\lambda\in\Lambda \}$. It is almost tautological
that the Banach space $\ell_p(\Lambda)$ is the $\bigoplus_p$-sum of the family $
\{\mathbb{C}:\lambda\in\Lambda \}$. A nice property of $\bigoplus_p$-sums is
their interrelation with duality:
$$
{\left(\bigoplus\nolimits_p \{E_\lambda:\lambda\in\Lambda \}\right)}^*
\isom{\mathbf{Ban}_1}
\bigoplus\nolimits_{p^*} \{E_\lambda^*:\lambda\in\Lambda \}
$$
for all $1\leq p<+\infty$ and 
$$
{\left(\bigoplus\nolimits_0 \{E_\lambda:\lambda\in\Lambda \}\right)}^*
\isom{\mathbf{Ban}_1}
\bigoplus\nolimits_1 \{E_\lambda^*:\lambda\in\Lambda \}
$$
If $ \{T_\lambda\in\mathcal{B}(E_\lambda, F_\lambda):\lambda\in\Lambda \}$ is a
family of bounded linear operators, then for all $1\leq p\leq+\infty$ and $p=0$
we have a well-defined linear operator
$$
T:\bigoplus\nolimits_p \{E_\lambda:\lambda\in\Lambda \}
  \to 
\bigoplus\nolimits_p \{ F_\lambda:\lambda\in\Lambda \}
:x\mapsto \bigoplus\nolimits_p \{ T_\lambda(x_\lambda):\lambda\in\Lambda \}
$$
which we shall denote by $\bigoplus_p \{T_\lambda:\lambda\in\Lambda \}$. Its
norm equals $\sup_{\lambda\in\Lambda}\Vert T_\lambda\Vert$.

Among different $\bigoplus_p$-sums the $\langle$~$\bigoplus_1$-sums /
$\bigoplus_\infty$-sums~$\rangle$ play a special role in Banach space theory.
The reason is that any family of Banach spaces admits $\langle$~product /
coproduct~$\rangle$ in $\mathbf{Ban}_1$ which in fact is their
$\langle$~$\bigoplus_1$-sum / $\bigoplus_\infty$-sum~$\rangle$. The same
statement holds for $\mathbf{Ban}$ if we restrict ourselves to finite families
of objects [\cite{HelLectAndExOnFuncAn}, chapter 2, section 5]. Obviously, any 
summand in a $\bigoplus_p$-sum is a $1$-complemented subspace in the sum.

We proceed to advanced topics of Banach space theory. Below we shall discuss
several geometric properties of Banach spaces such as the property of being an
$\mathscr{L}_p^g$-space, weak sequential completeness, the Dunford-Pettis
property, the l.u.st.\ property and the approximation property. In what follows,
imitating Banach space geometers, we shall say that a Banach space $E$ contains
$\langle$~an isometric copy / a copy~$\rangle$ of Banach space $F$ if $F$ is
$\langle$~isometrically isomorphic / topologically isomorphic~$\rangle$ to some
closed subspace of $E$. 

Let $1\leq p\leq +\infty$. We say that $E$ is an $\mathscr{L}_{p,C}^g$-space if
for any $\epsilon>0$ and any finite dimensional subspace $F$ of $E$ there exists
a finite dimensional $\ell_p$-space $G$ and two bounded linear operators 
$S:F\to G$, $T:G\to E$ such that $TS|^F=1_F$ and 
$\Vert T\Vert\Vert S\Vert\leq C+\epsilon$. 
If $E$ is an $\mathscr{L}_{p,C}^g$-space for some $C\geq 1$ we
simply say, that $E$ is an $\mathscr{L}_p^g$-space. This definition
[\cite{DefFloTensNorOpId}, definition 23.1] is an improvement of the definition
of $\mathscr{L}_p$-spaces given by Lindenstrauss and Pelczynski in their
pioneering work~\cite{LinPelAbsSumOpInLpSpAndApp}. Clearly, any finite
dimensional Banach space is an $\mathscr{L}_p^g$-space for 
all $1\leq p\leq +\infty$. Any $L_p$-space is an $\mathscr{L}_{p,1}^g$-space
[\cite{DefFloTensNorOpId}, exercise 4.7], but the converse is not true. Any
$c$-complemented subspace of $\mathscr{L}_{p,C}^g$-space is an
$\mathscr{L}_{p,cC}^g$-space [\cite{DefFloTensNorOpId}, corollary 23.2.1(2)]. A
Banach space is an $\mathscr{L}_{p,C}^g$-space iff its dual is an
$\mathscr{L}_{p^*,C}^g$-space [\cite{DefFloTensNorOpId}, corollary 23.2.1(1)].
All $C(K)$-spaces are $\mathscr{L}_{\infty, 1}^g$-spaces
[\cite{DefFloTensNorOpId}, lemma 4.4]. Note that, for a given locally compact
Hausdorff space $S$ the Banach space $C_0(S)$ is complemented in $C(\alpha S)$.
Therefore, $C_0(S)$-spaces are $\mathscr{L}_\infty^g$-spaces too. We will mainly
concern in $\mathscr{L}_1^g$- and $\mathscr{L}_\infty^g$-spaces.

We say that a Banach space $E$ is weakly sequentially complete if for any
sequence ${(x_n)}_{n\in\mathbb{N}}\subset E$ such that
${(f(x_n))}_{n\in\mathbb{N}}\subset\mathbb{C}$ is a Cauchy sequence for 
any $f\in E^*$ there exists a vector $x\in E$ 
such that $\lim_n f(x_n)=f(x)$ for all $f\in E^*$. That is any weakly 
Cauchy sequence converges in the weak topology. A typical example of a weakly 
sequentially complete Banach space is any $L_1$-space
[\cite{WojBanSpForAnalysts}, corollary III.C.14]. This property is preserved by
closed subspaces. A typical example of a Banach space that is not weakly
sequentially complete is $c_0(\mathbb{N})$, just consider the sequence
${(\sum_{k=1}^n \delta_k)}_{n\in\mathbb{N}}$.

Now we proceed to the discussion of the Dunford-Pettis property. A bounded
linear operator $T:E\to F$ is called weakly compact if it maps the unit ball of
$E$ into a relatively weakly compact subset of $F$. A bounded linear operator is
called completely continuous if the image of any weakly compact subset of $E$ is
norm compact in $F$. A Banach space $E$ is said to have the Dunford-Pettis
property if any weakly compact operator from $E$ to any Banach space $F$ is
completely continuous. There is a simple internal characterization
[\cite{KalAlbTopicsBanSpTh}, theorem 5.4.4]: a Banach space $E$ has the
Dunford-Pettis property iff $\lim_n f_n(x_n)=0$ for all sequences
${(x_n)}_{n\in\mathbb{N}}\subset E$ and ${(f_n)}_{n\in\mathbb{N}}\subset E^*$, 
that both weakly converge to $0$. Now it is easy to deduce, 
that if a Banach space $E^*$ has the Dunford-Pettis property, then so does $E$.
In his seminal work~\cite{GrothApllFaiblCompSpCK} Grothendieck showed that all
$L_1$-spaces and $C(K)$-spaces have this property. The Dunford-Pettis property
passes to complemented subspaces [\cite{FabHabBanSpTh}, proposition 13.44]. This
property behaves badly with reflexive spaces: since the unit ball of a reflexive
space is weakly compact [\cite{MeggIntroBanSpTh}, theorem 2.8.2], then reflexive
Banach space with the Dunford-Pettis property has norm compact unit ball and
therefore this space is finite dimensional. 

To introduce the next Banach geometric property we need definitions of Banach
lattice and unconditional Schauder basis. 

A real Riesz space $E$ is a vector space over $\mathbb{R}$ with the structure of
partially ordered set such that $x\leq y$ implies $x+z\leq y+z$ for every
$x,y,z\in E$ and $ax\geq 0$ for every $x\geq 0$, $a\in\mathbb{R}_+$. A partially
ordered set $L$ is a lattice if any two elements $x,y\in L$ have the least upper bound
$x\vee y\in L$ and the greatest lower bound $x\wedge y\in L$. A real vector lattice is
real Riesz space which is a lattice as a partially ordered set. If $E$ is a real
vector lattice, then for every $x\in E$ we define its absolute value by equality
$|x|:=x\vee(-x)$. A complex vector lattice $E$ is a vector space over
$\mathbb{C}$ such that there exists a real vector subspace
$\operatorname{Re}(E)$ called a real part of E, which is a real vector lattice and
\begin{enumerate}[label = (\roman*)]
  \item for any $x\in E$ there are unique
  $\operatorname{Re}(x),\operatorname{Im}(x)\in \operatorname{Re}(E)$ such that
  $x=\operatorname{Re}(x)+i\operatorname{Im}(x)$;

  \item for any $x\in E$ there exists an absolute value $|x|:=\sup
  \{\operatorname{Re}(e^{i\theta}x):\theta\in\mathbb{R} \}$.
\end{enumerate}

A Banach lattice $E$ is a Banach space with the structure of a complex vector
lattice such that $\Vert x\Vert\leq \Vert y\Vert$ whenever $x, y\in E$ 
and $|x|\leq |y|$. A classical example of a Banach lattice is an $L_p$-space 
or a $C(K)$-space. In both cases their real part consists of real 
valued functions. If $ \{E_\lambda:\lambda\in\Lambda \}$ is a family 
of Banach lattices then for any $1\leq p\leq +\infty$ or $p=0$ 
their $\bigoplus_p$-sum is a Banach lattice with lattice operation defined 
as $x\leq y$ if $x_\lambda\leq y_\lambda$ for all $\lambda\in\Lambda$, where 
$x,y\in\bigoplus_p \{ E_\lambda:\lambda\in\Lambda \}$. 
The dual space $E^*$ of a Banach lattice $E$ is again a Banach lattice with
lattice operation defined by $f\leq g$ if $f(x)\leq g(x)$ for all $x\geq 0$,
where $f,g\in  E^*$. A very nice account of Banach lattices can be found in
[\cite{LaceyIsomThOfClassicBanSp}, section 1].

The property of being a Banach lattice puts some restrictions on the geometry of
the space~\cite{SherOrderInOpAlg},~\cite{KadOrderPropOfBoundSAOps}. To explain
the Banach geometric reason of this phenomenon we need the definition of an
unconditional Schauder basis. Let $E$ be a Banach space. A collection of
functionals ${(f_\lambda)}_{\lambda\in\Lambda}\subset E^*$ is called 
a biorthogonal system for vectors ${(x_\lambda)}_{\lambda\in\Lambda}\subset E$ 
if $f_\lambda(x_{\lambda'})=1$ whenever $\lambda=\lambda'$ 
and $0$ otherwise. A collection ${(x_\lambda)}_{\lambda\in\Lambda}\subset E$ 
is called an unconditional Schauder basis if there exists 
a biorthogonal system ${(f_\lambda)}_{\lambda\in\Lambda}\subset E^*$ 
for it such that the series $\sum_{\lambda\in\Lambda} f_\lambda(x)x_\lambda$ 
unconditionally converges to $x$ for any $x\in E$. All $\ell_p$-spaces 
with $1\leq p<+\infty$ have an unconditional Schauder basis, for example, it is
${(\delta_\lambda)}_{\lambda\in\Lambda}$. A typical example of a Banach space without
unconditional basis is $C([0,1])$. Even more this Banach space can not even be a
subspace of the space with unconditional basis [\cite{KalAlbTopicsBanSpTh},
proposition 3.5.4].  Any unconditional Schauder basis
${(x_\lambda)}_{\lambda\in\Lambda}$ in $E$ satisfy the following property
[\cite{DiestAbsSumOps}, proposition 1.6]: there exists a constant $\kappa\geq 1$
such that
$$
\left\Vert \sum_{\lambda\in\Lambda}t_\lambda f_\lambda(x)x_\lambda\right\Vert
\leq
\kappa\left\Vert \sum_{\lambda\in\Lambda}f_\lambda(x)x_\lambda\right\Vert
$$
for all $x\in E$ and $t\in\ell_\infty(\Lambda)$. The least such constant
$\kappa$ among all unconditional Schauder bases of $E$ is denoted by
$\kappa(E)$. Similar constant could be defined for Banach spaces without
unconditional Schauder bases. The local unconditional constant $\kappa_u(E)$ of
Banach space $E$ is defined to be the infimum of all scalars $c$ with the
following property: given any finite dimensional subspace $F$ of $E$ there
exists a Banach space $G$ with unconditional Schauder basis and two bounded
linear operators $S:F\to G$, $T:G\to E$ such that $TS|^{F}=1_F$ and $\Vert
T\Vert\Vert S\Vert\kappa(G)\leq c$. We say that a Banach space $E$ has the local
unconditional structure property (the l.u.st.\ property for short) if
$\kappa_u(E)$ is finite. Clearly any Banach space $E$ with unconditional
Schauder basis has the l.u.st.\ property with $\kappa_u(E)=\kappa(E)$. In
particular, all finite dimensional Banach spaces have the l.u.st.\ property.
Though a general Banach lattice $E$ may not have an unconditional Schauder basis
it still has the l.u.st.\ property with $\kappa_u(E)=1$
[\cite{DiestAbsSumOps}, theorem 17.1]. Directly from the definition it follows
that the l.u.st.\ property is preserved by complemented subspaces. More
precisely: if $F$ is a $c$-complemented subspace of $E$, 
then $\kappa_u(F)\leq c\kappa_u(E)$. 
Therefore, all complemented subspaces of Banach lattices have the
l.u.st. property. This sufficient condition is not far from a criterion
[\cite{DiestAbsSumOps}, theorem 17.5]: a Banach space $E$ has the l.u.st.
property iff $E^{**}$ is topologically isomorphic to a complemented subspace of
some Banach lattice. As the corollary of this criterion we get that $E$ has the
l.u.st.\ property iff so does $E^*$ [\cite{DiestAbsSumOps}, corollary 17.6].

The last property we shall discuss is a well known approximation property
introduced by Grothendieck in~\cite{GrothProdTenTopNucl}. We say that a Banach
space $E$ has the approximation property if for any compact set $K\subset E$ and
any $\epsilon>0$ there exists a finite rank operator $T:E\to E$ such 
that $\Vert T(x)-x\Vert<\epsilon$ for all $x\in K$. If $T$ can be 
chosen with $\Vert T\Vert\leq c$, then $E$ is said to have the $c$-bounded
approximation property. The metric approximation property is another name for
$1$-bounded approximation property. We say that $E$ has the bounded
approximation property if $E$ has the $c$-bounded approximation property for
some $c\geq 1$. None of these properties are preserved by subspaces or quotient
spaces, but the approximation property and the bounded approximation properties
are inherited by complemented subspaces [\cite{DefFloTensNorOpId}, exercise
5.5]. All $L_p$-spaces and $C(K)$-spaces have the metric approximation property
[\cite{DefFloTensNorOpId}, section 5.2(3)], but their subspaces may fail the
approximation property [\cite{DefFloTensNorOpId}, section 5.2(1)]. Any Banach
space with unconditional Schauder basis has the approximation property
[\cite{RyanIntroTensNormsBanSp}, example 4.4]. If $E^*$ has the approximation
property, then so does $E$ [\cite{DefFloTensNorOpId}, corollary 5.7.2]. The
reason why approximation property is so important is rather simple --- it has a
lot of equivalent reformulations that involve many nice properties of Banach
spaces. For example, the following properties of Banach space $E$ are equivalent
[\cite{DefFloTensNorOpId}, sections 5.3, 5.6]:
\begin{enumerate}[label = (\roman*)]
  \item $E$ has the approximation property;

  \item the natural mapping $Gr:E^*\projtens E\to\mathcal{N}(E)$ is an isometric
  isomorphism;

  \item for any Banach space $F$ every compact operator $T:F\to E$ can be
  approximated in the operator norm by finite rank operators.
\end{enumerate}

There is much more to list here, but we confine ourselves with these three
properties.

%-------------------------------------------------------------------------------
%    Banach algebras and their modules
%-------------------------------------------------------------------------------

\subsection{
  Banach algebras and their modules}\label{SubSectionBanachAlgebrasAndTheirModules}

A thorough treatment of Banach algebras and Banach modules can be found
in~\cite{HelBanLocConvAlg} or~\cite{HelHomolBanTopAlg}
or~\cite{DalBanAlgAutCont}. We shall describe only the bare minimum required for
us.

A Banach algebra $A$ is an associative algebra over $\mathbb{C}$ which is a
Banach space and the multiplication bilinear operator 
$\cdot:A\times A\to A:(a,b)\mapsto ab$ is of the norm at most $1$. A typical
example of a commutative Banach algebra is the algebra of continuous functions on
a compact Hausdorff space with pointwise multiplication. A typical non-commutative 
example is the algebra of bounded linear operators on a Hilbert
space with composition in the role of multiplication. Both examples belong to a
very important class of $C^*$-algebras to be discussed below. By $\langle$~left
/ right / two-sided~$\rangle$ ideal $I$ of a Banach algebra $A$ we always mean 
a subalgebra of $A$ such that $\langle$~$ax$ / $xa$ / $ax$ and
$xa$~$\rangle$ belong to $I$ for all $a\in A$ and $x\in I$.

We say that an element $p$ of a Banach algebra $A$ is a $\langle$~left /
right~$\rangle$ identity of $A$ if $\langle$~$pa=a$ / $ap=a$~$\rangle$ for all
$a\in A$. The element which is both left and right identity is called the
identity and denoted by $e_A$. In general, we do not assume that Banach algebras
are unital, i.e.\ has an identity. Even if a Banach algebra $A$ is unital we do
not require its identity to be of norm $1$. We use notation
$A_+=A\bigoplus_1\mathbb{C}$ for the standard unitization of Banach algebras.
The multiplication in $A_+$ is defined as $(a\oplus_1 z)(b\oplus_1
w)=(ab+wa+zb)\oplus_1 zw$, for $a,b\in A$ and $z,w\in\mathbb{C}$. Clearly
$0\oplus_1 1$ is the identity of $A_+$. By $A_\times$ we denote the conditional
unitization of $A$, i.e. $A_\times=A$ if $A$ has identity of norm one and
$A_\times=A_+$ otherwise. Even in the absence of identity in case of Banach
algebras there are good substitutes for it which are called approximate
identities. We say that a net ${(e_\nu)}_{\nu\in N}\subset A$ is a 
$\langle$~left / right / two-sided~$\rangle$ approximate identity if 
$\langle$~$\lim_\nu e_\nu a=a$ / $\lim_\nu ae_\nu=a$ / 
$\lim_\nu e_\nu a=\lim_\nu ae_\nu=a$~$\rangle$ for
all $a\in A$. Here convergence of nets is understood
in the norm topology. If we replace norm topology with weak topology, we get
definitions of left, right and two-sided weak approximate identities. We say
that an approximate identity ${(e_\nu)}_{\nu\in N}$ is $c$-bounded if
$\sup_\nu\Vert e_\nu\Vert\leq c$. An approximate identity ${(e_\nu)}_{\nu\in N}$
is called $\langle$~contractive / bounded~$\rangle$ if it is
$\langle$~$1$-bounded / $c$-bounded for some $c\geq 1$~$\rangle$. Occasionally
we will use the following simple fact: if $A$ is a Banach algebra has a
$\langle$~left / right~$\rangle$ identity $p$ and a $\langle$~right /
left~$\rangle$ approximate identity ${(e_\nu)}_{\nu\in N}$, then $A$ is unital
with identity $p$ of norm $\lim_\nu\Vert e_\nu\Vert$. 

If $A$ is a unital Banach algebra we define the spectrum
$\operatorname{sp}_A(a)$ of element $a\in A$ as the set of all complex numbers
$z$ such that $a-ze_A$ is not invertible in $A$. For Banach algebras the
spectrum of any element is a non-empty compact subset of $\mathbb{C}$
[\cite{HelBanLocConvAlg}, corollary 2.1.16].

A character on a Banach algebra $A$ is a non-zero linear homomorphism
$\varkappa:A\to\mathbb{C}$. All characters are continuous and are contained in
the unit ball of $A^*$  [\cite{HelBanLocConvAlg}, theorem 1.2.6]. Therefore, we
may consider the set of characters with the induced weak$^*$ topology. The
resulting topological space is Hausdorff and locally compact. It is called the
spectrum of the Banach algebra $A$ and denoted by $\operatorname{Spec}(A)$. If $A$
is unital then its spectrum is compact [\cite{HelBanLocConvAlg}, theorem
1.2.50]. Now for a given Banach algebra $A$ with non-empty spectrum we can
construct a contractive homomorphism $\Gamma_A:A\to
C_0(\operatorname{Spec}(A)):a\mapsto(\varkappa\mapsto \varkappa(a))$ called the
Gelfand transform of $A$ [\cite{HelBanLocConvAlg}, theorem 4.2.11]. The kernel
of this homomorphism is called the Jacobson's radical and denoted by
$\operatorname{Rad}(A)$. For a Banach algebra $A$ with empty spectrum we define
$\operatorname{Rad}(A)=A$. If $\operatorname{Rad}(A)= \{0 \}$, then $A$ is
called semisimple. By Shilov's idempotent theorem [\cite{KaniBanAlg}, section
3.5] any semisimple Banach algebra with compact spectrum is unital.

Most standard constructions for Banach spaces have their counterparts for
Banach algebras. For example $\bigoplus_p$-sum of Banach algebras endowed with
componentwise multiplication is a Banach algebra, the quotient of a given Banach
algebra by its closed two-sided ideal is a Banach algebra. Even the projective tensor
product of two Banach algebras is a Banach algebra with multiplication defined
on elementary tensors the same way as in pure algebra.

We shall proceed to the discussion of the most important class of Banach
algebras. Let $A$ be an associative algebra over $\mathbb{C}$, then a conjugate
linear operator ${}^*:A\to A$ is called an involution if ${(ab)}^*=b^*a^*$ and
$a^{**}=a$ for all $a,b\in A$. Algebras with involution are called
${}^*$-algebras. Homomorphisms between ${}^*$-algebras that preserve involution
are called ${}^*$-homomorphisms. A Banach algebra with isometric involution is
called a ${}^*$-Banach algebra. An example of such algebra is the Banach algebra
of bounded linear operators on a Hilbert space with operation of taking the
Hilbert adjoint operator in the role of involution. In fact there is much more
to this algebra than one could expect. We say that a ${}^*$-Banach algebra $A$
is a $C^*$-algebra if it satisfies $\Vert a^*a\Vert=\Vert a\Vert^2$ for all
$a\in A$. One of the biggest advantages of $C^*$-algebras is their celebrated
representation theorems by Gelfand and Naimark. The first representation theorem
[\cite{HelBanLocConvAlg}, theorem 4.7.13] states that any commutative
$C^*$-algebra $A$ is isometrically isomorphic as ${}^*$-algebra to
$C_0(\operatorname{Spec}(A))$. The second theorem [\cite{HelBanLocConvAlg},
theorem 4.7.57] gives a description of generic $C^*$-algebras as closed
${}^*$-Banach subalgebras of $\mathcal{B}(H)$ for some Hilbert space $H$. Such
representation is not unique, but a norm (if it exists) that turn a
${}^*$-algebra into a $C^*$-algebra is always unique. If a ${}^*$-subalgebra of
$\mathcal{B}(H)$ is weak${}^*$ closed it is called a von Neumann algebra. If a
$C^*$-algebra is isomorphic as ${}^*$-algebra to a von Neumann algebra, then it is
called a $W^*$-algebra. By well known Sakai's theorem [\cite{BlackadarOpAlg},
theorem III.2.4.2] each $C^*$-algebra which is dual as Banach space is a
$W^*$-algebra, but beware a $W^*$-algebra may be represented as non weak${}^*$
closed ${}^*$-subalgebra in $\mathcal{B}(H)$ for some Hilbert space $H$. 

Till the end of this paragraph we assume that $A$ is a unital $C^*$-algebra. 
An element $a\in A$ is called a projection (or an orthogonal projection) 
if $a=a^*=a^2$, self-adjoint if $a=a^*$, positive if $a=b^*b$ for 
some $b\in A$, unitary if $a^*a=aa^*=e_A$. The set $A_{pos}$ of all positive 
elements of $A$ is a closed cone in $A$. If an element $a\in A$ 
is $\langle$~self-adjoint / positive~$\rangle$, then
$\langle$~$\operatorname{sp}_A(a)\subset[-\Vert a\Vert, \Vert a\Vert]$ /
$\operatorname{sp}_A(a)\subset[0,\Vert a\Vert]$~$\rangle$. For a given
self-adjoint element $a\in A$, there always exists the isometric
${}^*$-homomorphism $\operatorname{Cont}_a:C(\operatorname{sp}_A(a))\to A$ such
that $\operatorname{Cont}_a(f)=a$, where
$f:\operatorname{sp}_A(a)\to\mathbb{C},\, t\mapsto t$. It is called the continuous
functional calculus [\cite{HelBanLocConvAlg}, theorem 4.7.24]. Loosely speaking
it allows taking continuous functions of self-adjoint elements of
$C^*$-algebras, so following standard convention we shall write $f(a)$ instead
of $\operatorname{Cont}_a(f)$. Another related result called the spectral
mapping theorem allows to compute the spectrum of elements given by continuous
functional calculus: $\operatorname{sp}_A(f(a))=f(\operatorname{sp}_A(a))$.

A lot of standard constructions pass to $C^*$-algebras from Banach algebras, but
not all. For example a $\bigoplus_\infty$-sum of $C^*$-algebras is again a
$C^*$-algebra. A quotient of $C^*$-algebra by a closed two-sided ideal is a
$C^*$-algebra too. Meanwhile, the projective tensor product of $C^*$-algebras is
rarely a $C^*$-algebra, though there are a lot of norms that may turn their
algebraic tensor product into a $C^*$-algebra. In this book we shall exploit one
specific and highly important construction for $C^*$-algebras --- the matrix
algebras. For a given $C^*$-algebra $A$ by $M_n(A)$ we denote the linear space
of $n\times n$ matrices with entries in $A$. In fact $M_n(A)$ is a ${}^*$-algebra
with involution and multiplication defined by equalities 
$$
{(ab)}_{i,j}=\sum_{k=1}^n a_{i,k}b_{k,j}
\qquad\qquad
{(a^*)}_{i,j}=(a_{j,i}^*)
$$ 
for all $a,b\in M_n(A)$ and $i,j\in\mathbb{N}_n$. There is a unique norm on
$M_n(A)$ that makes it a $C^*$-algebra [\cite{MurphyCStarAlgsAndOpTh}, theorem
3.4.2]. Obviously, $M_n(\mathbb{C})$ is isometrically isomorphic as
${}^*$-algebra to $\mathcal{B}(\ell_2(\mathbb{N}_n))$. From
[\cite{MurphyCStarAlgsAndOpTh}, remark 3.4.1] it follows that the natural
embeddings 
$i_{k,l}:A\to M_n(A):a\mapsto{(a\delta_{i,k}\delta_{j,l})}_{i,j\in\mathbb{N}_n}$
and projections
$\pi_{k,l}:M_n(A)\to A:a\mapsto a_{k,l}$ are continuous. Therefore, for a given
bounded linear operator $\phi:A\to B$ between $C^*$-algebras $A$ and $B$ the
linear operator 
$$
M_n(\phi):M_n(A)\to M_n(B),\, a\mapsto {(\phi(a_{i,j}))}_{i,j\in\mathbb{N}_n}
$$ 
is also bounded. Even more if $\phi$ is an $A$-morphism or ${}^*$-homomorphism,
then so does $M_n(\phi)$. Finally, we shall mention two isometric isomorphisms
that will be of use:
$$
M_n\left(\bigoplus\nolimits_\infty \{A_\lambda:\lambda\in\Lambda \}\right)
\isom{\mathbf{Ban}_1}
\bigoplus\nolimits_\infty \{M_n\left(A_\lambda\right):\lambda\in\Lambda \},
$$
$$
M_n(C(K))\isom{\mathbf{Ban}_1}C(K,M_n(\mathbb{C}))
$$

Now a few facts on approximate identities and identities of $C^*$-algebras and
their ideals. Any closed two-sided ideal of a $C^*$-algebra has a two-sided
contractive positive approximate identity [\cite{HelBanLocConvAlg}, theorem
4.7.79], and any closed left ideal has a right contractive positive approximate
identity. In some cases even an approximate identity is not enough, so for this
situation there is a procedure to endow a $C^*$-algebra with identity and
preserve $C^*$-algebraic structure [\cite{HelBanLocConvAlg}, proposition 4.7.6].
This type of unitization we shall denote as $A_\#$. 

We proceed to the discussion of more general objects --- Banach modules. Let $A$
be a Banach algebra, we say that $X$ is a $\langle$~left / right~$\rangle$
Banach $A$-module if $X$ is a Banach space endowed with bilinear operator
$\langle$~$\cdot:A\times X\to X$ / $\cdot: X\times A\to X$~$\rangle$ of norm at
most $1$ (called a module action), such that 
$\langle$~$a\cdot(b\cdot x)=ab\cdot x$ / 
$(x\cdot a)\cdot b=x\cdot ab$~$\rangle$ for all $a,b\in A$ and $x\in X$.
Any Banach space $E$ can be turned into a $\langle$~left / right~$\rangle$
Banach $A$-module be defining $\langle$~$a\cdot x=0$ / $x\cdot a=0$~$\rangle$
for all $a\in A$ and $x\in E$. Any Banach algebra $A$ can be regarded as a left
and right Banach $A$-module --- the module action coincides with algebra
multiplication. Of course, there are more meaningful examples too.  Usually we
shall discuss only left Banach modules since for their right sided counterparts
all definitions and results are similar. We call a left Banach module $X$ over a 
unital Banach algebra $A$ unital if $e_A\cdot x=x$ for all $x\in X$. 

Let $X$ and $Y$ be two $\langle$~left / right~$\rangle$ Banach $A$-modules. We say
that a linear operator $\phi:X\to Y$ is an $A$-module map of $\langle$~left /
right~$\rangle$ modules if $\langle$~$\phi(a\cdot x)=a\cdot \phi(x)$ /
$\phi(x\cdot a)=\phi(x)\cdot a$~$\rangle$ for all $a\in A$ and $x\in X$. A
bounded $A$-module map is called an $A$-morphism. The set of $A$-morphisms
between $\langle$~left / right~$\rangle$ $A$-modules $X$ and $Y$ we denote as
$\langle$~${}_A\mathcal{B}(X,Y)$ / $\mathcal{B}_A(X,Y)$~$\rangle$. Note that if
$X$ and $Y$ are $\langle$~left / right~$\rangle$ annihilator $A$-modules, then
$\langle$~${}_A\mathcal{B}(X,Y)=\mathcal{B}(X,Y)$ /
$\mathcal{B}_A(X,Y)=\mathcal{B}(X,Y)$~$\rangle$.

If $X$ is a left Banach $A$-module and $E$ is a
Banach space, then $\langle$~$\mathcal{B}(X,E)$ / $\mathcal{B}(E,X)$~$\rangle$
is a $\langle$~right / left~$\rangle$ Banach $A$-module with module action
defined by $\langle$~$(T\cdot a)(x)=T(a\cdot x)$ for all $a\in A$, $x\in X$ and
$T\in\mathcal{B}(X, E)$ / $(a\cdot T)(x)=a\cdot T(x)$ for all $a\in A$, $x\in E$
and $T\in\mathcal{B}(E, X)$~$\rangle$. In particular, $X^*$ is a right Banach
$A$-module.

By $\langle A-\mathbf{mod}$ / $\mathbf{mod}-A\rangle$ we shall denote the
category of $\langle$~left / right~$\rangle$ $A$-modules with continuous
$A$-module maps in the role of morphisms. By $\langle$~$A-\mathbf{mod}_1$ /
$\mathbf{mod}_1-A$~$\rangle$ we denote its subcategory of
$\langle$~$A-\mathbf{mod}$ / $\mathbf{mod}-A$~$\rangle$ with the same objects
and contractive morphisms only. Therefore,
$\langle$~$\operatorname{Hom}_{A-\mathbf{mod}}(X,Y)={}_A\mathcal{B}(X,Y)$ /
$\operatorname{Hom}_{\mathbf{mod}-A}(X,Y)=\mathcal{B}_A(X,Y)$~$\rangle$. 

For a given left Banach $A$-module $X$ and $S\subset A$, $M\subset X$ we define 
their products $S\cdot M= \{a\cdot x:a\in S, x\in M \}$, 
$SM=\operatorname{span} (S\cdot M)$ and algebraic annihilators 
$$
S^{\perp M}= \{a\in S:a\cdot M= \{0 \} \},
\qquad\qquad
{}^{S\perp}M= \{x\in M: S\cdot x= \{0 \} \}.
$$ 
The essential and annihilator
parts of $X$ are defined as $X_{ess}=\operatorname{cl}_X(A X)$,
$X_{ann}={}^{A\perp}X$. The module $X$ is called $\langle$~faithful /
annihilator / essential~$\rangle$ if $\langle$~${}^{A\perp}X= \{0 \}$ /
$X=X_{ann}$ / $X=X_{ess}$~$\rangle$. Clearly, 
${(X^*)}^{\perp S}={\operatorname{cl}_X(S X)}^\perp$. Setting $S=A$ we get that 
$X$ is an essential $A$-module iff $X^*$ is a faithful $A$-module.

As in any category we can speak of retraction and coretractions in the
category of Banach modules. But for this particular case we have several
refinements for standard definitions. An $A$-morphism $\xi:X\to Y$ is called
a $\langle$~$c$-retraction / $c$-coretraction~$\rangle$ if there exists an
$A$-morphism $\eta:Y\to X$ such that $\langle$~$\xi\eta=1_Y$ /
$\eta\xi=1_X$~$\rangle$ and $\Vert\xi\Vert\Vert\eta\Vert\leq c$. From the
definition it follows that composition of $\langle$~$c_1$- and $c_2$-retraction
/ $c_1$- and $c_2$-coretraction~$\rangle$ gives a $\langle$~$c_1c_2$-retraction
/ $c_1c_2$-coretraction~$\rangle$. Clearly, the adjoint of
$\langle$~$c$-retraction / $c$-coretraction~$\rangle$ is a
$\langle$~$c$-coretraction / $c$-retraction~$\rangle$. Finally, an $A$-morphism
$\xi:X\to Y$ is called a $c$-isomorphism if there exists an $A$-morphism
$\eta:Y\to X$ such that $\xi\eta=1_Y$, $\eta\xi=1_X$ and
$\Vert\xi\Vert\Vert\eta\Vert\leq c$. In this case we say that $A$-modules $X$
and $Y$ are $c$-isomorphic.

Now we mention several constructions over Banach modules that we will encounter
in this book.  Any left Banach $A$-module can be regarded as a unital Banach
module over $A_+$, and we put by definition $(a\oplus_1 z)\cdot x=a\cdot x+zx$
for all $a\in A$, $x\in X$ and $z\in\mathbb{C}$. Most constructions used for
Banach spaces transfer to Banach modules.  We say that a linear subspace $ Y$ of
a left Banach $A$-module $X$ is a left $A$-submodule of $X$ 
if $A\cdot Y\subset Y$. For example, any closed left ideal $I$ of a 
Banach algebra $A$ is a left $A$-submodule of $A$. If $Y$ is a closed left
$A$-submodule of a left Banach $A$-module $X$, then the Banach space $X/Y$ can
be endowed with the structure of the left Banach $A$-module, just put by
definition $a\cdot(x+Y)=a\cdot x+Y$ for all $a\in A$ and $x+Y\in X/Y$. This
object is called the quotient $A$-module. Quotient modules of the form $A/I$,
where $I$ is a closed left ideal of $A$, are called cyclic modules. For motivation for
this term see [\cite{HelBanLocConvAlg}, proposition 6.2.2]. Clearly, $X/X_{ess}$
is an annihilator $A$-module. If $ \{X_\lambda:\lambda\in\Lambda \}$ is a family of left Banach
$A$-modules and $1\leq p\leq +\infty$ or $p=0$, then their $\bigoplus_p$-sum is
a left Banach $A$-module with module action defined 
by $a\cdot x:=\bigoplus_p \{a\cdot x_\lambda:\lambda\in\Lambda \}$, 
where $a\in A$, $x\in\bigoplus_p \{X_\lambda:\lambda\in\Lambda \}$. 
Again, as in Banach space theory, any family
of $A$-modules admits the $\langle$~product / coproduct~$\rangle$ in
$A-\mathbf{mod}_1$ which in fact is their $\langle$~$\bigoplus_1$-sum /
$\bigoplus_\infty$-sum~$\rangle$. The category $A-\mathbf{mod}$ admits
$\langle$~products / coproducts~$\rangle$ only for finite families of objects.
Similar statements are valid for $\mathbf{mod}-A$ and $\mathbf{mod}_1-A$.

The projective tensor product of Banach spaces also has its module version, it is
called the projective module tensor product. Assume $X$ is a right and $Y$ is a
left Banach $A$-module. Their projective module tensor product
$X\projmodtens{A}Y$ is defined as a quotient space $X\projtens Y / N$ where
$N
=\operatorname{cl}_{X\projtens Y}(\operatorname{span} \{
  x\cdot a\projtens y-x\projtens a\cdot y
  :x\in X,y\in Y,a\in A
 \})$. 
Let $\phi\in\mathcal{B}_A(X_1,X_2)$ and $\psi\in{}_A\mathcal{B}(Y_1,Y_2)$ 
for right Banach $A$-modules $X_1$, $X_2$ and left 
Banach $A$-modules $Y_1$, $Y_2$, then there exists a unique bounded 
linear operator 
$$
\phi\projmodtens{A} \psi:X_1\projmodtens{A} Y_1\to X_2\projmodtens{A} Y_2
$$ 
such that
$(\phi\projmodtens{A} \psi)(x\projmodtens{A} y)=\phi(x)\projmodtens{A} \psi(y)$
for all $x\in X_1$ and $y\in Y_1$. Even more 
$\Vert \phi\projmodtens{A} \psi\Vert\leq\Vert \phi\Vert\Vert \psi\Vert$. 
The projective module tensor product has its own universal property: for any
right Banach $A$-module $X$, any left Banach $A$-module $Y$ and any Banach space
$E$ there exists an isometric isomorphism:
$$
\mathcal{B}(X\projmodtens{A}Y,E)
\isom{\mathbf{Ban}_1}
\mathcal{B}_{bal}(X\times Y, E)
$$
where $\mathcal{B}_{bal}(X\times Y, E)$ stands for the Banach space of bilinear
operators $\Phi:X\times Y\to E$ satisfying $\Phi(x\cdot a,y)=\Phi(x,a\cdot y)$
for all $x\in X$, $y\in Y$ and $a\in A$. Such bilinear operators are called
balanced. Furthermore, we have two (natural in $X$, $Y$ and $E$) isometric
isomorphisms:
$$
\mathcal{B}(X\projmodtens{A}Y,E)
\isom{\mathbf{Ban}_1}
{}_A\mathcal{B}(Y,\mathcal{B}(X,E))
\isom{\mathbf{Ban}_1}
\mathcal{B}_A(X,\mathcal{B}(Y,E))
$$
Analogously to Banach space theory we may define the following functors:
$$
\mathcal{B}(-,E):A-\mathbf{mod}\to \mathbf{mod}-A
\qquad\qquad
\mathcal{B}(E,-):\mathbf{mod}-A\to \mathbf{mod}-A
$$
$$
-\projmodtens{A} Y:\mathbf{mod}-A\to\mathbf{Ban}
\qquad\qquad
X\projmodtens{A} -:A-\mathbf{mod}\to\mathbf{Ban}
$$
where $E$ is a Banach space, $X$ is a right $A$-module and $Y$ is a left
$A$-module. All these functors have their counterparts for categories
$A-\mathbf{mod}_1$, $\mathbf{mod}_1-A$. 

In some cases it is possible to explicitly compute the projective module tensor
product. For example [\cite{HelBanLocConvAlg}, proposition 6.3.24], if $A$ is a 
Banach algebra and $I$ is a closed left ideal of $A_+$ with 
left $\langle$~contractive / bounded~$\rangle$ approximate identity, and $X$ is 
a left Banach $A$-module then the linear operator 
$$
i_{I,X}
:I\projmodtens{A}X \to \operatorname{cl}_X(IX)
:a\projmodtens{A} x\mapsto a\cdot x
$$
is $\langle$~a topological isomorphism / an isometric isomorphism~$\rangle$ of
Banach spaces. If $I$ is a closed two-sided ideal, then $i_{I,X}$ is a morphism of left
$A$-modules. We call reduced all left Banach modules of the form
$A\projmodtens{A}X$. 

Most of what have been said here can be generalized to Banach bimodules, but in
this book we shall not exploit them much. In those rare case when we shall
encounter bimodules, the respective definitions and results are easily
recoverable from their one-sided counterparts.

%-------------------------------------------------------------------------------
%    Banach homology
%-------------------------------------------------------------------------------

\section{
  Banach homology}\label{SectionBanachHomology}

%-------------------------------------------------------------------------------
%    Relative homology
%-------------------------------------------------------------------------------

\subsection{
  Relative homology}\label{SubSectionRelativeHomology}

Further we briefly discuss ABCs of so-called relative homology introduced and intensively
studied by Helemskii. In this text we shall use a bit more involved
definition given by White in~\cite{WhiteInjmoduAlg}, though it is equivalent to the one
given by Helemskii. Fix an arbitrary Banach algebra $A$. We say that a
morphism $\xi:X\to Y$ of left $A$-modules $X$ and $Y$ is a $c$-relatively 
admissible epimorphism if it admits a right inverse bounded linear operator of 
the norm at most $c$. A left $A$-module $P$ is called $C$-relatively projective 
if for any $c$-relatively admissible epimorphism $\xi:X\to Y$ and 
for any  $A$-morphism $\phi:P\to Y$ there exists 
an $A$-morphism $\psi:P\to X$ such 
that $\Vert \psi\Vert\leq cC\Vert \phi\Vert$ and the diagram
$$
\xymatrix{
& {X} \ar[d]^{\xi}\\  % chktex 3
{P} \ar@{-->}[ur]^{\psi} \ar[r]^{\phi} &{Y}}  % chktex 3
$$
is commutative. Such $A$-morphism $\psi$ is called a lifting of $\phi$, and it is
not unique in general. Similarly,  we say that a morphism $\xi:Y\to X$ of right
$A$-modules $X$ and $Y$ is a $c$-relatively admissible monomorphism if it admits
a left inverse bounded linear operator of the norm at most $c$. A right 
$A$-module $J$ is called $C$-relatively injective if for any $c$-relatively 
admissible monomorphism $\xi:Y\to X$ and for 
any $A$-morphism $\phi:Y\to J$ there exists an $A$-morphism $\psi:X\to J$ such 
that $\Vert\psi\Vert\leq cC\Vert\phi\Vert$ and the diagram
$$
\xymatrix{
& {X} \ar@{-->}[dl]_{\psi} \\  % chktex 3
{J} &{Y} \ar[l]_{\phi} \ar[u]_{\xi}}  % chktex 3
$$
is commutative. Such $A$-morphism $\psi$ is called an extension of $\phi$, and it
is not unique in general.

Another closely related homological property is flatness. A
left $A$-module $F$ is called $C$-relatively flat if for each
$c$-relatively admissible monomorphism $\xi:X\to Y$ the operator 
$\xi\projmodtens{A} 1_F:X\projmodtens{A} F\to Y\projmodtens{A} F$ is
$cC$-topologically injective. A left $A$-module $F$ is $C$-relatively flat iff
$F^*$ is $C$-relatively injective. 

We say that an $A$-morphism is relatively admissible if it is $c$-relatively 
admissible for some $c\geq 1$. Similarly, we say that an $A$-module $X$ is 
relatively $\langle$~projective / injective / flat~$\rangle$ if it is  
$C$-relatively $\langle$~projective / injective / flat~$\rangle$ for 
some $C\geq 1$.

The reason for considering relatively admissible morphisms in these definitions
is the intention to separate Banach geometric and algebraic properties of a 
Banach module that may prevent it to be relatively projective, injective or flat. 
A straightforward check shows that any $c$-retract of a 
$C$-relatively $\langle$~projective / injective / flat~$\rangle$ $A$-module is 
again $cC$-relatively $\langle$~projective / injective / flat~$\rangle$. 
Obviously, any $c$-relatively admissible $\langle$~epimorphism
/ monomorphism~$\rangle$ $\langle$~onto / from~$\rangle$ a $C$-relatively
$\langle$~projective / injective~$\rangle$ $A$-module is a 
$\langle$~$cC$-retraction / $cC$-coretraction~$\rangle$.

A special class of relatively $\langle$~projective / injective~$\rangle$
$A$-modules is the class of so-called 
relatively $\langle$~free / cofree~$\rangle$ modules. 
These are modules of the form $\langle$~$A_+\projtens E$ /
$\mathcal{B}(A_+,E)$~$\rangle$ for some Banach space $E$. Their main feature is
the following: for any $A$-module $X$ there exists a relatively $\langle$~free /
cofree~$\rangle$ $A$-module $F$, which in fact is $\langle$~$A_+\projtens X$ /
$\mathcal{B}(A_+,X)$~$\rangle$ and a $1$-relatively admissible 
$\langle$~epimorphism $\xi:F\to X$ / monomorphism $\xi:X\to F$~$\rangle$. 
If $X$ is $C$-relatively
$\langle$~projective / injective~$\rangle$ then we immediately get that $\xi$ is a
$\langle$~$C$-retraction / $C$-coretraction~$\rangle$. Therefore, an $A$-module 
is $C$-relatively $\langle$~projective / injective~$\rangle$ iff it is 
a $C$-retract of relatively $\langle$~free / cofree~$\rangle$ $A$-module. 

It is worth emphasizing one more time that the major nuance of relative Banach
homology is a balance between algebra and topology in the choice of
admissible morphisms. This choice allows one to build a homological theory with
some interesting phenomena and with no analogs in pure algebra. We demonstrate an
example related to Banach algebras. For a given Banach algebra define an $A$-morphism 
of $A$-bimodules $\Pi_A:A\projtens A\to A:a\projtens b\mapsto ab$. We say 
that a Banach algebra $A$ is 
\begin{enumerate}[label = (\roman*)]
  \item $c$-relatively biprojective if $\Pi_A$ is a $c$-retraction of
  $A$-bimodules;

  \item $c$-relatively biflat if $\Pi_A^*$ is a $c$-coretraction of 
  $A$-bimodules;

  \item $c$-relatively contractible if $\Pi_{A_+}$ is a $c$-retraction of
  $A$-bimodules;

  \item $c$-relatively amenable if $\Pi_{A_+}^*$ is a $c$-coretraction of
  $A$-bimodules.
\end{enumerate}

We say that $A$ is relatively $\langle$~biprojective / biflat / contractive /
amenable~$\rangle$ if it is $c$-relatively $\langle$~biprojective / biflat /
contractive / amenable~$\rangle$ for some $c\geq 1$. The infimum of the
constants $c$ is called the $\langle$~biprojectivity / biflatness /
contractivity / amenability~$\rangle$ constant.  With slight modifications of
[\cite{HelBanLocConvAlg}, proposition 7.1.72] one can show that $A$ is
$c$-relatively $\langle$~contractible / amenable~$\rangle$ iff there exists
$\langle$~an element $d\in A\projtens A$ / a net 
${(d_\nu)}_{\nu\in N}\subset A\projtens A$~$\rangle$ with 
norm not greater than $c$ such that for all $a\in A$ holds 
$\langle$~$a\cdot d-d\cdot a=0$ and $a\Pi_A(d)=a$ / 
$\lim_\nu(a\cdot d_\nu-d_\nu\cdot a)=0$ 
and $\lim_\nu a\Pi_A(d_\nu)=a$~$\rangle$. Note that 
$\langle$~such element $d$ / such net ${(d_\nu)}_{\nu\in N}$~$\rangle$ is called
$\langle$~a diagonal / an approximate diagonal~$\rangle$. From homological point
of view, the main advantage of relatively $\langle$~biprojective / biflat /
contractible / amenable~$\rangle$ Banach algebras is that $\langle$~any reduced
/ any reduced / any / any~$\rangle$ left and right Banach $A$-module is
relatively $\langle$~projective / flat / projective / flat~$\rangle$
[\cite{HelBanLocConvAlg}, theorem 7.1.60]. As for flatness such phenomena is
typical for relative Banach homology, but not for the purely algebraic one.
