% chktex-file 35
% Chapter Template
% Main chapter title
% Change X to a consecutive number; for referencing this 
% chapter elsewhere, use~\ref{ChapterX}
\chapter{
    Applications to algebras of analysis}\label{ChapterApplicationsToAlgebrasOfAnalysis} 

% Change X to a consecutive number; this is for the header on 
% each page - perhaps a shortened title
\lhead{Chapter 3. \emph{Applications to algebras of analysis}} 

Vaguely speaking there are three types of Banach modules depending on the type
of module action: modules with pointwise multiplication, modules with
composition of operators in the role of module action and modules with
convolution. We shall investigate main examples of these types. Following the
style of Dales and Polyakov from~\cite{DalPolHomolPropGrAlg} we shall
systematize all results on classical modules of analysis, but this time for
metric and topological theory. We shall consider modules over operator algebras,
sequence algebras, algebras of continuous functions and, finally, over classical
modules of harmonic analysis.


%-------------------------------------------------------------------------------
%	Applications to operator algebras
%-------------------------------------------------------------------------------

\section{
    Applications to modules over \texorpdfstring{$C^*$}{C*}-algebras}\label{
SectionApplicationsToModulesOverCStarAlgebras}

%-------------------------------------------------------------------------------
%	Spatial modules
%-------------------------------------------------------------------------------

\subsection{
    Spatial modules}\label{SubSectionSpatialModules}

We start from the simplest  examples of modules over operator algebras --- the
spatial modules. By Gelfand-Naimark's theorem (see e.g.
[\cite{HelBanLocConvAlg}, theorem 4.7.57]) for any $C^*$-algebra $A$ there
exists a Hilbert space $H$ and an isometric ${}^*$-homomorphism
$\varrho:A\to\mathcal{B}(H)$. For Hilbert spaces that admit such homomorphism we
may consider the left $A$-module $H_\varrho$ with module action defined as
$a\cdot x=\varrho(a)(x)$. Automatically we get the structure of right $A$-module
on $H^*$ which is by Riesz's theorem is isometrically isomorphic to $H^{cc}$.
This isomorphism allows one to define a right $A$-module structure on $H^{cc}$
by $\overline{x}\cdot a=\overline{\varrho(a^*)(x)}$. For a given $x_1,x_2\in H$
we define a rank one operator 
$x_1\bigcirc x_2:H\to H:x\mapsto \langle x, x_2\rangle x_1$. 

\begin{proposition}\label{SpatModOverCStarAlgProp} Let $A$ be a $C^*$-algebra
and $\varrho:A\to\mathcal{B}(H)$ be an isometric ${}^*$-homomorphism, such that
its image contains a subspace of rank one operators of the 
form $ \{x\bigcirc x_0:x\in H \}$ for some non-zero $x_0\in H$. 
Then the left $A$-module $H_\varrho$ is metrically projective and flat, 
while the  right $A$-module $H_\varrho^{cc}$ is metrically injective.
\end{proposition}
\begin{proof} Without loss of generality we may assume that $\Vert x_0\Vert=1$.
Consider linear operators 
$\pi:A_+\to H_\varrho:a\oplus_1 z\mapsto \varrho(a)(x_0)+zx_0$ 
and $\sigma:H_\varrho\to A_+:x\mapsto \varrho^{-1}(x\bigcirc x_0)$. 
It is straightforward to check that $\pi$ and
$\sigma$ are contractive $A$-morphisms such that $\pi\sigma=1_{H_\varrho}$.
Therefore, $H_\varrho$ is a retract of $A_+$ in $A-\mathbf{mod}_1$. From
propositions~\ref{UnitalAlgIsMetTopProj} and~\ref{RetrMetCTopProjIsMetCTopProj} 
it follows that $H_\varrho$ is a metrically projective $A$-module. From
proposition~\ref{MetTopProjIsMetTopFlat} it follows that $H_\varrho$ is
metrically flat too. Since $H_\varrho^{cc}\isom{\mathbf{mod}_1-A}H_\varrho^*$,
proposition~\ref{DualMetTopProjIsMetrInj} gives that $H_\varrho^{cc}$ is
metrically injective.
\end{proof}

In what follows we shall use the following simple application of the above
result.

\begin{proposition}\label{FinDimNHModTopProjFlat} Let $H$ be a finite
dimensional Hilbert space. Then $\mathcal{N}(H)$ is topologically projective and
hence flat as $\mathcal{B}(H)$-module.
\end{proposition}
\begin{proof} From [\cite{HelBanLocConvAlg}, proposition 0.3.38] we know that
$\mathcal{N}(H)\isom{\mathbf{Ban}_1}H\projtens H^*$. Let
$\varrho=1_{\mathcal{B}(H)}$, then we can claim a bit more:
$\mathcal{N}(H)\isom{\mathcal{B}(H)-\mathbf{mod}_1} H_\varrho\projtens H^*$.
Since $H^*$ is finite dimensional, then
$H^*\isom{\mathbf{Ban}}\ell_1(\mathbb{N}_n)$ for $n=\dim(H)$ and as a result
$\mathcal{N}(H)\isom{\mathcal{B}(H)-\mathbf{mod}}
H_\varrho\projtens\ell_1(\mathbb{N}_n)$. By
proposition~\ref{SpatModOverCStarAlgProp} the module $H_\varrho$ it
topologically projective, so from corollary~\ref{MetTopProjTensProdWithl1} we
get that $\mathcal{N}(H)$ is topologically projective as
$\mathcal{B}(H)$-module. The last claim of the theorem follows from
proposition~\ref{MetTopProjIsMetTopFlat}.
\end{proof}

%-------------------------------------------------------------------------------
%	Projective ideals of C^*-algebras
%-------------------------------------------------------------------------------

\subsection{
    Projective ideals of \texorpdfstring{$C^*$}{C*}-algebras}\label{
SubSectionProjectiveIdealsOfCStarAlgebras}

We start the study of homologically trivial closed ideals of $C^*$-algebras from
projectivity, but before stating the main result we need a preparatory lemma.

\begin{lemma}\label{ContFuncCalcOnIdealOfCStarAlg} Let $I$ be a closed left ideal of a
unital $C^*$-algebra $A$. Assume $a\in I$ is a self-adjoint element and let $E$
be the real subspace of real valued functions in $C(\operatorname{sp}_A(a))$
vanishing at zero. Then there is an isometric homomorphism
$\operatorname{RCont}_a^0:E\to I$ well-defined by
$\operatorname{RCont}_a^0(f)=a$, where
$f:\operatorname{sp}_A(a)\to\mathbb{C}:t\mapsto t$.
\end{lemma}
\begin{proof} By $\mathbb{R}_0[t]$ we denote the real linear subspace of $E$
consisting of polynomials vanishing at zero. Since $I$ is an ideal of $A$ and
any $p\in\mathbb{R}_0[t]$ has no constant term then $p(a)\in I$.  Hence, we have 
a well-defined $\mathbb{R}$-linear homomorphism of algebras
$\operatorname{RPol}_a^0:\mathbb{R}_0[t]\to I:p\mapsto p(a)$. By continuous
functional calculus for any polynomial $p$ 
holds $\Vert p(a)\Vert=\Vert p|_{\operatorname{sp}_A(a)}\Vert_\infty$, so
$\Vert\operatorname{RPol}_a^0(p)\Vert
=\Vert p|_{\operatorname{sp}_A(a)}\Vert_\infty$. 
Thus, $\operatorname{RPol}_a^0$ is isometric. 
As $\mathbb{R}_0[t]$ is dense in $E$ and $I$ is complete, then
$\operatorname{RPol}_a^0$ has an isometric extension
$\operatorname{RCont}_a^0:E\to I$ which is also an $\mathbb{R}$-linear
homomorphism. 
\end{proof}

The following proof is inspired by ideas of Blecher and Kania. In
[\cite{BleKanFinGenCStarAlgHilbMod}, lemma 2.1] they proved that any
algebraically finitely generated left ideal of $C^*$-algebras is principal.  

\begin{theorem}\label{LeftIdealOfCStarAlgMetTopProjCharac} Let $I$ be a closed left
ideal of a $C^*$-algebra $A$. Then the following are equivalent:

\begin{enumerate}[label = (\roman*)]
    \item $I=Ap$ for some self-adjoint idempotent $p\in I$;

    \item $I$ is a metrically projective $A$-module;

    \item $I$ is a topologically projective $A$-module.
\end{enumerate}
\end{theorem}
\begin{proof} $(i)\implies (ii)$ Since $p$ is a self-adjoint idempotent, then
$\Vert p\Vert=1$, so by proposition~\ref{UnIdeallIsMetTopProj} paragraph $(i)$
the ideal $I$ is metrically projective as $A$-module.

$(ii)\implies (iii)$ See
proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj}.

$(iii) \implies (i)$ Let ${(e_\nu)}_{\nu\in N}$ be a right contractive
approximate identity of the ideal $I$ [\cite{HelBanLocConvAlg}, theorem 4.7.79].
Since $I$ admits a right approximate identity, then it is an essential left
$I$-module, and a fortiori an essential $A$-module. By
proposition~\ref{NonDegenMetTopProjCharac} we have a right inverse $A$-morphism
$\sigma:I\to A\projtens \ell_1(B_I)$ of $\pi_I$ in $A-\mathbf{mod}$. For each
$d\in B_I$ consider $A$-morphisms $\sigma_d=p_d\sigma$, where 
$p_d:A\projtens \ell_1(B_I)\to A$ is well-defined 
by $p_d(a\projtens \delta_x)=\delta_x(d)a$ for all $a\in A$, $x\in B_I$. Then
$\sigma(x)=\sum_{d\in B_I}\sigma_d(x)\projtens \delta_d$ for all $x\in I$. From
identification 
$A\projtens\ell_1(B_I)\isom{\mathbf{Ban}_1}\bigoplus_1 \{ A:d\in B_I \}$, 
for all $x\in I$ we 
have $\Vert\sigma(x)\Vert=\sum_{d\in B_I} \Vert\sigma_d(x)\Vert$. 
Since $\sigma$ is a right inverse morphism of $\pi_I$ we
have $x=\pi_I(\sigma(x))=\sum_{d\in B_I}\sigma_d(x)d$ for all $x\in I$. 

For all $x\in I$ we have 
$\Vert\sigma_d(x)\Vert
=\Vert\sigma_d(\lim_\nu xe_\nu)\Vert
=\lim_\nu\Vert x\sigma_d(e_\nu)\Vert 
\leq\Vert x\Vert\liminf_\nu\Vert\sigma_d(e_\nu)\Vert$, 
so $\Vert\sigma_d\Vert\leq \liminf_\nu\Vert\sigma_d(e_\nu)\Vert$. 
Then for all $S\in\mathcal{P}_{f}(B_I)$ holds
$$
\sum_{d\in S}\Vert \sigma_d\Vert
\leq \sum_{d\in S}\liminf_\nu\Vert \sigma_d(e_\nu)\Vert
\leq \liminf_\nu\sum_{d\in S}\Vert \sigma_d(e_\nu)\Vert
\leq \liminf_\nu\sum_{d\in B_I}\Vert \sigma_d(e_\nu) \Vert
$$
$$
=\liminf_{\nu}\Vert\sigma(e_\nu)\Vert
\leq \Vert\sigma\Vert\liminf_{\nu}\Vert e_\nu\Vert
\leq \Vert\sigma\Vert
$$
Since $S\in \mathcal{P}_{f}(B_I)$ is arbitrary, then the sum 
$\sum_{d\in B_I}\Vert\sigma_d\Vert$ is finite. As a consequence, the 
sum $\sum_{d\in B_I}\Vert\sigma_d\Vert^2$ is finite too. 

Now we regard $A$ as an ideal in its unitization $A_\#$, then $I$ is an ideal of
$A_\#$ too. Fix a natural number $m\in\mathbb{N}$ and a real number
$\epsilon>0$. Then there exists a set $S\in\mathcal{P}_{f}(B_I)$ such that
$\sum_{d\in B_I\setminus S}\Vert\sigma_d\Vert<\epsilon$. Denote its cardinality
by $N$. Consider a positive element 
$b=\sum_{d\in B_I}\Vert\sigma_d\Vert^2 d^*d\in I$. Now we perform 
a ``power trick'' by considering different powers $b^{1/m}$ of the positive element 
$b$, where $m\in\mathbb{N}$. By lemma~\ref{ContFuncCalcOnIdealOfCStarAlg} we 
have that $b^{1/m}\in I$, so $b^{1/m}=\sum_{d\in B_I}\sigma_d(b^{1/m})d$. 
By continuous functional calculus we have 
$\Vert b^{1/m}\Vert
=\sup_{t\in\operatorname{sp}_{A_\#}(b)} t^{1/m}\leq\Vert b\Vert^{1/m}$, 
then $\limsup_{m\to\infty}\Vert b^{1/m}\Vert\leq 1$. 
Therefore, $\Vert b^{1/m}\Vert\leq 2$ for sufficiently big $m$. Denote
$\varsigma_d=\sigma_d(b^{1/m})$, $u=\sum_{d\in S}\varsigma_d d$ and
$v=\sum_{d\in B_I\setminus S}\varsigma_d d$, so 
$$
b^{2/m}={(b^{1/m})}^*b^{1/m}=u^*u+u^*v+v^*u+v^*v
$$
Clearly, $\varsigma_d^*\varsigma_d\leq \Vert \varsigma_d\Vert^2 e_{A_\#}\leq
\Vert \sigma_d\Vert^2\Vert b^{1/m}\Vert^2 e_{A_\#}\leq 4\Vert \sigma_d\Vert^2
e_{A_\#}$. For any $x,y\in A$ we have $x^*x+y^*y-(x^*y+y^*x)={(x-y)}^*(x-y)\geq
0$, therefore 
$$
d^*\varsigma_d^* \varsigma_c c+c^*\varsigma_c^* \varsigma_d d
\leq d^*\varsigma_d^*\varsigma_d d + c^*\varsigma_c^*\varsigma_c c
\leq 4\Vert \sigma_d\Vert^2 d^*d+4\Vert \sigma_c\Vert^2 c^*c
$$
for all $c,d\in B_I$. We sum up these inequalities over $c\in S$ and $d\in S$,
then 
$$
\begin{aligned}
\sum_{c\in S}\sum_{d\in S}c^*\varsigma_c^* \varsigma_d d
&=\frac{1}{2}\left(
    \sum_{c\in S}\sum_{d\in S}d^*\varsigma_d^* \varsigma_c c
    +
    \sum_{c\in S}\sum_{d\in S}c^*\varsigma_c^* \varsigma_d d
\right)\\
&\leq\frac{1}{2}\left(4 N\sum_{d\in S} \Vert \sigma_d\Vert^2 d^*d+
4 N\sum_{c\in S} \Vert \sigma_c\Vert^2 c^*c\right)\\
&=4 N\sum_{d\in S} \Vert \sigma_d\Vert^2 d^*d.
\end{aligned}
$$
Therefore,
$$
u^*u
={\left(\sum_{c\in S}\varsigma_c c\right)}^*
\left(\sum_{d\in S}\varsigma_d d\right)
=\sum_{c\in S}\sum_{d\in S}c^*\varsigma_c^* \varsigma_d d
\leq 4N\sum_{d\in S} \Vert \sigma_d\Vert^2 d^*d
= 4N b
$$
Note that
$$
\Vert u\Vert
\leq \sum_{d\in S}\Vert\varsigma_d\Vert\Vert d\Vert
\leq \sum_{d\in S}2\Vert\sigma_d\Vert
\leq 2\Vert\sigma\Vert,
\qquad
\Vert v\Vert
\leq \sum_{d\in B_I\setminus S}\Vert\varsigma_d\Vert\Vert d\Vert
\leq \sum_{d\in B_I\setminus S}2\Vert\sigma_d\Vert
\leq 2\epsilon,
$$
so $\Vert u^*v+v^*u\Vert\leq 8\Vert\sigma\Vert\epsilon$ 
and $\Vert v^*v\Vert\leq 4\epsilon^2$. Since $u^*v+v^*u$ and $v^*v$ are self 
adjoint, then $u^*v+v^*u\leq 8\Vert\sigma\Vert\epsilon e_{A_\#}$ 
and $v^*v\leq 4\epsilon^2 e_{A_\#}$ Therefore for any $\epsilon>0$ and 
sufficiently big $m$ we have 
$$
b^{2/m}
=u^*u+u^*v+v^*u+v^*v
\leq 4Nb+\epsilon(8\Vert\sigma\Vert+4\epsilon)e_{A_\#}.
$$


In other words $g_m(b)\geq 0$ for a continuous function
$g_m:\mathbb{R}_+\to\mathbb{R}:t\mapsto
4Nt+\epsilon(8\Vert\sigma\Vert+4\epsilon)-t^{2/m}$. Now choose $\epsilon>0$ such
that $M:=\epsilon(8\Vert\sigma\Vert+4\epsilon)<1$.  By spectral mapping theorem
[\cite{HelLectAndExOnFuncAn}, theorem 6.4.2] we get
$g_m(\operatorname{sp}_{A_\#}(b))
=\operatorname{sp}_{A_\#}(g_m(b))\subset\mathbb{R}_+$.
It is routine to check that $g_m$ has the only one extreme point
$t_{0,m}={(2Nm)}^{\frac{m}{2-m}}$ where the minimum of $g_m$ is attained. Since
$\lim_{m\to\infty} g_m(t_{0,m})=M-1<0$, $g_m(0)=M>0$ and $\lim_{t\to\infty}
g_m(t)=+\infty$, then for sufficiently big $m$ the function $g_m$ has exactly
two zeros: $0<t_{1,m}<t_{0,m}$ and $t_{2,m} > t_{0,m}$. Therefore, $g_m(t)\geq 0$
for $0\leq t\leq t_{1,m}$ or $t\geq t_{2,m}$. Hence, for all sufficiently big
$m$ holds $\operatorname{sp}_{A_\#}(b)\subset T_{t_{1,m},t_{2,m}}$, 
where $T_{a, b}:=\{t\in\mathbb{R} : 0\leq t \leq a \vee t \geq b\}$. 
Since $\lim_{m\to\infty} t_{0,m}=0$ then $\lim_{m\to\infty} t_{1,m}=0$ too. 
Note that $g_m(1)=4N+M-1>0$, so for sufficiently big $m$ we also 
have $t_{2,m}\leq 1$. Consequently,
$\operatorname{sp}_{A_\#}(b)\subset T_{0,1}$.

Consider a continuous function $h:\mathbb{R}_+\to\mathbb{R}:t\mapsto\min(1, t)$,
then from lemma~\ref{ContFuncCalcOnIdealOfCStarAlg} we get an idempotent
$p=h(b)=\operatorname{RCont}_b^0(h)\in I$ such that $\Vert
p\Vert=\sup_{t\in\operatorname{sp}_{A_\#}(b)}|h(t)|\leq 1$. Therefore, $p$ is a
self-adjoint idempotent. Since $h(t)t=th(t)=t$ for all $t\in
\operatorname{sp}_{A_\#}(b)$ we have $bp=pb=b$. The last equality implies
$$
0=(e_{A_\#}-p)b(e_{A_\#}-p)
=\sum_{d\in B_I}
    {(\Vert\sigma_d\Vert d(e_{A_\#}-p))}^*\Vert\sigma_d\Vert d(e_{A_\#}-p).
$$
Since the right-hand side of this equality is non-negative, then $d=dp$ for all
$d\in B_I$ with $\sigma_d\neq 0$. Finally, for any $x\in I$ we obtain
$xp=\sum_{d\in B_I}\sigma_d(x)dp=\sum_{d\in B_I}\sigma_d(x)d=x$, i.e. $I=Ap$,
for self-adjoint idempotent $p\in I$.
\end{proof}

It is worth pointing out here that in relative theory there no such description
for relative projectivity of closed left ideals of $C^*$-algebras. Though for the case
of separable $C^*$-algebras (that is $C^*$-algebras that are separable as Banach
spaces) all closed left ideals are relatively projective. See
[\cite{LykProjOfBanAndCStarAlgsOfContFld}, section 6] for a nice overview of the
current state of the problem.

\begin{corollary}\label{BiIdealOfCStarAlgMetTopProjCharac} Let $I$ be a closed
two-sided ideal of a $C^*$-algebra $A$. Then the following are equivalent:

\begin{enumerate}[label = (\roman*)]
    \item $I$ is unital;

    \item $I$ is a metrically projective $A$-module;

    \item $I$ is a topologically projective $A$-module.
\end{enumerate}
\end{corollary}
\begin{proof} The ideal $I$ has a contractive approximate identity
[\cite{HelBanLocConvAlg}, theorem 4.7.79]. Therefore, $I$ has a right identity
iff $I$ is unital. Now all equivalences follow from
theorem~\ref{LeftIdealOfCStarAlgMetTopProjCharac}. 
\end{proof}

\begin{corollary}\label{IdealofCommCStarAlgMetTopProjCharac} Let $S$ be a
locally compact Hausdorff space, and $I$ be an ideal of $C_0(S)$. Then the
following are equivalent:

\begin{enumerate}[label = (\roman*)]
    \item $\operatorname{Spec}(I)$ is compact;

    \item $I$ is a metrically projective $C_0(S)$-module;

    \item $I$ is a topologically projective $C_0(S)$-module.
\end{enumerate}
\end{corollary}
\begin{proof} By Gelfand-Naimark's theorem
$I\isom{\mathbf{Ban}_1}C_0(\operatorname{Spec}(I))$, therefore $I$ is
semisimple. Now by Shilov's idempotent theorem $I$ is unital iff
$\operatorname{Spec}(I)$ is compact. It remains to apply
corollary~\ref{BiIdealOfCStarAlgMetTopProjCharac}. 
\end{proof}

It is worth mentioning that the class of relatively projective closed ideals of
$C_0(S)$ is much larger. In fact a closed ideal $I$ of $C_0(S)$ is relatively
projective iff $\operatorname{Spec}(I)$ is paracompact
[\cite{HelHomolBanTopAlg}, chapter IV,\S\S 2--3].

%-------------------------------------------------------------------------------
%	Injective ideals of C^*-algebras
%-------------------------------------------------------------------------------

\subsection{
    Injective ideals of \texorpdfstring{$C^*$}{C*}-algebras}\label{
SubSectionInjectiveIdealsOfCStarAlgebras}

Now we proceed to injectivity of closed two-sided ideals of $C^*$-algebras.
Unfortunately we don't have a complete characterization at hand, but some
necessary conditions and several examples. The following proposition shows that
we may restrict investigation of injective closed ideals to the case of $C^*$-algebras
that are $\langle$~metrically / topologically~$\rangle$ injective over themselves as
right modules.

\begin{proposition}\label{MetTopInjOvrAlgIffOvrItslf} Let $I$ be a closed two-sided
ideal of a $C^*$-algebra $A$, then $I$ is $\langle$~metrically /
topologically~$\rangle$ injective as $A$-module iff $I$ is $\langle$~metrically
/ topologically~$\rangle$ injective as $I$-module.
\end{proposition}
\begin{proof} Note that any closed two-sided ideal $I$ of a $C^*$-algebra $A$ is again
a $C^*$-algebra with a contractive approximate identity [\cite{HelBanLocConvAlg},
theorem 4.7.79]. Therefore, $I$ is faithful as a right $I$-module. Now
proposition~\ref{ReduceInjIdToInjAlg} gives the desired equivalence.
\end{proof}

We shall say a few words on so called $AW^*$-algebras, since they are key
players here. In attempt to find a purely algebraic definition of
$W^*$-algebras Kaplanski introduced this class of $C^*$-algebras
in~\cite{KaplProjInBanAlg}. A $C^*$-algebra $A$ is called an $AW^*$-algebra if
for any subset $S\subset A$ the right algebraic annihilator
$S^{\perp A}$ has the form $pA$ for
some self-adjoint idempotent $p\in A$. This class contains all $W^*$-algebras,
but strictly larger. Note that for the case of commutative $C^*$-algebras the
property of being an $AW^*$-algebra is equivalent to  $\operatorname{Spec}(A)$
being a Stonean space [\cite{BerbBaerStarRings}, theorem 1.7.1]. The main
reference to $AW^*$-algebras and more general Baer ${}^*$-rings
is~\cite{BerbBaerStarRings}. 

The following proposition is a combination of results by Hamana and Takesaki.

\begin{proposition}[Hamana, Takesaki]\label{MetInjCStarAlgCharac} Let $A$ be a
$C^*$-algebra, then it is a metrically injective right $A$-module iff it is a
commutative $AW^*$-algebra, that is $\operatorname{Spec}(A)$ is a Stonean space.
\end{proposition}
\begin{proof} 

If $A$ is metrically injective as $A$-module, then it has norm one left identity
by proposition~\ref{MetTopInjOfId}. But $A$ also has a contractive approximate
identity  [\cite{HelBanLocConvAlg}, theorem 4.7.79], therefore $A$ is unital.
Now by result of Hamana  [\cite{HamInjEnvBanMod}, proposition 2] the
$C^*$-algebra $A$ is a commutative $AW^*$-algebra. Hamana's argument was for
left modules, but one can easily modify his proof to get the result for right
modules.

The converse was proved by Takesaki in [\cite{TakHanBanThAndJordDecomOfModMap},
theorem 2]. Although only two-sided Banach modules were treated there, the
reasoning is essentially the same for right modules.
\end{proof}

It remains to consider topological injectivity. As the following proposition
shows topologically injective $C^*$-algebras are not so far from commutative
ones. This proposition exploits the l.u.st.\ property. For its definition see
section~\ref{
    SubSectionHomologicallyTrivialModulesOverBanachAlgebrasWithSpecificGeometry
}.

\begin{proposition}\label{TopInjIdHaveLUST} Let $A$ be a $C^*$-algebra which is
topologically injective as an $A$-module. Then $A$ has the l.u.st.\ property and
as a consequence it cannot contain  $\mathcal{B}(\ell_2(\mathbb{N}_n))$ as
${}^*$-subalgebra for arbitrarily big $n\in\mathbb{N}$.
\end{proposition}
\begin{proof} By Gelfand-Naimark's theorem [\cite{HelBanLocConvAlg}, theorem
4.7.57] there exists a Hilbert space $H$ and an isometric ${}^*$-homomorphism
$\varrho:A\to\mathcal{B}(H)$. Denote $\Lambda:=B_{H_\varrho^{cc}}$. It is easy
to check that 
$$
\rho:
A
    \to
\bigoplus\nolimits_\infty \{H_\varrho^{cc}:\overline{x}\in \Lambda \},\, 
a
    \mapsto 
\bigoplus\nolimits_\infty \{\overline{x}\cdot a:\overline{x}\in \Lambda \}
$$
is an isometric $A$-morphism of right $A$-modules. Since $A$ is a topologically
injective $A$-module, then $\rho$ has a left inverse $A$-morphism $\tau$.
Therefore, $A$ is complemented in $E:=\bigoplus_\infty
\{H_\varrho^{cc}:\overline{x}\in \Lambda \}$ via projection $\rho\tau$. Note
that $H_{\varrho}^{cc}$ is a Banach lattice as any Hilbert space, then so is
$E$. As any Banach lattice $E$ has the l.u.st.\ property [\cite{DiestAbsSumOps},
theorem 17.1], then so does $A$, because the l.u.st.\ property is inherited by
complemented subspaces.

Assume $A$ contains $\mathcal{B}(\ell_2(\mathbb{N}_n))$ as ${}^*$-subalgebra for
arbitrarily big $n\in\mathbb{N}$. In fact this copy of
$\mathcal{B}(\ell_2(\mathbb{N}_n))$ is $1$-complemented in $A$
[\cite{LauLoyWillisAmnblOfBanAndCStarAlgsOfLCG}, lemma 2.1]. Therefore, we have
an inequality for local unconditional constants
$\kappa_u(\mathcal{B}(\ell_2(\mathbb{N}_n)))\leq \kappa_u(A)$. By theorem 5.1
in~\cite{GorLewAbsSmOpAndLocUncondStrct} we know that $\lim_n
\kappa_u(\mathcal{B}(\ell_2(\mathbb{N}_n)))=+\infty$, so $\kappa_u(A)=+\infty$.
This contradicts the l.u.st.\ property of $A$. Hence, $A$ cannot contain
$\mathcal{B}(\ell_2(\mathbb{N}_n))$ as ${}^*$-subalgebra for arbitrarily big 
$n\in\mathbb{N}$.
\end{proof}

As the proposition~\ref{TopInjIdHaveLUST} shows $C^*$-algebras that are
topologically injective over themselves cannot contain
$\mathcal{B}(\ell_2(\mathbb{N}_n))$ as a ${}^*$-subalgebra for arbitrarily big 
$n\in\mathbb{N}$. Such $C^*$-algebras are called subhomogeneous, and in fact
[\cite{BlackadarOpAlg}, proposition IV.1.4.3] they can be treated as closed
${}^*$-subalgebras of $M_n(C(K))$ for some compact Hausdorff space $K$ and some
natural number $n$. For more on subhomogeneous $C^*$-algebras see
[\cite{BlackadarOpAlg}, section IV.1.4]. 

We shall give two important examples of non-commutative $C^*$-algebras that are
topologically injective over themselves.

\begin{proposition}\label{FinDimBHModTopInj} Let $H$ be a finite dimensional
Hilbert space. Then $\mathcal{B}(H)$ is topologically injective as
$\mathcal{B}(H)$-module. 
\end{proposition}
\begin{proof} Note that
$\mathcal{B}(H)\isom{\mathbf{mod}_1-\mathcal{B}(H)}{\mathcal{N}(H)}^*$, and
the result immediately follows from propositions~\ref{FinDimNHModTopProjFlat}
and~\ref{DualMetTopProjIsMetrInj}.
\end{proof}

\begin{proposition}\label{CKMatrixModTopInj} Let $K$ be a Stonean space and
$n\in\mathbb{N}$, then $M_n(C(K))$ is topologically injective
$M_n(C(K))$-module.
\end{proposition}
\begin{proof} For a fixed $s\in K$ by $\mathbb{C}_s$ we denote the right
$C(K)$-module $\mathbb{C}$ with module action defined by $z\cdot a=a(s)z$ for all
$a\in C(K)$ and $z\in\mathbb{C}$. By $M_n(\mathbb{C}_s)$ we denote the right
Banach $M_n(C(K))$-module $M_n(\mathbb{C})$ with module action defined by
${(x\cdot a)}_{i,j}=\sum_{k=1}^n x_{i,k}a_{k,j}(s)$ for $a\in M_n(C(K))$ and 
$x\in M_n(\mathbb{C}_s)$. The $C^*$-algebra $M_n(C(K))$ is nuclear
[\cite{BroOzaCStarAlgFinDimApprox}, corollary 2.4.4], then by
[\cite{HaaNucCStarAlgAmen}, theorem 3.1] this algebra is relatively amenable and
even $1$-relatively amenable [\cite{RundeAmenConstFour}, example 2]. Since
$M_n(\mathbb{C}_s)$ is finite dimensional, it is an $\mathscr{L}_{1, C}^g$-space
for some constant $C\geq 1$ independent of $s$. Thus, by
proposition~\ref{MetTopEssL1FlatModAoverAmenBanAlg} the $M_n(C(K))$-module
${M_n(\mathbb{C}_s)}^*$ is $C$-topologically flat. Since the latter module is
essential, by proposition~\ref{MetCTopFlatCharac} the right $M_n(C(K))$-module
${M_n(\mathbb{C}_s)}^{**}$ is $C$-topologically injective. Note that
${M_n(\mathbb{C}_s)}^{**}$ is isometrically isomorphic to $M_n(\mathbb{C}_s)$ as a 
right $M_n(C(K))$-module, so from proposition~\ref{MetTopInjModProd} we get that
$\bigoplus_\infty \{M_n(\mathbb{C}_s):s\in K \}$ is topologically injective as
$M_n(C(K))$-module.

Note that by proposition~\ref{MetInjCStarAlgCharac} the $C(K)$-module $C(K)$ is
metrically injective, therefore an isometric $C(K)$-morphism
$\widetilde{\rho}:
C(K)\to\bigoplus_\infty \{ \mathbb{C}_s:s\in K \},\, 
x\mapsto \bigoplus_\infty \{x(s):s\in K \}$ 
admits a left inverse contractive $C(K)$-morphism 
$\widetilde{\tau}:\bigoplus_\infty \{ \mathbb{C}_s:s\in K \} \to C(K)$. 
It is routine to check now that linear operators
$$
\rho:
M_n(C(K))\to\bigoplus\nolimits_\infty \{M_n(\mathbb{C}_s):s\in K \},\, 
x\mapsto \bigoplus\nolimits_\infty \{
    {(x_{i,j}(s))}_{i,j\in\mathbb{N}_n}:s\in K
 \}
$$
$$
\tau
:\bigoplus\nolimits_\infty \{M_n(\mathbb{C}_s):s\in K \}\to M_n(C(K))
:y\mapsto {\left(
    \widetilde{\tau}\left(\bigoplus\nolimits_\infty \{y_{s,i,j}:s\in K \}\right)
\right)}_{i,j\in\mathbb{N}_n}
$$
are bounded $M_n(C(K))$-morphisms such that $\tau \rho=1_{M_n(C(K))}$. That is
$M_n(C(K))$ is a retract of topologically injective $M_n(C(K))$-module
$\bigoplus_\infty \{M_n(\mathbb{C}_s):s\in K \}$ in $\mathbf{mod}_1-M_n(C(K))$.
Finally, from proposition~\ref{RetrMetCTopInjIsMetCTopInj} we conclude that
$M_n(C(K))$ is topologically injective $M_n(C(K))$-module.
\end{proof}

\begin{theorem}\label{TopInjAWStarAlgCharac} Let $A$ be a $C^*$-algebra. Then
the following are equivalent:

\begin{enumerate}[label = (\roman*)]
    \item $A$ is an $AW^*$-algebra which is topologically injective 
    as $A$-module;

    \item $A
    =\bigoplus_\infty \{M_{n_\lambda}(C(K_\lambda)):\lambda\in\Lambda \}$
    for some finite families of natural 
    numbers ${(n_\lambda)}_{\lambda\in\Lambda}$ and Stonean 
    spaces ${(K_\lambda)}_{\lambda\in\Lambda}$.
\end{enumerate}
\end{theorem}
\begin{proof}$(i)\implies (ii)$ From proposition 6.6
in~\cite{SmithDecompPropCStarAlg} we know that an $AW^*$-algebra is either
isomorphic as $C^*$-algebra 
to  $\bigoplus_\infty \{M_{n_\lambda}(C(K_\lambda)):\lambda\in\Lambda \}$ 
for some finite families of natural numbers ${(n_\lambda)}_{\lambda\in\Lambda}$ 
and Stonean spaces ${(K_\lambda)}_{\lambda\in\Lambda}$ or contains 
a ${}^*$-subalgebra 
$\bigoplus_\infty \{ \mathcal{B}(\ell_2(\mathbb{N}_n)):n\in\mathbb{N} \}$. The
second option is canceled out by proposition~\ref{TopInjIdHaveLUST}.

$(ii)\implies (i)$ For each $\lambda\in\Lambda$ the algebra
$M_{n_\lambda}(C(K_\lambda))$ is unital because $K_\lambda$ is compact.
Therefore, $M_{n_\lambda}(C(K_\lambda))$ is faithful as
$M_{n_\lambda}(C(K_\lambda))$-module. It is also topologically injective as
$M_{n_\lambda}(C(K_\lambda))$-module by proposition~\ref{CKMatrixModTopInj}.
Now the topological injectivity of $A$-module $A$ follows from paragraph
$(ii)$ of proposition~\ref{MetTopProjInjFlatUnderSumOfAlg} with $p=\infty$ and
$X_\lambda=A_\lambda=M_{n_\lambda}(C(K_\lambda))$ for all $\lambda\in\Lambda$. 

For all $\lambda\in\Lambda$ the algebra $C(K_\lambda)$ is an $AW^*$-algebra,
because $K_\lambda$ is a Stonean space [\cite{BerbBaerStarRings}, theorem
1.7.1]. Therefore, $M_{n_\lambda}(C(K_\lambda))$ is an $AW^*$-algebra too
[\cite{BerbBaerStarRings}, corollary 9.62.1]. Finally, $A$ is an $AW^*$-algebra
as $\bigoplus_\infty$-sum of such algebras [\cite{BerbBaerStarRings},
proposition 1.10.1].
\end{proof}

It is desirable to prove that any $C^*$-algebra which is topologically injective 
over itself is an $AW^*$-algebra, but it seems to be a challenge even in the
commutative case.

%-------------------------------------------------------------------------------
%	Flat ideals of C^*-algebras
%-------------------------------------------------------------------------------

\subsection{
    Flat ideals of \texorpdfstring{$C^*$}{C*}-algebras}\label{
SubSectionFlatIdealsOfCStarAlgebras}

By considering flatness we finalize this lengthy investigations of closed ideals of
$C^*$-algebras.

\begin{proposition}\label{IdealofCstarAlgisMetTopFlat} Let $I$ be a closed left ideal
of a $C^*$-algebra $A$. Then $I$ is metrically and topologically flat as
$A$-module.
\end{proposition}
\begin{proof} From [\cite{HelBanLocConvAlg}, proposition 4.7.78] it follows that
$I$ has a right contractive identity. It remains to apply
proposition~\ref{MetTopFlatIdealsInUnitalAlg}.
\end{proof}

\begin{proposition}\label{CStarAlgIsL1IfFinDim} Let $A$ be a $C^*$-algebra, then
$A$ is an $\langle$~$L_1$-space / $\mathscr{L}_1^g$-space~$\rangle$ iff
$\langle$~$\operatorname{dim}(A)\leq 1$ / $A$ is finite dimensional~$\rangle$.
\end{proposition}
\begin{proof} Assume $A$ is an $\mathscr{L}_1^g$-space, then $A^{**}$ is
complemented in some $L_1$-space [\cite{DefFloTensNorOpId}, corollary
23.2.1(2)]. Since $A$ isometrically embeds in its second dual via $\iota_{A}$ we
may regard $A$ as closed subspace of some $L_1$-space. The latter space is
weakly sequentially complete [\cite{WojBanSpForAnalysts}, corollary III.C.14].
The property of being weakly sequentially complete is preserved by closed
subspaces, therefore $A$ is weakly sequentially complete too. By proposition 2
in~\cite{SakWeakCompOpOnOpAlg} every weakly sequentially complete $C^*$-algebra
is finite dimensional, hence $A$ is finite dimensional. Conversely, if $A$ is
finite dimensional it is an $\mathscr{L}_1^g$-space as any finite dimensional
Banach space.

Assume $A$ is an $L_1$-space and, a fortiori, an $\mathscr{L}_1^g$-space. As was
noted above $A$ is a finite dimensional, so
$A\isom{\mathbf{Ban}_1}\ell_1(\mathbb{N}_n)$ for $n=\operatorname{dim}(A)$. On
the other hand, $A$ is a finite dimensional $C^*$-algebra, so it is
isometrically isomorphic to $\bigoplus_\infty \{
\mathcal{B}(\ell_2(\mathbb{N}_{n_k})):k\in\mathbb{N}_m \}$ for some natural
numbers ${(n_k)}_{k\in\mathbb{N}_m}$ 
[\cite{DavCSatrAlgByExmpl}, theorem III.1.1].
Assume $\operatorname{dim}(A)>1$, then $A$ contains an isometric copy of
$\ell_\infty(\mathbb{N}_2)$. Therefore, we have an isometric embedding of
$\ell_\infty(\mathbb{N}_2)$ into $\ell_1(\mathbb{N}_n)$. This is impossible by
theorem 1 from~\cite{LyubIsomEmdbFinDimLp}. 
Therefore, $\operatorname{dim}(A)\leq 1$. 
\end{proof}

\begin{proposition}\label{CStarAlgIsTopFlatOverItsIdeal} Let $I$ be a proper
closed two-sided ideal of a  $C^*$-algebra $A$. Then the following are equivalent:

\begin{enumerate}[label = (\roman*)]
    \item $A$ is a $\langle$~metrically / topologically~$\rangle$ flat $I$-module;

    \item $\langle$~$\operatorname{dim}(A)=1$, $I= \{0 \}$ / $A/I$ is finite
    dimensional~$\rangle$.
\end{enumerate}
\end{proposition}
\begin{proof} We may regard $I$ as a closed  ideal of the unitazation $A_\#$ of $A$. Since
$I$ is a two-sided ideal, then it has a contractive approximate identity
${(e_\nu)}_{\nu\in N}$ such that $0\leq e_\nu\leq e_{A_\#}$
[\cite{HelBanLocConvAlg}, proposition 4.7.79]. As a 
corollary $\sup_{\nu\in N}\Vert e_{A_\#}-e_\nu\Vert\leq 1$. Since $I$ has an 
approximate identity we also have $A_{ess}:=\operatorname{cl}_A(IA)=I$. 
Since $I$ is a two-sided ideal then $A/I$ is a $C^*$-algebra 
[\cite{HelBanLocConvAlg}, theorem 4.7.81].

Assume, $A$ is a metrically flat $I$-module. Since 
$\sup_{\nu\in N}\Vert e_{A_\#}-e_\nu\Vert\leq 1$, then paragraph $(ii)$ of
proposition~\ref{DualBanModDecomp} tells us that ${(A/A_{ess})}^*={(A/I)}^*$ is 
a retract of $A^*$ in $\mathbf{mod}_1-I$. Now from
propositions~\ref{MetCTopFlatCharac} and~\ref{RetrMetCTopInjIsMetCTopInj} it
follows that $A/I$ is metrically flat $I$-module. Since this is an annihilator
module, then from proposition~\ref{MetTopFlatAnnihModCharac} it follows that 
$I= \{0 \}$ and $A/I$ is an $L_1$-space. Now from
proposition~\ref{CStarAlgIsL1IfFinDim} we get that 
$\operatorname{dim}(A/I)\leq 1$. Since $A$ contains a proper 
ideal $I= \{0 \}$, then $\operatorname{dim}(A)=1$. Conversely, 
if $I= \{0 \}$ and $\operatorname{dim}(A)=1$, then we have an 
annihilator $I$-module $A$ which is isometrically isomorphic 
to $\ell_1(\mathbb{N}_1)$. By proposition~\ref{MetTopFlatAnnihModCharac} 
it is metrically flat. 

By proposition~\ref{TopFlatModCharac} the $I$-module $A$ is topologically flat
iff $A_{ess}=I$ and $A/A_{ess}=A/I$ are topologically flat $I$-modules. Note that by
proposition~\ref{IdealofCstarAlgisMetTopFlat} the ideal $I$ is a topologically
flat $I$-module. From proposition~\ref{MetTopFlatAnnihModCharac} we get that the 
annihilator $I$-module $A/I$ is topologically flat iff it is an $\mathscr{L}_1^g$-space. 
The latter is equivalent to $A/I$ being finite dimensional, see 
proposition~\ref{CStarAlgIsL1IfFinDim}.
\end{proof}

%-------------------------------------------------------------------------------
%	\mathcal{K}(H)- and \mathcal{B}(H)-modules
%-------------------------------------------------------------------------------

\subsection{
    \texorpdfstring{$\mathcal{K}(H)$}{K(H)}- and
    \texorpdfstring{$\mathcal{B}(H)$}{B(H)}-modules}\label{
SubSectionKHAndBHModules}

In this section we apply general results on closed ideals obtained above to classical
modules over $C^*$-algebras.  For a given Hilbert space $H$ we consider
$\mathcal{B}(H)$, $\mathcal{K}(H)$ and $\mathcal{N}(H)$ as left and right Banach
modules over $\mathcal{B}(H)$ and $\mathcal{K}(H)$. For all these modules the module
action is just the composition of operators. The Schatten-von Neumann
isomorphisms $\mathcal{N}(H)\isom{\mathbf{Ban}_1}{\mathcal{K}(H)}^*$,
$\mathcal{B}(H)\isom{\mathbf{Ban}_1}{\mathcal{N}(H)}^*$ (see
[\cite{TakThOpAlgVol1}, theorems II.1.6, II.1.8]) will be of use here. 
In fact, these identifications are isomorphisms of left and right 
$\mathcal{B}(H)$-modules and a fortiori of $\mathcal{K}(H)$-modules.

\begin{proposition}\label{KHAndBHModBH} Let $H$ be a Hilbert space. Then

\begin{enumerate}[label = (\roman*)]
    \item $\mathcal{B}(H)$ is metrically and topologically projective and 
    flat as $\mathcal{B}(H)$-module;

    \item $\mathcal{B}(H)$ is metrically or topologically projective or flat as
    $\mathcal{K}(H)$-module iff $H$ is finite dimensional;

    \item $\mathcal{B}(H)$ is topologically injective as $\mathcal{B}(H)$- or
    $\mathcal{K}(H)$-module iff $H$ is finite dimensional;

    \item $\mathcal{B}(H)$ is metrically injective as $\mathcal{B}(H)$- or
    $\mathcal{K}(H)$-module iff $\dim(H)\leq 1$.
\end{enumerate}
\end{proposition}
\begin{proof} $(i)$ Since $\mathcal{B}(H)$ is a unital algebra it is metrically
and topologically projective as $\mathcal{B}(H)$-module by
proposition~\ref{UnitalAlgIsMetTopProj}. Both results regarding flatness follow
from proposition~\ref{MetTopProjIsMetTopFlat}.

$(ii)$ For infinite dimensional $H$ the Banach space
$\mathcal{B}(H)/\mathcal{K}(H)$ is of infinite dimension, so by
proposition~\ref{CStarAlgIsTopFlatOverItsIdeal} the module $\mathcal{B}(H)$
neither topologically nor metrically flat as $\mathcal{K}(H)$-module. Both
claims regarding projectivity follow from
proposition~\ref{MetTopProjIsMetTopFlat}. If $H$ is finite dimensional, then
$\mathcal{K}(H)=\mathcal{B}(H)$, so the result follows from paragraph $(i)$.

$(iii)$ If $H$ is infinite dimensional, then $\mathcal{B}(H)$ contains
$\mathcal{B}(\ell_2(\mathbb{N}_n))$ as ${}^*$-subalgebra for all
$n\in\mathbb{N}$. By proposition~\ref{TopInjIdHaveLUST} we get that
$\mathcal{B}(H)$ is not topologically injective as $\mathcal{B}(H)$-module. The
rest follows from paragraph $(i)$ of
proposition~\ref{MetTopInjUnderChangeOfAlg}. If $H$ is finite dimensional, then
$\mathcal{K}(H)=\mathcal{B}(H)$, so the result follows from
proposition~\ref{FinDimBHModTopInj}.

$(iv)$ If $\dim(H)>1$, then the $C^*$-algebra $\mathcal{B}(H)$ is not commutative. 
By proposition~\ref{MetInjCStarAlgCharac} we get that it is not metrically
injective as $\mathcal{B}(H)$-module. Now from paragraph $(i)$
of~\ref{MetTopInjUnderChangeOfAlg} we get that $\mathcal{B}(H)$ is not
metrically injective as $\mathcal{K}(H)$-module. If $\dim(H)\leq 1$ both claims
obviously follow from~\ref{MetInjCStarAlgCharac}.
\end{proof}

\begin{proposition}\label{KHAndBHModKH} Let $H$ be a Hilbert space. Then 

\begin{enumerate}[label = (\roman*)]
    \item $\mathcal{K}(H)$ is metrically and topologically flat 
    as $\mathcal{B}(H)$- or $\mathcal{K}(H)$-module;

    \item $\mathcal{K}(H)$ is metrically or topologically projective as
    $\mathcal{B}(H)$- or $\mathcal{K}(H)$-module iff $H$ is finite dimensional;

    \item $\mathcal{K}(H)$ is topologically injective as $\mathcal{B}(H)$- 
    or $\mathcal{K}(H)$-module iff $H$ is finite dimensional;

    \item $\mathcal{K}(H)$ is metrically injective as $\mathcal{B}(H)$- 
    or $\mathcal{K}(H)$-module iff $\dim(H)\leq 1$.
\end{enumerate}
\end{proposition}
\begin{proof} Let $A$ be either $\mathcal{B}(H)$ or $\mathcal{K}(H)$. Note that
$\mathcal{K}(H)$ is a two-sided ideal of $A$. 

$(i)$ Recall that $\mathcal{K}(H)$ has a contractive approximate identity
consisting of orthogonal projections onto all finite-dimensional subspaces of
$H$. Since $\mathcal{K}(H)$ is a two-sided ideal of $A$, then the result follows
from proposition~\ref{IdealofCstarAlgisMetTopFlat}.

$(ii)$, $(iii)$, $(iv)$ If $H$ is infinite dimensional, then $\mathcal{K}(H)$ is
not unital as a Banach algebra. From
corollary~\ref{BiIdealOfCStarAlgMetTopProjCharac} and
proposition~\ref{MetTopInjOfId} the $A$-module $\mathcal{K}(H)$ is neither
metrically nor topologically projective or injective. If $H$ is finite
dimensional, then $\mathcal{K}(H)=\mathcal{B}(H)$, so both results follow from
paragraphs $(i)$, $(iii)$ and $(iv)$ of proposition~\ref{KHAndBHModBH}.
\end{proof}

\begin{proposition}\label{KHAndBHModNH} Let $H$ be a Hilbert space. Then

\begin{enumerate}[label = (\roman*)]
    \item $\mathcal{N}(H)$ is metrically and topologically injective as
    $\mathcal{B}(H)$- or $\mathcal{K}(H)$-module;

    \item $\mathcal{N}(H)$ is topologically projective or flat 
    as $\mathcal{B}(H)$- or $\mathcal{K}(H)$-module 
    iff $H$ is finite dimensional;

    \item $\mathcal{N}(H)$ is metrically projective or flat 
    as $\mathcal{B}(H)$- or $\mathcal{K}(H)$-module iff $\dim(H)\leq 1$.
\end{enumerate}
\end{proposition}
\begin{proof} Let $A$ be either $\mathcal{B}(H)$ or $\mathcal{K}(H)$.

$(i)$ Note that $\mathcal{N}(H)\isom{\mathbf{mod}_1-A}{\mathcal{K}(H)}^*$, 
so the result follows from proposition~\ref{MetCTopFlatCharac} and 
paragraph $(i)$ of proposition~\ref{KHAndBHModKH}.

$(ii)$ Assume $H$ is infinite dimensional. Note that
$\mathcal{B}(H)\isom{\mathbf{mod}_1-A}{\mathcal{N}(H)}^*$, so from
proposition~\ref{DualMetTopProjIsMetrInj} and paragraph $(iii)$ of
proposition~\ref{KHAndBHModBH} we get that $\mathcal{N}(H)$ is not topologically
projective as $A$-module. Both results regarding flatness follow from
proposition~\ref{MetTopProjIsMetTopFlat}. If $H$ is finite dimensional we use
proposition~\ref{FinDimNHModTopProjFlat}.

$(iii)$ Assume $\dim(H)>1$, then by paragraph $(iv)$ of
proposition~\ref{KHAndBHModBH} the $A$-module $\mathcal{B}(H)$ is not metrically
injective. Since $\mathcal{B}(H)\isom{\mathbf{mod}_1-A}{\mathcal{N}(H)}^*$, then
from proposition~\ref{MetCTopFlatCharac} we get that $\mathcal{N}(H)$ is not
metrically flat as $A$-module. By proposition~\ref{MetTopProjIsMetTopFlat}, it
is not metrically projective as $A$-module. If $\dim(H)\leq 1$, then
$\mathcal{N}(H)=\mathcal{K}(H)=\mathcal{B}(H)$, so both results follow from
paragraph $(i)$ of proposition~\ref{KHAndBHModBH}.
\end{proof}

\begin{proposition}\label{KHAndBHModsRelTh} Let $H$ be a Hilbert space. Then
\begin{enumerate}[label = (\roman*)]
    \item as $\mathcal{K}(H)$-modules $\mathcal{N}(H)$ is relatively projective
    injective and flat, $\mathcal{K}(H)$ is relatively projective and flat, but
    relatively injective only for finite dimensional $H$, $\mathcal{B}(H)$ is
    relatively injective and flat, but relatively projective only for finite
    dimensional $H$;

    \item as $\mathcal{B}(H)$-modules $\mathcal{N}(H)$ is relatively projective
    injective and flat, $\mathcal{K}(H)$ is relatively projective and flat,
    $\mathcal{B}(H)$ is relatively projective, injective and flat.
\end{enumerate}
\end{proposition}
\begin{proof} $(i)$ Note that $H$ is relatively projective as
$\mathcal{K}(H)$-module [\cite{HelBanLocConvAlg}, theorem 7.1.27], so from
proposition 7.1.13 in~\cite{HelBanLocConvAlg} we get that
$\mathcal{N}(H)\isom{\mathcal{K}(H)-\mathbf{mod}_1}H\projtens H^*$ is also
relatively projective as $\mathcal{K}(H)$-module. By theorem IV.2.16
in~\cite{HelHomolBanTopAlg} the $\mathcal{K}(H)$-module $\mathcal{K}(H)$ is
relatively projective. A fortiori $\mathcal{N}(H)$ and $\mathcal{K}(H)$ are
relatively flat $\mathcal{K}(H)$-modules 
[\cite{HelBanLocConvAlg}, proposition 7.1.40], 
so $\mathcal{N}(H)\isom{\mathbf{mod}_1-\mathcal{K}(H)}{\mathcal{K}(H)}^*$
and  $\mathcal{B}(H)\isom{\mathbf{mod}_1-\mathcal{K}(H)}{\mathcal{N}(H)}^*$ are
relatively injective $\mathcal{K}(H)$-modules. From
[\cite{RamsHomPropSemgroupAlg}, proposition 2.2.8  (i)] we know that a Banach
algebra relatively injective over itself as a right module, necessarily has a
left identity. Therefore, $\mathcal{K}(H)$ is not relatively injective
$\mathcal{K}(H)$-module for infinite dimensional $H$. If $H$ is finite
dimensional, then $\mathcal{K}(H)$-module $\mathcal{K}(H)$ is relatively
injective because $\mathcal{K}(H)=\mathcal{B}(H)$ and $\mathcal{B}(H)$ is
relatively injective $\mathcal{K}(H)$-module as was shown above. By corollary
5.5.64 from~\cite{DalBanAlgAutCont} the algebra $\mathcal{K}(H)$ is relatively
amenable, so all its left modules are relatively flat [\cite{HelBanLocConvAlg},
theorem 7.1.60]. In particular $\mathcal{B}(H)$ is relatively flat
$\mathcal{K}(H)$-module. From [\cite{HelHomolBanTopAlg}, exercise V.2.20] we
know that $\mathcal{B}(H)$ is not relatively projective as
$\mathcal{K}(H)$-module when $H$ is infinite dimensional. If $H$ is finite
dimensional then $\mathcal{B}(H)$ is relatively projective
$\mathcal{K}(H)$-module because $\mathcal{B}(H)=\mathcal{K}(H)$ and
$\mathcal{K}(H)$ is relatively projective $\mathcal{K}(H)$-module as was shown
above.

$(ii)$ From proposition~\ref{KHAndBHModBH} paragraph $(i)$ and
proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj} it follows that
$\mathcal{B}(H)$ is relatively projective $\mathcal{B}(H)$-module. From
[\cite{RamsHomPropSemgroupAlg}, propositions 2.3.3, 2.3.4] we know that
$\langle$~an essential relatively projective / a faithful relatively
injective~$\rangle$ module over an ideal of a Banach algebra 
is $\langle$~relatively projective / relative injective~$\rangle$ over 
an algebra itself. Since $\mathcal{K}(H)$ and $\mathcal{N}(H)$ are essential 
and faithful $\mathcal{K}(H)$-modules, then from results of previous paragraph
$\mathcal{N}(H)$ is relatively projective and injective, while $\mathcal{K}(H)$
is relatively projective as $\mathcal{B}(H)$-modules. Now, by
[\cite{HelBanLocConvAlg}, proposition 7.1.40] all aforementioned modules are
relatively flat $\mathcal{B}(H)$-modules. In particular
$\mathcal{B}(H)\isom{\mathbf{mod}_1-\mathcal{B}(H)}{\mathcal{N}(H)}^*$ is
relatively injective $\mathcal{B}(H)$-module.
\end{proof}

Results of this section are summarized in the following three tables. Each cell
contains a condition under which the respective module has the respective
property and propositions where this result is proved. We use ``?'' symbol to indicate
open problems. These tables confirm that the property of being homologically
trivial in metric and topological theory is too restrictive. It is easier to
mention cases where metric and topological properties coincide with relative
ones: flatness of $\mathcal{K}(H)$ as $\mathcal{B}(H)$- or
$\mathcal{K}(H)$-module, injectivity of $\mathcal{N}(H)$ as $\mathcal{B}(H)$- or
$\mathcal{K}(H)$-module, projectivity and flatness of $\mathcal{B}(H)$-module
$\mathcal{B}(H)$. In the remaining cases $H$ needs to be at least finite
dimensional in order for these properties be equivalent in metric, topological
and relative theory.


\begin{scriptsize}
    \begin{longtable}{|c|c|c|c|c|c|c|} 
    \multicolumn{7}{c}{
        \mbox{
            Homologically trivial $\mathcal{K}(H)$- 
            and $\mathcal{B}(H)$-modules in metric theory
        }
    }                                                                                                                                                                                                                                                                                                                                                                                                                                                    \\
    \hline &
    \multicolumn{3}{c|}{
        $\mathcal{K}(H)$-modules
    } & 
    \multicolumn{3}{c|}{
        $\mathcal{B}(H)$-modules
    }                                                                                                                                                                                                                       \\
    \hline & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} \\ 
    \hline
        $\mathcal{N}(H)$ & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)\leq 1$ \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)\leq 1$ \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)\leq 1$ \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)\leq 1$ \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} \\
    \hline
        $\mathcal{B}(H)$ & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)\leq 1$ \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)\leq 1$ \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular}          \\ 
    \hline
        $\mathcal{K}(H)$ & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)\leq 1$ \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)\leq 1$ \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} \\ 
    \hline
    \multicolumn{7}{c}{
        \mbox{
            Homologically trivial $\mathcal{K}(H)$- 
            and $\mathcal{B}(H)$-modules in topological theory
        }
    } \\
    \hline & 
    \multicolumn{3}{c|}{
        $\mathcal{K}(H)$-modules
    } & 
    \multicolumn{3}{c|}{
        $\mathcal{B}(H)$-modules
    } \\
    \hline & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} \\ 
    \hline
        $\mathcal{N}(H)$ & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModNH}}
        \end{tabular} \\
    \hline
        $\mathcal{B}(H)$ & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModBH}}
        \end{tabular} \\ 
    \hline
        $\mathcal{K}(H)$ &
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModKH}}
        \end{tabular} \\ 
    \hline
    \multicolumn{7}{c}{
        \mbox{
            Homologically trivial $\mathcal{K}(H)$- 
            and $\mathcal{B}(H)$-modules in relative theory
        }
    } \\
    \hline & 
    \multicolumn{3}{c|}{
        $\mathcal{K}(H)$-modules
    } & 
    \multicolumn{3}{c|}{
        $\mathcal{B}(H)$-modules
    } \\
    \hline & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} \\ 
    \hline
        $\mathcal{N}(H)$ & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (ii)
        \end{tabular} \\
    \hline
        $\mathcal{B}(H)$ & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModsRelTh}}, (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (ii)
        \end{tabular} \\
    \hline
        $\mathcal{K}(H)$ & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\dim(H)<\aleph_0$ \\
            \mbox{\ref{KHAndBHModsRelTh}}, (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}} 
            {?}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $H$\mbox{ is any } \\
            \mbox{\ref{KHAndBHModsRelTh}}, (ii)
        \end{tabular} \\
    \hline
    \end{longtable}
\end{scriptsize}

%-------------------------------------------------------------------------------
%	c_0(\Lambda)- and l_infty(\Lambda)-modules
%-------------------------------------------------------------------------------

\subsection{
    \texorpdfstring{$c_0(\Lambda)$}{c0 (Lambda)}- and
    \texorpdfstring{$\ell_\infty(\Lambda)$}{lInfty(Lambda)}-modules}\label{
SubSectionc0AndlInftyModules}

We continue our study of modules over $C^*$-algebras and move to commutative
examples. For a given index set $\Lambda$ we consider spaces $c_0(\Lambda)$ and
$\ell_p(\Lambda)$ for $1\leq p\leq+\infty$ as left and right modules over
algebras $c_0(\Lambda)$ and $\ell_\infty(\Lambda)$. For all these modules the
module action is just the pointwise multiplication. It is well known that
${c_0(\Lambda)}^*\isom{\mathbf{Ban}_1}\ell_1(\Lambda)$ and
${\ell_p(\Lambda)}^*\isom{\mathbf{Ban}_1}\ell_{p^*}(\Lambda)$ 
for $1\leq p<+\infty$. In fact these isomorphisms are isomorphisms of
$\ell_\infty(\Lambda)$- and $c_0(\Lambda)$-modules. 

For a given $\lambda\in\Lambda$ we define $\mathbb{C}_\lambda$ as a left or right
$\ell_\infty(\Lambda)$- or $c_0(\Lambda)$-module $\mathbb{C}$ with module action
defined by
$$
a\cdot_\lambda z=a(\lambda)z,\qquad z\cdot_\lambda a=a(\lambda) z
$$
for $a\in \ell_\infty(\Lambda)$ or $a\in c_0(\Lambda)$ and $z\in\mathbb{C}_s$. 

\begin{proposition}\label{OneDimlInftyc0ModMetTopProjIngFlat} Let $\Lambda$ be a
set and $\lambda\in\Lambda$. Then $\mathbb{C}_\lambda$ is a metrically and
topologically projective, injective and flat $\ell_\infty(\Lambda)$- or
$c_0(\Lambda)$-module.
\end{proposition}
\begin{proof} Let $A$ be either $\ell_\infty(\Lambda)$ or $c_0(\Lambda)$. One
can easily check that the 
maps $\pi:A_+\to\mathbb{C}_\lambda,\, a\oplus_1 z\mapsto a(\lambda)+z$ 
and $\sigma:\mathbb{C}_\lambda\to A_+,\, z\mapsto z\delta_\lambda\oplus_1 0$ 
are contractive $A$-morphisms of left $A$-modules.
Since $\pi\sigma=1_{\mathbb{C}_\lambda}$, then $\mathbb{C}_\lambda$ is a retract
of $A_+$ in $A-\mathbf{mod}_1$. From proposition~\ref{UnitalAlgIsMetTopProj}
and~\ref{RetrMetCTopProjIsMetCTopProj} it follows that $\mathbb{C}_\lambda$ is a 
metrically and topologically projective left $A$-module and a fortiori
metrically and topologically flat by proposition~\ref{MetTopProjIsMetTopFlat}.
By proposition~\ref{DualMetTopProjIsMetrInj} we have that $\mathbb{C}_\lambda^*$
is metrically and topologically injective as $A$-module. Now metric and
topological injectivity of $\mathbb{C}_\lambda$ follow from isomorphism
$\mathbb{C}_\lambda\isom{\mathbf{mod}_1-A}\mathbb{C}_\lambda^*$.
\end{proof}

\begin{proposition}\label{c0AndlInftyModlIfty} Let $\Lambda$ be a set. Then

\begin{enumerate}[label = (\roman*)]
    \item $\ell_\infty(\Lambda)$ is metrically and topologically projective 
    and flat as $\ell_\infty(\Lambda)$-module;

    \item $\ell_\infty(\Lambda)$ is metrically or topologically projective 
    or flat as $c_0(\Lambda)$-module iff $\Lambda$ is finite;

    \item $\ell_\infty(\Lambda)$ is metrically and topologically injective as
    $\ell_\infty(\Lambda)$- and $c_0(\Lambda)$-module.
\end{enumerate}
\end{proposition}
\begin{proof} $(i)$ Since $\ell_\infty(\Lambda)$ is a unital algebra, then it is
metrically and topologically projective as $\ell_\infty(\Lambda)$-module by
proposition~\ref{UnitalAlgIsMetTopProj}. Results on flatness follow from
proposition~\ref{MetTopProjIsMetTopFlat}.

$(ii)$ For infinite $\Lambda$ the Banach space
$\ell_\infty(\Lambda)/c_0(\Lambda)$ is of infinite dimension, so by
proposition~\ref{CStarAlgIsTopFlatOverItsIdeal} the module
$\ell_\infty(\Lambda)$ is neither topologically nor metrically flat as
$c_0(\Lambda)$-module. Both claims regarding projectivity follow from
proposition~\ref{MetTopProjIsMetTopFlat}. If $\Lambda$ is finite, then
$c_0(\Lambda)=\ell_\infty(\Lambda)$, so the result follows from paragraph $(i)$.

$(iii)$ Let $A$ be either $\ell_\infty(\Lambda)$ or $c_0(\Lambda)$. Note that
$\ell_\infty(\Lambda)
\isom{A-\mathbf{mod}_1}
\bigoplus_\infty \{\mathbb{C}_\lambda:\lambda\in\Lambda \}$, then from
propositions~\ref{OneDimlInftyc0ModMetTopProjIngFlat} and~\ref{MetTopInjModProd}
it follows that $\ell_\infty(\Lambda)$ is metrically injective as $A$-module.
Topological injectivity follows from
proposition~\ref{MetInjIsTopInjAndTopInjIsRelInj}.
\end{proof}

\begin{proposition}\label{c0AndlInftyModc0} Let $\Lambda$ be a set. Then 

\begin{enumerate}[label = (\roman*)]
    \item $c_0(\Lambda)$ is metrically and topologically flat as
    $\ell_\infty(\Lambda)$- or $c_0(\Lambda)$-module;

    \item $c_0(\Lambda)$ is metrically or topologically projective as
    $\ell_\infty(\Lambda)$- or $c_0(\Lambda)$-module iff $\Lambda$ is finite;

    \item $c_0(\Lambda)$ is metrically or topologically injective as
    $\ell_\infty(\Lambda)$- or $c_0(\Lambda)$-module iff $\Lambda$ is finite.
\end{enumerate}
\end{proposition}
\begin{proof} Let $A$ be either $\ell_\infty(\Lambda)$ or $c_0(\Lambda)$. Note
that $c_0(\Lambda)$ is a two-sided ideal of $A$. 

$(i)$ Recall that $c_0(\Lambda)$ has a contractive approximate identity of the
form ${(\sum_{\lambda\in S}\delta_\lambda)}_{S\in\mathcal{P}_{f}(\Lambda)}$. Since
$c_0(\Lambda)$ is a two-sided ideal of $A$, then the result follows from
proposition~\ref{IdealofCstarAlgisMetTopFlat}.

$(ii)$, $(iii)$ If $\Lambda$ is infinite, then $c_0(\Lambda)$ is not unital as a 
Banach algebra. From corollary~\ref{BiIdealOfCStarAlgMetTopProjCharac} and
proposition~\ref{MetTopInjOfId} the $A$-module $c_0(\Lambda)$ is neither
metrically nor topologically projective or injective. If $\Lambda$ is finite,
then $c_0(\Lambda)=\ell_\infty(\Lambda)$, so both results follow from paragraphs
$(i)$ and $(iii)$ of proposition~\ref{c0AndlInftyModlIfty}.
\end{proof}

\begin{proposition}\label{c0AndlInftyModl1} Let $\Lambda$ be a set. Then

\begin{enumerate}[label = (\roman*)]
    \item $\ell_1(\Lambda)$ is metrically and topologically injective as
    $\ell_\infty(\Lambda)$- or $c_0(\Lambda)$-module;

    \item $\ell_1(\Lambda)$ is metrically and topologically projective and 
    flat as $\ell_\infty(\Lambda)$- or $c_0(\Lambda)$-module;
\end{enumerate}
\end{proposition}
\begin{proof} Let $A$ be either $\ell_\infty(\Lambda)$ or $c_0(\Lambda)$.

$(i)$ Note that $\ell_1(\Lambda)\isom{\mathbf{mod}_1-A}{c_0(\Lambda)}^*$, so the
result follows from proposition~\ref{MetCTopFlatCharac} and paragraph $(i)$ of
proposition~\ref{c0AndlInftyModc0}.

$(ii)$ Note that 
$\ell_1(\Lambda)
\isom{A-\mathbf{mod}_1}
\bigoplus_1 \{\mathbb{C}_\lambda:\lambda\in\Lambda \}$, then from
propositions~\ref{OneDimlInftyc0ModMetTopProjIngFlat}
and~\ref{MetTopProjModCoprod} it follows that $\ell_1(\Lambda)$ is metrically
projective as $A$-module. Topological projectivity follows from
proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj}. Metric and topological
flatness follow from proposition~\ref{MetTopProjIsMetTopFlat}.
\end{proof}

\begin{proposition}\label{c0AndlInftyModlp} Let $\Lambda$ be a set and
$1<p<+\infty$. Then $\ell_p(\Lambda)$ is metrically or topologically projective,
injective or flat as $\ell_\infty(\Lambda)$- or $c_0(\Lambda)$-module iff
$\Lambda$ is finite.

\begin{enumerate}[label = (\roman*)]
    \item $\ell_p(\Lambda)$ is topologically projective,
    injective or flat as $\ell_\infty(\Lambda)$- or $c_0(\Lambda)$-module iff
    $\Lambda$ is finite;

    \item if $\ell_p(\Lambda)$ is metrically projective,
    injective or flat as $\ell_\infty(\Lambda)$- or $c_0(\Lambda)$-module then
    $\Lambda$ is finite;
\end{enumerate}
\end{proposition}
\begin{proof} $(i)$, $(ii)$ Let $A$ be either $\ell_\infty(\Lambda)$ 
or $c_0(\Lambda)$, then $A$ is an $\mathscr{L}_\infty^g$-space. 
Since $\ell_p(\Lambda)$ is reflexive for $1<p<+\infty$, then from corollary
~\ref{NoInfDimRefMetTopProjInjFlatModOverMthscrL1OrLInfty} it follows that
$\ell_p(\Lambda)$ is necessarily finite dimensional if it is metrically or
topologically projective injective or flat. This is equivalent to $\Lambda$
being finite. If $\Lambda$ is finite then
$\ell_p(\Lambda)\isom{A-\mathbf{mod}}\ell_1(\Lambda)$ and
$\ell_p(\Lambda)\isom{\mathbf{mod}-A}\ell_1(\Lambda)$, so topological
projectivity injectivity and flatness follow from
proposition~\ref{c0AndlInftyModl1}.
\end{proof}

\begin{proposition}\label{c0AndlInftyModsRelTh} Let $\Lambda$ be a set. Then

\begin{enumerate}[label = (\roman*)]
    \item as $c_0(\Lambda)$-modules $\ell_p(\Lambda)$ for $1\leq p<+\infty$ and
    $\mathbb{C}_\lambda$ for $\lambda\in\Lambda$ are relatively projective,
    injective and flat, $c_0(\Lambda)$ is relatively projective and flat, but
    relatively injective only for finite $\Lambda$, $\ell_\infty(\Lambda)$ is
    relatively injective and flat, but relatively projective only for finite
    $\Lambda$;

    \item as $\ell_\infty(\Lambda)$-modules $\ell_p(\Lambda)$ for 
    $1\leq p\leq+\infty$ and $\mathbb{C}_\lambda$ for $\lambda\in\Lambda$ 
    are relatively projective, injective and flat, $c_0(\Lambda)$ is 
    relatively projective, injective and flat.
\end{enumerate}
\end{proposition}
\begin{proof} $(i)$ The algebra $c_0(\Lambda)$ is relatively biprojective
[\cite{HelHomolBanTopAlg}, theorem IV.5.26] and admits a contractive approximate
identity, so by [\cite{HelBanLocConvAlg}, theorem 7.1.60] all essential
$c_0(\Lambda)$-modules are projective. Thus, $c_0(\Lambda)$ and $\ell_p(\Lambda)$
for $1\leq p<+\infty$ are relatively projective $c_0(\Lambda)$-modules. A
fortiori they are relatively flat as $c_0(\Lambda)$-modules
[\cite{HelBanLocConvAlg}, proposition 7.1.40]. By the same proposition
$\ell_1(\Lambda)\isom{\mathbf{mod}_1-c_0(\Lambda)}{c_0(\Lambda)}^*$ and
$\ell_{p^*}(\Lambda)\isom{\mathbf{mod}_1-c_0(\Lambda)}{\ell_p(\Lambda)}^*$ for
$1\leq p<+\infty$ are relatively injective $c_0(\Lambda)$-modules. From
[\cite{RamsHomPropSemgroupAlg}, proposition 2.2.8 (i)] we know that a Banach
algebra which is relatively injective over itself as a right module, necessarily 
has a left identity. Therefore, $c_0(\Lambda)$ is not relatively injective
$c_0(\Lambda)$-module for infinite $\Lambda$. If $\Lambda$ is finite, then
$c_0(\Lambda)$-module $c_0(\Lambda)$ is relatively injective because
$c_0(\Lambda)=\ell_\infty(\Lambda)$ and $\ell_\infty(\Lambda)$ is relatively
injective $c_0(\Lambda)$-module as was shown above. From
[\cite{HelHomolBanTopAlg}, corollary V.2.16(II)] we know that
$\ell_\infty(\Lambda)$ is not relatively projective as $c_0(\Lambda)$-module
provided $\Lambda$ is infinite. If $\Lambda$ is finite then
$\ell_\infty(\Lambda)$ is relatively projective $c_0(\Lambda)$-module because
$\ell_\infty(\Lambda)=c_0(\Lambda)$ and $c_0(\Lambda)$ is relatively projective
$c_0(\Lambda)$-module as was shown above.
Propositions~\ref{OneDimlInftyc0ModMetTopProjIngFlat},
~\ref{MetProjIsTopProjAndTopProjIsRelProj},
~\ref{MetInjIsTopInjAndTopInjIsRelInj}
and~\ref{MetFlatIsTopFlatAndTopFlatIsRelFlat} give the result for modules
$\mathbb{C}_\lambda$, where $\lambda\in\Lambda$.

$(ii)$ From proposition~\ref{c0AndlInftyModlIfty} paragraph $(i)$ and
proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj} it follows that
$\ell_\infty(\Lambda)$ is a relatively projective $\ell_\infty(\Lambda)$-module. 
In [\cite{NemANoteOnRelInjC0ModC0}, theorem 4.4] it was shown 
that $\ell_\infty(\Lambda)$-module $c_0(\Lambda)$ is relatively injective. 
From [\cite{RamsHomPropSemgroupAlg}, propositions 2.3.3, 2.3.4] we know that
$\langle$~an essential relatively projective / a  faithful relatively
injective~$\rangle$ module over an ideal of a Banach algebra is 
$\langle$~relatively projective / relatively injective~$\rangle$ over the algebra 
itself. For each $1\leq p<+\infty$ the $c_0(\Lambda)$-module $\ell_p(\Lambda)$  
is essential and faithful, hence by results of 
the previous paragraph $\ell_p(\Lambda)$ is relatively projective and
injective as $\ell_\infty(\Lambda)$-module. Since $c_0(\Lambda)$-module 
$c_0(\Lambda)$ is essential and relatively projective, then analogously 
the $\ell_\infty(\Lambda)$-module $c_0(\Lambda)$ is relatively projective. 
Therefore, all these $\ell_\infty(\Lambda)$-modules are relatively 
flat [\cite{HelBanLocConvAlg}, proposition 7.1.40]. As a consequence 
$\ell_\infty(\Lambda)\isom{\mathbf{mod}_1-\ell_\infty(\Lambda)} {\ell_1(\Lambda)}^*$ 
is relatively injective $\ell_\infty(\Lambda)$-module.
Propositions~\ref{OneDimlInftyc0ModMetTopProjIngFlat},
~\ref{MetProjIsTopProjAndTopProjIsRelProj},
~\ref{MetInjIsTopInjAndTopInjIsRelInj}
and~\ref{MetFlatIsTopFlatAndTopFlatIsRelFlat} give the result for modules
$\mathbb{C}_\lambda$, where $\lambda\in\Lambda$.
\end{proof}

Results of this section are summarized in the following three tables. Each cell
contains a condition under which the respective module has the respective
property and propositions where this result is proved. For the case 
of $\ell_\infty(\Lambda)$- and $c_0(\Lambda)$-modules $\ell_p(\Lambda)$ 
for $1<p<+\infty$ we don't have a criterion of homological triviality in metric
theory, just a necessary condition. We indicate this fact via symbol ${}^*$.
From these tables one can easily see that for modules over commutative
$C^*$-algebras, there is much more in common between relative, metric and
topological  theory. For example $\ell_1(\Lambda)$ is projective injective and
flat as $\ell_\infty(\Lambda)$- or $c_0(\Lambda)$-module in all three theories.


\begin{scriptsize}
    \begin{longtable}{|c|c|c|c|c|c|c|} 
    \multicolumn{7}{c}{
        \mbox{
            Homologically trivial $c_0(\Lambda)$- 
            and $\ell_\infty(\Lambda)$-modules in metric theory
        }
    } \\ 
    \hline & 
    \multicolumn{3}{c|}{
        $c_0(\Lambda)$-modules
    } & 
    \multicolumn{3}{c|}{
        $\ell_\infty(\Lambda)$-modules
    } \\
    \hline & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} \\ 
    \hline
        $\ell_1(\Lambda)$ & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any }  \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} \\
    \hline 
        $\ell_p(\Lambda)$ & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\ 
            \mbox{\ref{c0AndlInftyModlp}}${}^*$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\ 
            \mbox{\ref{c0AndlInftyModlp}}${}^*$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\ 
            \mbox{\ref{c0AndlInftyModlp}}${}^*$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\ 
            \mbox{\ref{c0AndlInftyModlp}}${}^*$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\ 
            \mbox{\ref{c0AndlInftyModlp}}${}^*$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\ 
            \mbox{\ref{c0AndlInftyModlp}}${}^*$
        \end{tabular} \\
    \hline
        $\ell_\infty(\Lambda)$ & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} \\ 
    \hline
        $c_0(\Lambda)$ & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)< \aleph_0$ \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)< \aleph_0$ \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} \\ 
    \hline
        $\mathbb{C}_\lambda$ &
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} &
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} \\
    \hline 
    \multicolumn{7}{c}{
        \mbox{
            Homologically trivial $c_0(\Lambda)$- 
            and $\ell_\infty(\Lambda)$-modules in topological theory
        }
    } \\
    \hline & 
    \multicolumn{3}{c|}{
        $c_0(\Lambda)$-modules
    } & 
    \multicolumn{3}{c|}{
        $\ell_\infty(\Lambda)$-modules
    } \\
    \hline & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} \\ 
    \hline 
        $\ell_1(\Lambda)$ & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any }  \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any }  \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModl1}}
        \end{tabular} \\
    \hline
        $\ell_p(\Lambda)$ & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModlp}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModlp}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModlp}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModlp}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModlp}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModlp}}
        \end{tabular} \\
    \hline
        $\ell_\infty(\Lambda)$ & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModlIfty}}
        \end{tabular} \\ 
    \hline
        $c_0(\Lambda)$ &
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModc0}}
        \end{tabular} \\ 
    \hline
        $\mathbb{C}_\lambda$ & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{OneDimlInftyc0ModMetTopProjIngFlat}}
        \end{tabular} \\
    \hline
    \multicolumn{7}{c}{
        \mbox{
            Homologically trivial $c_0(\Lambda)$- 
            and $\ell_\infty(\Lambda)$-modules in relative theory
        }
    } \\
    \hline & 
    \multicolumn{3}{c|}{
        $c_0(\Lambda)$-modules
    } & 
    \multicolumn{3}{c|}{
        $\ell_\infty(\Lambda)$-modules
    } \\
    \hline & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} \\ 
    \hline
        $\ell_1(\Lambda)$ & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (ii)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (ii)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModlIfty}, (ii)}
        \end{tabular} \\
    \hline 
        $\ell_p(\Lambda)$ & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any }  \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any }  \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (ii)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (ii)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModlIfty}, (ii)}
        \end{tabular} \\
    \hline
        $\ell_\infty(\Lambda)$ & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any }  \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (ii)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (ii)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModlIfty}, (ii)}
        \end{tabular} \\
    \hline
        $c_0(\Lambda)$ &
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\operatorname{Card}(\Lambda)<\aleph_0$ \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i) }
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (ii)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}} 
            $\Lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (ii)} 
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\Lambda$\mbox{ is any }  \\
            \mbox{\ref{c0AndlInftyModlIfty}, (ii)}
        \end{tabular} \\
    \hline 
        $\mathbb{C}_\lambda$ & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any }  \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (i)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any }  \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (ii)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any } \\
            \mbox{\ref{c0AndlInftyModsRelTh}, (ii)}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\lambda$\mbox{ is any }  \\
            \mbox{\ref{c0AndlInftyModlIfty}, (ii)}
        \end{tabular} \\
    \hline
    \end{longtable}
\end{scriptsize}

%-------------------------------------------------------------------------------
%	C_0(S)-modules
%-------------------------------------------------------------------------------

\subsection{
    \texorpdfstring{$C_0(S)$}{C0(S)}-modules}\label{
SubSectionC0SModules}

This section is devoted to the study of homological triviality of classical modules
over the algebra $C_0(S)$, where $S$ is a locally compact Hausdorff space. By
classic we mean modules $C_0(S)$, $M(S)$ and $L_p(S,\mu)$ for positive measures
$\mu\in M(S)$. The pointwise multiplication plays the role of module action for
these modules.

We shall give short preliminaries on these modules. Recall that
${C_0(S)}^*\isom{\mathbf{Ban}_1}M(S)$ and
${L_p(S,\mu)}^*\isom{\mathbf{Ban}_1}L_{p^*}(S,\mu)$ for $1\leq p<+\infty$. 
In fact these identifications are isomorphisms of left and 
right $C_0(S)$-modules. For a given positive measure $\mu\in M(S)$ 
by $M_s(S,\mu)$ we shall denote the closed $C_0(S)$-submodule of $M(S)$ 
consisting of measures strictly singular with respect to $\mu$. Then the well 
known Lebesgue decomposition theorem can be stated 
as $M(S)\isom{\mathbf{Ban}_1}L_1(S,\mu)\bigoplus_1 M_s(S,\mu)$. Even
more, this identification is an isomorphism of left and right $C_0(S)$-modules. 

We obliged to emphasize here that we consider only finite Borel regular positive
measures. This shall simplify many considerations. For example, any atom of a 
regular measure on a locally compact Hausdorff spaces is a point
[\cite{BourbElemMathIntegLivVI}, chapter 5, \S 5, exercise 7]. Since we consider
only finite measures, one cannot say that this section simply generalizes
results of the previous one. Strictly speaking these sections are different,
though their methods have much in common.

For a fixed point $s\in S$ by $\mathbb{C}_s$ we denote the left or right Banach
$C_0(S)$-module $\mathbb{C}$ with module action defined by
$$
a\cdot_s z=a(s)z,\qquad z\cdot_s a=a(s)z
$$
\begin{proposition}\label{OneDimC0SModMetTopRelProjIngFlat} Let $S$ be a locally
compact Hausdorff space and let $s\in S$. Then 

\begin{enumerate}[label = (\roman*)]
    \item $\mathbb{C}_s$ is a metrically, topologically or relatively projective 
    $C_0(S)$-module iff $s$ is an isolated point of $S$;

    \item $\mathbb{C}_s$ is a metrically, topologically and relatively flat 
    $C_0(S)$-module.

    \item $\mathbb{C}_s$ is a metrically, topologically and relatively injective 
    $C_0(S)$-module;

\end{enumerate}
\end{proposition}
\begin{proof} $(i)$ If $\mathbb{C}_s$ is metrically or topologically or
relatively projective, then by
proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj} it is at least relatively
projective. Now from [\cite{HelBanLocConvAlg}, proposition 7.1.31] we know that
the latter forces $s$ to be an isolated point of $S$. Conversely, assume that 
$s$ is an isolated point of $S$. One can easily check that the maps
$\pi:{C_0(S)}_+\to\mathbb{C}_s,\, a\oplus_1 z\mapsto a(s)+z$ and
$\sigma:\mathbb{C}_s\to {C_0(S)}_+,\, z\mapsto z\delta_s\oplus_1 0$ are contractive
$C_0(S)$-morphisms. Since $\pi\sigma=1_{\mathbb{C}_s}$, then $\mathbb{C}_s$ is a
retract of ${C_0(S)}_+$ in $C_0(S)-\mathbf{mod}_1$. From
propositions~\ref{RetrMetCTopProjIsMetCTopProj} and~\ref{UnitalAlgIsMetTopProj} 
it follows that $\mathbb{C}_s$ is a metrically and topologically projective left
$C_0(S)$-module. From~\ref{MetProjIsTopProjAndTopProjIsRelProj} we conclude that
$\mathbb{C}_s$ is also relatively projective $C_0(S)$-module.

$(ii)$ By [\cite{HelBanLocConvAlg}, theorem 7.1.87] the algebra $C_0(S)$ is
relatively amenable. Since this algebra is a $C^*$-algebra it is $1$-relatively 
amenable [\cite{RundeAmenConstFour}, example 3]. Clearly, $\mathbb{C}_s$ is a
$1$-dimensional $L_1$-space and an essential $C_0(S)$-module. Therefore, by
proposition~\ref{MetTopEssL1FlatModAoverAmenBanAlg} this module is metrically
flat. Now the result follows from
proposition~\ref{MetFlatIsTopFlatAndTopFlatIsRelFlat}.

$(iii)$ From paragraph $(ii)$ and proposition~\ref{MetCTopFlatCharac} it follows
that the $C_0(S)$-module $\mathbb{C}_s^*$ is metrically injective. By
proposition~\ref{MetFlatIsTopFlatAndTopFlatIsRelFlat} it is topologically and
relatively injective too. It remains to note that
$\mathbb{C}_s\isom{\mathbf{mod}_1-A}\mathbb{C}_s^*$. 
\end{proof}

\begin{proposition}\label{C0SC0SModMetTopRelProjInjFlat} Let $S$ be a locally
compact Hausdorff space and let $s\in S$. Then

\begin{enumerate}[label = (\roman*)]
    \item $C_0(S)$ is a $\langle$~metrically / 
    topologically / relatively~$\rangle$
    projective $C_0(S)$-module iff $S$ is $\langle$~compact / compact /
    paracompact~$\rangle$;

    \item $C_0(S)$ is a metrically injective as $C_0(S)$-module iff $S$ is 
    a Stonean space; if $C_0(S)$ is topologically or relatively injective then
    $S$ is compact and $S=\beta(S\setminus \{ s\})$ for any limit point $s\in S$;

    \item $C_0(S)$ is a metrically, topologically and relatively flat 
    $C_0(S)$-module.
\end{enumerate}
\end{proposition}
\begin{proof} We regard $C_0(S)$ as a two-sided ideal of $C_0(S)$. Recall that
$\operatorname{Spec}(C_0(S))$ is homeomorphic to $S$ [\cite{HelHomolBanTopAlg},
corollary 3.1.6].

$(i)$ It is enough to note that by
$\langle$~proposition~\ref{IdealofCommCStarAlgMetTopProjCharac} /
proposition~\ref{IdealofCommCStarAlgMetTopProjCharac} /
[\cite{HelHomolBanTopAlg}, chapter IV,\S\S 2--3]~$\rangle$ the spectrum of
$C_0(S)$ is $\langle$~compact / compact / paracompact~$\rangle$. 

$(ii)$ The result on metric injectivity is a weakened version of
proposition~\ref{MetInjCStarAlgCharac}. The result on relatively injectivity 
follows from~[\cite{NemANoteOnRelInjC0ModC0}, theorem 4.4]. It remains to recall
that by proposition~\ref{MetInjIsTopInjAndTopInjIsRelInj} any metrically injective
module is relatively injective.

$(iii)$ From proposition~\ref{IdealofCstarAlgisMetTopFlat} it immediately follows
that $C_0(S)$-module $C_0(S)$ is metrically and topologically flat. By
proposition~\ref{MetFlatIsTopFlatAndTopFlatIsRelFlat} it is also relatively
flat.
\end{proof}

\begin{proposition}\label{AtomsOfRelProjLpMod} Let $S$ be a locally compact
Hausdorff space, $\mu$ be a finite positive Borel regular measure on $S$. Assume 
that $1\leq p\leq+\infty$ and $C_0(S)$-module $L_p(S,\mu)$ is relatively 
projective. Then any atom of $\mu$ is an isolated point in $S$.
\end{proposition} 
\begin{proof} Assume $\mu$ has at least one atom, otherwise there is nothing to
prove. From [\cite{BourbElemMathIntegLivVI}, chapter 5, \S 5, exercise 7] we
know that any atom of $\mu$ is a point. Call it $s\in S$. Consider well-defined
linear maps $\pi:L_p(\Omega,\mu)\to\mathbb{C}_s:f\mapsto f(s)$ and
$\sigma:\mathbb{C}_s\to L_p(\Omega,\mu):z\mapsto z\delta_s$. One can easily
check that these maps are $C_0(S)$-morphisms and $\pi\sigma=1_{\mathbb{C}_s}$.
Therefore, $\mathbb{C}_s$ is a retract of $L_p(S,\mu)$ in $C_0(S)-\mathbf{mod}$.
By assumption, the latter module is relatively projective, so by
[\cite{HelBanLocConvAlg}, proposition 7.1.6] the $C_0(S)$-module $\mathbb{C}_s$
is relatively projective. By paragraph $(i)$ of
proposition~\ref{C0SC0SModMetTopRelProjInjFlat} we see that $s$ is an isolated
point of $S$.
\end{proof}

\begin{proposition}\label{L1C0SModMetTopRelProjInjFlat} Let $S$ be a locally
compact Hausdorff space and $\mu$ be a finite Borel regular positive measure on
$S$. Then 

\begin{enumerate}[label = (\roman*)]
    \item $L_1(S,\mu)$ is a metrically or topologically or relatively projective 
    $C_0(S)$-module iff $\mu$ is purely atomic and all its atoms are 
    isolated points in $S$;

    \item $L_1(S,\mu)$ is a metrically, topologically and relatively injective 
    $C_0(S)$-module;

    \item $L_1(S,\mu)$ is a metrically, topologically and relatively flat
    $C_0(S)$-module.
\end{enumerate}
\end{proposition}
\begin{proof} $(i)$ If $L_1(S,\mu)$ is metrically or topologically or relatively
projective, then by proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj} it is
at least relatively projective. Now from [\cite{NemRelProjModLp}, theorem 2] 
the measure $\mu$ is purely atomic, and all atoms are isolated  points.
Conversely, assume that $\mu$ is purely atomic, and all atoms are isolated
points. By $S_a^{\mu}$ we denote the set of these atoms. Now one can easily show
that the linear map 
$i:L_1(S,\mu)\to\bigoplus_1 \{\mathbb{C}_s:s\in S_a^{\mu} \}
:f\mapsto \bigoplus_1 \{\mu( \{s \})f(s):s\in S_a^{\mu} \}$ is an isometric
isomorphism of $C_0(S)$-modules. By paragraphs $(i)$ of
propositions~\ref{MetTopProjModCoprod}
and~\ref{OneDimC0SModMetTopRelProjIngFlat} the $C_0(S)$-module $\bigoplus_1
\{\mathbb{C}_s:s\in S_a^{\mu} \}$ is metrically projective. Therefore, so is
$L_1(S,\mu)$. By proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj} it is
also topologically and relatively projective.

$(ii)$ By paragraph $(iii)$ of proposition~\ref{C0SC0SModMetTopRelProjInjFlat} 
the $C_0(S)$-module $C_0(S)$ is metrically flat. From
proposition~\ref{DualMetTopProjIsMetrInj} we get that
$M(S)\isom{\mathbf{mod}_1-C_0(S)}{C_0(S)}^*$ is metrically injective. Since
$M(S)\isom{\mathbf{mod}_1-C_0(S)}L_1(S,\mu)\bigoplus_1 M_s(S,\mu)$, then
$L_1(S,\mu)$ is a retract of $M(S)$ in $\mathbf{mod}_1-C_0(S)$. So by
proposition~\ref{RetrMetCTopInjIsMetCTopInj} the $C_0(S)$-module $L_1(S,\mu)$ is
metrically injective. Relative and topological injectivity of $L_1(S,\mu)$
follows from proposition~\ref{MetInjIsTopInjAndTopInjIsRelInj}.

$(iii)$ By [\cite{HelBanLocConvAlg}, theorem 7.1.87] the algebra $C_0(S)$ is
relatively amenable. Since this algebra is a $C^*$-algebra it is $1$-relatively 
amenable [\cite{RundeAmenConstFour}, example 3]. Since $L_1(S,\mu)$ is 
an essential $C_0(S)$-module which tautologically an $L_1$-space, then by
proposition~\ref{MetTopEssL1FlatModAoverAmenBanAlg} this module is metrically
flat. From proposition~\ref{MetFlatIsTopFlatAndTopFlatIsRelFlat} the
$C_0(S)$-module $L_1(S,\mu)$ is also topologically and relatively flat.
\end{proof}

\begin{proposition}\label{LpC0SModMetTopRelProjIngFlat} Let $S$ be a locally
compact Hausdorff space and $\mu$ be a finite Borel regular positive measure on
$S$. Assume $1<p<+\infty$, then 

\begin{enumerate}[label = (\roman*)]
    \item $L_p(S,\mu)$ is a relatively injective and flat, but relatively 
    projective $C_0(S)$-module iff $\mu$ is purely atomic, and all atoms 
    are isolated points;

    \item $L_p(S,\mu)$ is a topologically projective or injective or flat 
    $C_0(S)$-module iff $\mu$ is purely atomic with finitely many atoms;

    \item if $L_p(S,\mu)$ is a metrically projective or injective or flat 
    $C_0(S)$-module, then $\mu$ is purely atomic with finitely many atoms.
\end{enumerate}
\end{proposition}
\begin{proof} $(i)$ By [\cite{HelBanLocConvAlg}, theorem 7.1.87] the algebra
$C_0(S)$ is relatively amenable. Now from [\cite{HelBanLocConvAlg}, theorem
7.1.60] it follows that $L_p(S,\mu)$ is relatively flat for all $1<p<+\infty$.
Note that $L_p(S,\mu)\isom{\mathbf{mod}_1-C_0(S)}{L_ a{p^*}(S,\mu)}^*$. Then from
[\cite{HelBanLocConvAlg}, proposition 7.1.42] we get that $L_p(S,\mu)$ is
relatively injective for any $1<p<+\infty$. Now assume that $L_p(S,\mu)$ is
relatively projective, then by [\cite{NemRelProjModLp}, theorem 2]
the measure $\mu$ is purely atomic and all its atoms are isolated points.
Conversely, let $\mu$ be purely atomic with all atoms isolated. Denote by
$S_a^{\mu}$ the set of these atoms. Since $S_a^{\mu}$ is discrete, then
$C_0(S_a^{\mu})$ is relatively biprojective [\cite{HelHomolBanTopAlg}, theorem
4.5.26]. Then $L_p(S,\mu)$ is a relatively projective $C_0(S_a^{\mu})$-module
because it is an essential module over a relatively biprojective algebra with
a two-sided bounded approximate identity. Clearly $C_0(S_a^{\mu})$ is a closed 
two-sided ideal of $C_0(S)$, so 
from [\cite{RamsHomPropSemgroupAlg}, proposition 2.3.2(i)]
we get that $L_p(S,\mu)$ is relatively projective as $C_0(S)$-module.

$(ii), (iii)$ Assume that $L_p(S,\mu)$ is a metrically or topologically projective
or injective or flat $C_0(S)$-module. Since $L_p(S,\mu)$ is reflexive and
$C_0(S)$ is an $\mathscr{L}_\infty^g$-space, then $L_p(S,\mu)$ is finite
dimensional by
corollary~\ref{NoInfDimRefMetTopProjInjFlatModOverMthscrL1OrLInfty}. The latter
is equivalent to measure $\mu$ being purely atomic with finitely many atoms. On
the other hand, if $\mu$ is purely atomic with finitely many atoms, then
$L_p(S,\mu)$ is topologically isomorphic to $L_1(S,\mu)$ as a left or right
$C_0(S)$-module. The latter module is topologically projective, injective and
flat by proposition~\ref{L1C0SModMetTopRelProjInjFlat}. Hence, so is $L_p(S,\mu)$.
\end{proof}

\begin{proposition}\label{LinftyC0SModMetTopRelProjIngFlat} Let $S$ be a locally
compact Hausdorff space and $\mu$ be a finite positive Borel regular measure on
$S$. Then

\begin{enumerate}[label = (\roman*)]
    \item if $L_\infty(S,\mu)$ is a metrically, topologically or relatively 
    projective $C_0(S)$-module, then $\mu$ is a normal measure 
    with pseudocompact support; 

    \item $L_\infty(S,\mu)$ is a metrically, topologically and relatively 
    injective $C_0(S)$-module;

    \item $L_\infty(S,\mu)$ is a relatively flat $C_0(S)$-module.
\end{enumerate}
\end{proposition}
\begin{proof} $(i)$ From [\cite{NemRelProjModLp}, theorem 3] it follows 
that $\operatorname{supp}(\mu)$ is pseudocompact and $\mu$ is inner open 
regular. Since $\mu$ is regular and finite it is 
normal [\cite{NemRelProjModLp}, proposition 9].
    
$(ii)$ Since
$L_\infty(S,\mu)\isom{\mathbf{mod}_1-C_0(S)}{L_1(S,\mu)}^*$, then the result
immediately follows from proposition~\ref{DualMetTopProjIsMetrInj} and paragraph
$(iii)$ of proposition~\ref{L1C0SModMetTopRelProjInjFlat}.

$(iii)$ By [\cite{HelBanLocConvAlg}, theorem 7.1.87] the algebra $C_0(S)$ is
relatively amenable. Any left Banach module over a relatively amenable Banach
algebra is relatively flat [\cite{HelBanLocConvAlg}, theorem 7.1.60]. In
particular $L_\infty(S,\mu)$ is a relatively flat $C_0(S)$-module.
\end{proof}

\begin{proposition}\label{MSC0SModMetTopRelProjIngFlat} Let $S$ be a locally
compact Hausdorff space and $\mu$ be a finite positive Borel regular measure on
$S$. Then

\begin{enumerate}[label = (\roman*)]
    \item $M(S)$ is a metrically or topologically or relatively projective 
    $C_0(S)$-module iff $S$ is discrete; 

    \item $M(S)$ is a metrically, topologically and relatively injective 
    $C_0(S)$-module; 

    \item $M(S)$ is a metrically, topologically and relatively flat 
    $C_0(S)$-module.
\end{enumerate}
\end{proposition}
\begin{proof} $(i)$ If the $C_0(S)$-module $M(S)$ is metrically or topologically 
or relatively projective, then by proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj} 
it is at least relatively projective. For arbitrary $s\in S$ consider measure
$\mu=\delta_s$ and recall the decomposition
$M(S)\isom{C_0(S)-\mathbf{mod}_1}L_1(S,\mu)\bigoplus_1 M_s(S,\mu)$. Then
$L_1(S,\mu)$ is a retract of $M(S)$ in $C_0(S)-\mathbf{mod}_1$. So from
[\cite{HelBanLocConvAlg}, proposition 7.1.6] we get that $L_1(S,\mu)$ is
relatively projective $C_0(S)$-module. Since $s$ is the only atom of $\mu$, then
from proposition~\ref{L1C0SModMetTopRelProjInjFlat} it follows that $s$ is an
isolated point in $S$. Since $s\in S$ is arbitrary, then $S$ is discrete.
Conversely, assume $S$ is discrete. Then $C_0(S)=c_0(S)$, and
$M(S)
\isom{C_0(S)-\mathbf{mod}_1}{C_0(S)}^*
\isom{C_0(S)-\mathbf{mod}_1}\ell_1(S)
\isom{C_0(S)-\mathbf{mod}_1}
\bigoplus_1 \{\mathbb{C}_s:s\in S \}$. The latter $C_0(S)$-module is metrically
projective by paragraphs $(i)$ of propositions~\ref{MetTopProjModCoprod}
and~\ref{OneDimC0SModMetTopRelProjIngFlat}. Therefore, $M(S)$ is a metrically
projective $C_0(S)$-module too. By
proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj} it is also topologically
and relatively projective.

$(ii)$ Since $M(S)\isom{\mathbf{mod}_1-C_0(S)}{C_0(S)}^*$, then the result
immediately follows from proposition~\ref{DualMetTopProjIsMetrInj} and paragraph
$(iii)$ of proposition~\ref{C0SC0SModMetTopRelProjInjFlat}.

$(iii)$ By [\cite{HelBanLocConvAlg}, theorem 7.1.87] the algebra $C_0(S)$ is
relatively amenable. Since this algebra is a $C^*$-algebra it is $1$-relatively 
amenable [\cite{RundeAmenConstFour}, example 2]. Note that $M(S)$ is 
an essential $C_0(S)$-module which as Banach space is an $L_1$-space
[\cite{DalLauSecondDualOfMeasAlg}, discussion after proposition 2.14]. Then by
proposition~\ref{MetTopEssL1FlatModAoverAmenBanAlg} this module is metrically
flat. From proposition~\ref{MetFlatIsTopFlatAndTopFlatIsRelFlat} it is also
topologically and relatively flat.
\end{proof}

Results of this section are summarized in the following three tables. Each cell
contains a condition under which the respective module has the respective
property and propositions where this result is proved. We use ``?'' symbol to 
indicate open problems, and ``*'' symbol for partial results. 

Below is a short overview of unsolved problems of this section. We don't have 
a complete description of relatively and topologically injective $C_0(S)$-modules 
$C_0(S)$. It seems quite a challenge for one simple reason --- to this day there is 
no standard category of functional analysis where topologically injective 
objects were fully understood. The question of relative
projectivity of $C_0(S)$-module $L_\infty(S,\mu)$ is rather old. It seems that
even relative projectivity of $L_\infty(S,\mu)$ is a rare property. Our
conjecture that $\mu$ must be normal and $S$ must be hyper-Stonean. For metric and 
topological flatness of $C_0(S)$-module $L_\infty(S,\mu)$ we conjecture that $\mu$
must have a compact support. Neither do we have a criterion of homological triviality 
of $C_0(S)$-modules $L_p(S,\mu)$ in metric theory for $1<p<+\infty$. Using advanced
Banach geometric techniques on factorization constants through finite
dimensional Hilbert spaces one may show that atoms count must not exceed some 
universal constant. It seems that $L_p(S,\mu)$ is homologically trivial 
$C_0(S)$-module in metric theory only for purely atomic measures with a unique atom. 

\begin{scriptsize}
    \begin{longtable}{|c|c|c|c|} 
    \multicolumn{4}{c}{
        \mbox{
            Homologically trivial $C_0(S)$-modules in metric theory
        }
    } \\
    \hline & 
    \mbox{Projectivity} & 
    \mbox{Injectivity} & 
    \mbox{Flatness} \\
    \hline
        $L_1(S,\mu)$ & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is purely atomic, all } \\ 
            \mbox{ atoms are isolated points } \\
            \mbox{\ref{L1C0SModMetTopRelProjInjFlat}} (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any }  \\
            \mbox{\ref{L1C0SModMetTopRelProjInjFlat}} (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any }  \\
            \mbox{\ref{L1C0SModMetTopRelProjInjFlat}} (iii)
        \end{tabular} \\
    \hline
        $L_p(S,\mu)$ & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is purely atomic } \\ 
            \mbox{ with finitely many atoms } \\ 
            \mbox{\ref{LpC0SModMetTopRelProjIngFlat}} (iii)${}^{*}$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is purely atomic } \\ 
            \mbox{ with finitely many atoms } \\ 
            \mbox{\ref{LpC0SModMetTopRelProjIngFlat}} (iii)${}^{*}$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is purely atomic } \\ 
            \mbox{ with finitely many atoms } \\ 
            \mbox{\ref{LpC0SModMetTopRelProjIngFlat}} (iii)${}^{*}$
        \end{tabular} \\
    \hline
        $L_\infty(S,\mu)$ & 
        \begin{tabular}{@{}c@{}} 
            $\mu$ is normal, with \\
            pseudocompact support \\
            \mbox{\ref{LinftyC0SModMetTopRelProjIngFlat}} (i)${}^{*}$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any } \\
            \mbox{\ref{LinftyC0SModMetTopRelProjIngFlat}} (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}} 
            {?}
        \end{tabular} \\
    \hline
        $M(S)$ & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is discrete } \\
            \mbox{\ref{MSC0SModMetTopRelProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is any } \\
            \mbox{\ref{MSC0SModMetTopRelProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is any } \\
            \mbox{\ref{MSC0SModMetTopRelProjIngFlat}}
        \end{tabular} \\
    \hline
        $C_0(S)$ & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is compact } \\
            \mbox{\ref{C0SC0SModMetTopRelProjInjFlat}} (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is Stonean } \\
            \mbox{\ref{C0SC0SModMetTopRelProjInjFlat}} (ii) 
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is any } \\
            \mbox{\ref{C0SC0SModMetTopRelProjInjFlat}} (iii)
        \end{tabular} \\
    \hline
        $\mathbb{C}_s$ & 
        \begin{tabular}{@{}c@{}}
            $s$\mbox{ is an isolated point } \\
            \mbox{\ref{OneDimC0SModMetTopRelProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $s$\mbox{ is any } \\
            \mbox{\ref{OneDimC0SModMetTopRelProjIngFlat}}
        \end{tabular} &
        \begin{tabular}{@{}c@{}}
            $s$\mbox{ is any } \\
            \mbox{\ref{OneDimC0SModMetTopRelProjIngFlat}}
        \end{tabular} \\
    \hline
    \multicolumn{4}{c}{
        \mbox{
            Homologically trivial $C_0(S)$-modules in topological theory
        }
    } \\
    \hline & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} \\
    \hline
        $L_1(S,\mu)$ & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is purely atomic, all } \\ 
            \mbox{ atoms are isolated points } \\
            \mbox{\ref{L1C0SModMetTopRelProjInjFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any }  \\
            \mbox{\ref{L1C0SModMetTopRelProjInjFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any } \\
            \mbox{\ref{L1C0SModMetTopRelProjInjFlat}}
        \end{tabular} \\
    \hline
        $L_p(S,\mu)$ & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is purely atomic } \\ 
            \mbox{ with finitely many atoms } \\
            \mbox{\ref{LpC0SModMetTopRelProjIngFlat}} (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is purely atomic } \\ 
            \mbox{ with finitely many atoms } \\
            \mbox{\ref{LpC0SModMetTopRelProjIngFlat}} (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is purely atomic } \\ 
            \mbox{ with finitely many atoms } \\
            \mbox{\ref{LpC0SModMetTopRelProjIngFlat}} (ii)
        \end{tabular} \\
    \hline
        $L_\infty(S,\mu)$ & 
        \begin{tabular}{@{}c@{}} 
            $\mu$ is normal, with \\
            pseudocompact support \\
            \mbox{\ref{LinftyC0SModMetTopRelProjIngFlat}} (i)${}^{*}$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any } \\
            \mbox{\ref{LinftyC0SModMetTopRelProjIngFlat}} (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            {?}
        \end{tabular} \\
    \hline
        $M(S)$ & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is discrete } \\
            \mbox{\ref{MSC0SModMetTopRelProjIngFlat}} (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is any } \\
            \mbox{\ref{MSC0SModMetTopRelProjIngFlat}} (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is any } \\
            \mbox{\ref{MSC0SModMetTopRelProjIngFlat}} (iii)
        \end{tabular} \\
    \hline
        $C_0(S)$ & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is compact } \\
            \mbox{\ref{C0SC0SModMetTopRelProjInjFlat}} (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}} 
            $S=\beta(S\setminus \{s \})$ \\
            for any limit point $s$ \\
            \mbox{\ref{C0SC0SModMetTopRelProjInjFlat}} (ii)${}^{*}$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is any } \\
            \mbox{\ref{C0SC0SModMetTopRelProjInjFlat}} (iii)
        \end{tabular} \\
    \hline
        $\mathbb{C}_s$ & 
        \begin{tabular}{@{}c@{}}
            $s$\mbox{ is an isolated point } \\
            \mbox{\ref{OneDimC0SModMetTopRelProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $s$\mbox{ is any } \\
            \mbox{\ref{OneDimC0SModMetTopRelProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $s$\mbox{ is any } \\
            \mbox{\ref{OneDimC0SModMetTopRelProjIngFlat}}
        \end{tabular} \\
    \hline
    \multicolumn{4}{c}{
        \mbox{
            Homologically trivial $C_0(S)$-modules in relative theory
        }
    } \\
    \hline & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} \\
    \hline
        $L_1(S,\mu)$ & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is purely atomic, all } \\ 
            \mbox{ atoms are isolated points } \\
            \mbox{\ref{L1C0SModMetTopRelProjInjFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any }  \\
            \mbox{\ref{L1C0SModMetTopRelProjInjFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any } \\
            \mbox{\ref{L1C0SModMetTopRelProjInjFlat}}
        \end{tabular} \\
    \hline
        $L_p(S,\mu)$ & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is purely atomic, all } \\ 
            \mbox{ atoms are isolated points } \\
            \mbox{\ref{LpC0SModMetTopRelProjIngFlat}} (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any } \\
            \mbox{\ref{LpC0SModMetTopRelProjIngFlat}} (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any } \\
            \mbox{\ref{LpC0SModMetTopRelProjIngFlat}} (i)
        \end{tabular} \\
    \hline
        $L_\infty(S,\mu)$ & 
        \begin{tabular}{@{}c@{}} 
            $\mu$ is normal, with \\
            pseudocompact support \\
            \mbox{\ref{LinftyC0SModMetTopRelProjIngFlat}} (i)${}^{*}$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any } \\
            \mbox{\ref{LinftyC0SModMetTopRelProjIngFlat}} (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $\mu$\mbox{ is any } \\
            \mbox{\ref{LinftyC0SModMetTopRelProjIngFlat}} (iii)
        \end{tabular} \\
    \hline
        $M(S)$ & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is discrete } \\
            \mbox{\ref{MSC0SModMetTopRelProjIngFlat}} (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is any } \\
            \mbox{\ref{MSC0SModMetTopRelProjIngFlat}} (ii)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is any } \\
            \mbox{\ref{MSC0SModMetTopRelProjIngFlat}} (iii)
        \end{tabular} \\
    \hline
        $C_0(S)$ & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is paracompact } \\
            \mbox{\ref{C0SC0SModMetTopRelProjInjFlat}} (i)
        \end{tabular} & 
        \begin{tabular}{@{}c@{}} 
            $S=\beta(S\setminus \{s \})$ \\
            for any limit point $s$ \\
            \mbox{\ref{C0SC0SModMetTopRelProjInjFlat}} (ii)${}^{*}$
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $S$\mbox{ is any } \\
            \mbox{\ref{C0SC0SModMetTopRelProjInjFlat}} (iii)
        \end{tabular} \\
    \hline  
        $\mathbb{C}_s$ & 
        \begin{tabular}{@{}c@{}}
            $s$\mbox{ is an isolated point } \\
            \mbox{\ref{OneDimC0SModMetTopRelProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $s$\mbox{ is any } \\
            \mbox{\ref{OneDimC0SModMetTopRelProjIngFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $s$\mbox{ is any } \\
            \mbox{\ref{OneDimC0SModMetTopRelProjIngFlat}}
        \end{tabular} \\
    \hline
    \end{longtable}
\end{scriptsize}


%-------------------------------------------------------------------------------
%	Applications to harmonic analysis
%-------------------------------------------------------------------------------

\section{
    Applications to modules of harmonic analysis}\label{
SectionApplicationsToModulesOfHarmonicAnalysis}

%-------------------------------------------------------------------------------
%	Preliminaries on harmonic analysis
%-------------------------------------------------------------------------------

\subsection{
    Preliminaries on harmonic analysis}\label{
SectionPreliminariesOnHarmonicAnalysis} 

Let $G$ be a locally compact group. Its identity we shall denote by $e_G$. By
well known Haar's theorem [\cite{HewRossAbstrHarmAnalVol1},section 15.8] there
exists a unique up to a positive constant Borel regular measure $m_G$ which is
finite on all compact sets, positive on all open sets and left translation
invariant, that is $m_G(sE)=m_G(E)$ for all $s\in G$ and $E\in Bor(G)$. It is
called the left Haar measure of group $G$. If $G$ is compact we assume that 
$m_G(G)=1$. If $G$ is infinite and discrete we choose $m_G$ as the counting measure.
For each $s\in G$ the map $m:Bor(G)\to[0,+\infty]:E\mapsto m_G(Es)$ is also a
left Haar measure, so from uniqueness we infer that $m(E)=\Delta_G(s)m_G(E)$ for
some $\Delta_G(s)>0$. The function $\Delta_G:G\to(0,+\infty)$ is called the
modular function of the group $G$. It is clear that
$\Delta_G(st)=\Delta_G(s)\Delta_G(t)$ for all $s,t\in G$. Groups with modular
function equal to one are called unimodular. Examples of unimodular groups 
include compact groups, commutative groups and discrete groups. In what
follows we use the notation $L_p(G)$ instead of $L_p(G,m_G)$ 
for $1\leq p\leq+\infty$. For a fixed $s\in G$ we define the left shift operator
$L_s:L_1(G)\to L_1(G),\, f\mapsto(t\mapsto f(s^{-1}t))$ and the right shift
operator $R_s:L_1(G)\to L_1(G),\, f\mapsto (t\mapsto f(ts))$. 

Group structure of $G$ allows us to introduce the Banach algebra structure on
$L_1(G)$. For a given $f,g\in L_1(G)$ we define their convolution as
$$
(f\convol g)(s)=\int_G f(t)g(t^{-1}s)dm_G(t)=\int_G f(st)g(t^{-1})dm_G(t)
$$
$$=\int_G f(st^{-1})g(t)\Delta_G(t^{-1})dm_G(t)
$$
for almost all $s\in G$. In this case the Banach space $L_1(G)$ endowed with 
convolution product becomes a Banach algebra. The Banach algebra $L_1(G)$ has a 
contractive two-sided approximate identity consisting of positive compactly 
supported continuous functions. The algebra $L_1(G)$ is unital iff $G$ is 
discrete, and in this case $\delta_{e_G}$ is the identity of $L_1(G)$. 
Group structure of $G$ allows us to turn the Banach space of complex finite 
Borel regular measures $M(G)$ into a Banach algebra too. We define the 
convolution of two measures $\mu,\nu\in M(G)$ as
$$
(\mu\convol \nu)(E)=\int_G\nu(s^{-1}E)d\mu(s)=\int_G\mu(Es^{-1})d\nu(s)
$$
for all $E\in Bor(G)$. The Banach space $M(G)$ along with this convolution is 
a unital Banach algebra. The role of identity is played by Dirac's delta 
measure $\delta_{e_G}$ supported on $e_G$. In fact $M(G)$ is a coproduct 
in $L_1(G)-\mathbf{mod}_1$ (but not in $M(G)-\mathbf{mod}_1$) of the 
closed two-sided ideal $M_a(G)$ of measures absolutely continuous with 
respect to $m_G$ and  subalgebra $M_s(G)$ of measures singular with 
respect to $m_G$. Note that $M_a(G)\isom{M(G)-\mathbf{mod}_1}L_1(G)$ 
and $M_s(G)$ is an annihilator $L_1(G)$-module. 
Finally, $M(G)=M_a(G)$ iff $G$ is discrete. 

Now we proceed to the discussion of standard left and right modules 
over $L_1(G)$ and $M(G)$. Since the Banach algebra $L_1(G)$ can be 
regarded as a closed two-sided ideal  of $M(G)$ because of isometric 
left and right $M(G)$-morphism $i:L_1(G)\to M(G):f\mapsto f m_G$. 
Therefore, it is enough to define all module structures over $M(G)$. 
For $1\leq p<+\infty$ and any $f\in L_p(G)$, $\mu\in M(G)$ we define
$$
(\mu\convol_p f)(s)=\int_G f(t^{-1}s)d\mu(t), \qquad\qquad (f\convol_p
\mu)(s)=\int_G f(st^{-1}){\Delta_G(t^{-1})}^{1/p}d\mu(t)
$$
These module actions turn any Banach space $L_p(G)$ for $1\leq p<+\infty$ into 
left and right $M(G)$-module. Note that for $p=1$ and $\mu\in M_a(G)$ we 
get the usual definition of convolution. For $1<p\leq +\infty$ and 
any $f\in L_p(G)$, $\mu\in M(G)$ we define module actions
$$
(\mu\cdot_p f)(s)=\int_G {\Delta_G(t)}^{1/p}f(st)d\mu(t), \qquad\qquad (f\cdot_p
\mu)(s)=\int_G f(ts)d\mu(t)
$$
These module actions turn any Banach space $L_p(G)$ for $1<p\leq+\infty$ into 
left and right $M(G)$-module too. This special choice of module structure 
nicely interacts with duality. Indeed, we have 
and ${(L_p(G),\convol_p)}^*\isom{\mathbf{mod}_1-M(G)}(L_{p^*}(G),\cdot_{p^*})$ 
for all $1\leq p<+\infty$. Finally, the Banach space $C_0(G)$ also becomes left 
and right $M(G)$-module when endowed with $\cdot_\infty$ in the role of module 
action. Even more, $C_0(G)$ is a closed left and right $M(G)$-submodule 
of $L_\infty(G)$ 
and ${(C_0(G),\cdot_\infty)}^*\isom{M(G)-\mathbf{mod}_1}(M(G),\convol)$.

A character on a locally compact group $G$ is by definition a continuous 
homomorphism from $G$ to $\mathbb{T}$. The set of all characters on $G$ forms a 
group denoted by $\widehat{G}$. It becomes a locally compact group when 
considered with compact open topology. Any character $\gamma\in\widehat{G}$ 
gives rise to a continuous character 
$\varkappa_\gamma^L:
L_1(G)\to\mathbb{C},\, 
f\mapsto \int_G f(s)\overline{\gamma(s)}dm_G(s)$ on $L_1(G)$. In fact all 
characters of $L_1(G)$ arise this way. This result is due to 
Gelfand [\cite{KaniBanAlg}, theorems 2.7.2, 2.7.5]. Similarly, for 
each $\gamma\in\widehat{G}$ we have a character on $M(G)$ defined by 
$\varkappa_\gamma^M:
M(G)\to\mathbb{C},\, 
\mu\mapsto\int_{G} \overline{\gamma(s)}d\mu(s)$. By $\mathbb{C}_\gamma$ we 
denote the respective augmentation left and right $L_1(G)$- or $M(G)$-module. 
Their module actions are defined by
$$
f\cdot_{\gamma}z=z\cdot_{\gamma}f=\varkappa_\gamma^L(f)z \qquad\qquad
\mu\cdot_{\gamma}z=z\cdot_{\gamma}\mu=\varkappa_\gamma^M(\mu)z
$$
for all $f\in L_1(G)$, $\mu\in M(G)$ and $z\in\mathbb{C}$. 

One of the numerous definitions of amenable group says, that a locally compact 
group $G$ is amenable if there exists an $L_1(G)$-morphism of right 
modules $M:L_\infty(G)\to\mathbb{C}_{e_{\widehat{G}}}$ such 
that $M(\chi_G)=1$ [\cite{HelBanLocConvAlg}, section VII.2.5]. We can even 
assume that $M$ is contractive [\cite{HelBanLocConvAlg}, remark 7.1.54].

Most results of this section that are not supported with references are 
presented in a full detail in [\cite{DalBanAlgAutCont}, section 3.3].

%-------------------------------------------------------------------------------
%	L_1(G)-modules
%-------------------------------------------------------------------------------

\subsection{
    \texorpdfstring{$L_1(G)$}{L1(G)}-modules}\label{
SubSectionL1GModules}

Metric homological properties of most of the standard $L_1(G)$-modules of 
harmonic analysis are studied in~\cite{GravInjProjBanMod}. We borrow these 
ideas to unify approaches to metric and topological homological properties 
of modules over group algebras.

\begin{proposition}\label{LInfIsL1MetrInj} Let $G$ be a locally compact group. 
Then $L_1(G)$ is metrically and topologically flat $L_1(G)$-module, 
i.e. the $L_1(G)$-module $L_\infty(G)$ is metrically and topologically injective.
\end{proposition} 
\begin{proof} Since $L_1(G)$ has a contractive approximate identity, 
then $L_1(G)$ is metrically and topologically flat $L_1(G)$-module 
by proposition~\ref{MetTopFlatIdealsInUnitalAlg}. 
Since $L_\infty(G)\isom{\mathbf{mod}_1-L_1(G)}{L_1(G)}^*$, then by 
proposition~\ref{MetCTopFlatCharac} this module is metrically and topologically injective.
\end{proof}

\begin{proposition}\label{OneDimL1ModMetTopProjCharac} Let $G$ be a locally 
compact group, and $\gamma\in\widehat{G}$. Then the following are equivalent:

\begin{enumerate}[label = (\roman*)]
    \item $G$ is compact;

    \item $\mathbb{C}_\gamma$ is a metrically projective $L_1(G)$-module;

    \item $\mathbb{C}_\gamma$ is a topologically projective $L_1(G)$-module.
\end{enumerate}
\end{proposition}
\begin{proof} $(i)\implies (ii)$ Consider $L_1(G)$-morphisms 
$\sigma^+:\mathbb{C}_\gamma\to {L_1(G)}_+,\, z\mapsto z\gamma \oplus_1 0$ 
and $\pi^+:{L_1(G)}_+\to\mathbb{C}_\gamma,\, f\oplus_1 w\to f\cdot_{\gamma}1+w$. 
One can easily check 
that $\Vert\pi^+\Vert=\Vert\sigma^+\Vert=1$ 
and $\pi^+\sigma^+=1_{\mathbb{C}_\gamma}$. Therefore, $\mathbb{C}_\gamma$ is a 
retract of ${L_1(G)}_+$ in $L_1(G)-\mathbf{mod}_1$. From 
propositions~\ref{UnitalAlgIsMetTopProj} 
and~\ref{RetrMetCTopProjIsMetCTopProj} it follows 
that $\mathbb{C}_\gamma$ is metrically projective.

$(ii)\implies (iii)$ See
proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj}.

$(iii)\implies (i)$ Consider $L_1(G)$-morphism
$\pi:L_1(G)\to\mathbb{C}_\gamma,\, f\mapsto f\cdot_{\gamma} 1$. It is easy to see
that $\pi$ is strictly coisometric. Since $\mathbb{C}_\gamma$ is topologically
projective, then there exists an $L_1(G)$-morphism $\sigma:\mathbb{C}_\gamma\to
L_1(G)$ such that $\pi\sigma=1_{\mathbb{C}_\gamma}$. Let $f=\sigma(1)\in L_1(G)$
and ${(e_\nu)}_{\nu\in N}$ be a standard approximate identity of $L_1(G)$. Since
$\sigma$ is an $L_1(G)$-morphism, then for all $s,t\in G$ we have 
$$
f(s^{-1}t)
=L_s(f)(t)
=\lim_\nu L_s(e_\nu\convol \sigma(1))(t)
=\lim_\nu((\delta_s\convol e_\nu)\convol \sigma(1))(t)
=\lim_\nu\sigma((\delta_s\convol e_\nu)\cdot_{\gamma} 1)(t)
$$
$$
=\lim_\nu\sigma(\varkappa_\gamma^L(\delta_s\convol e_\nu))(t)
=\lim_\nu\varkappa_\gamma^L(\delta_s\convol e_\nu)\sigma(1)(t)
=\lim_\nu(e_\nu\convol\gamma)(s^{-1})f(t)
=\gamma(s^{-1})f(t).
$$
Therefore, for the function $g(t):=\gamma(t^{-1})f(t)$ in $L_1(G)$ we have
$g(st)=g(t)$ for all $s,t\in G$. Thus, $g$ is a constant function in $L_1(G)$,
which is possible only when $G$ is compact.
\end{proof}

\begin{proposition}\label{OneDimL1ModMetTopInjFlatCharac} Let $G$ be a locally
compact group, and $\gamma\in\widehat{G}$. Then the following are equivalent:

\begin{enumerate}[label = (\roman*)]
    \item $G$ is amenable;

    \item $\mathbb{C}_\gamma$ is a metrically injective $L_1(G)$-module;

    \item $\mathbb{C}_\gamma$ is a topologically injective $L_1(G)$-module.

    \item $\mathbb{C}_\gamma$ is a metrically flat $L_1(G)$-module;

    \item $\mathbb{C}_\gamma$ is a topologically flat $L_1(G)$-module.
\end{enumerate}
\end{proposition}
\begin{proof} $(i)\implies (ii)$ Since $G$ is amenable, then we have a 
contractive $L_1(G)$-morphism $M:L_\infty(G)\to\mathbb{C}_{e_{\widehat{G}}}$
with $M(\chi_G)=1$. Consider linear 
operators $\rho:\mathbb{C}_\gamma\to L_\infty(G),\, z\mapsto z\overline{\gamma}$ 
and $\tau:L_\infty(G)\to\mathbb{C}_\gamma,\, f\mapsto M(f\gamma)$. These are
$L_1(G)$-morphisms of right $L_1(G)$-modules. We shall check this for operator
$\tau$: for all $f\in L_\infty(G)$ and $g\in L_1(G)$ we have
$$
\tau(f\cdot_\infty g)
=M((f\cdot_\infty g)\gamma)
=M(f\gamma\cdot_\infty g\overline{\gamma})
=M(f\gamma)\cdot_{e_{\widehat{G}}} g\overline{\gamma}
=M(f\gamma)\varkappa_\gamma^L(g)
=\tau(f)\cdot_{\gamma} g.
$$  
It is easy to check that $\rho$ and $\tau$ are contractive and
$\tau\rho=1_{\mathbb{C}_\gamma}$. Therefore, $\mathbb{C}_\gamma$ is a retract of
$L_\infty(G)$ in $\mathbf{mod}_1-L_1(G)$. From
propositions~\ref{LInfIsL1MetrInj} and~\ref{RetrMetCTopInjIsMetCTopInj} it 
follows that $\mathbb{C}_\gamma$ is metrically injective as $L_1(G)$-module.

$(ii)\implies (iii)$ See proposition~\ref{MetInjIsTopInjAndTopInjIsRelInj}.

$(iii) \implies (i)$ Since $\rho$ is an isometric $L_1(G)$-morphism of right
$L_1(G)$-modules and $\mathbb{C}_\gamma$ is topologically injective as
$L_1(G)$-module, then $\rho$ is a coretraction in $\mathbf{mod}-L_1(G)$. Denote
its left inverse morphism by $\pi$, then
$\pi(\overline{\gamma})=\pi(\rho(1))=1$. Consider a bounded linear functional
$M:L_\infty(G)\to\mathbb{C}_\gamma:f\mapsto \pi(f\overline{\gamma})$. For all
$f\in L_\infty(G)$ and $g\in L_1(G)$ we have
$$
M(f\cdot_\infty g)
=\pi((f\cdot_\infty g)\overline{\gamma})
=\pi(f\overline{\gamma}\cdot_\infty g\gamma)
=\pi(f\overline{\gamma})\cdot_{\gamma} g\gamma
=M(f)\varkappa_\gamma^L(g\gamma)
=M(f)\cdot_{e_{\widehat{G}}}g.
$$
Therefore, $M$ is an $L_1(G)$-morphism, but we also have
$M(\chi_G)=\pi(\overline{\gamma})=1$. Therefore, $G$ is amenable.

$(ii) \Longleftrightarrow (iv)$, $(iii) \Longleftrightarrow (v)$ Note that
$\mathbb{C}_\gamma^*\isom{\mathbf{mod}_1-L_1(G)}\mathbb{C}_\gamma$, so all
equivalences  follow from three previous paragraphs and
proposition~\ref{MetCTopFlatCharac}.
\end{proof}

In the next proposition we shall study specific ideals of the Banach algebra
$L_1(G)$. They have the form $L_1(G)\convol\mu$ for some idempotent measure
$\mu\in M(G)$. In fact, this class of ideals in case of commutative compact groups $G$
coincides with those closed left ideals of $L_1(G)$ that admit a right bounded
approximate identity.

\begin{proposition}\label{CommIdealByIdemMeasL1MetTopProjCharac} Let $G$ be a
locally compact group and  $\mu\in M(G)$ be an idempotent measure, that is
$\mu\convol\mu=\mu$. If the left ideal $I=L_1(G)\convol\mu$ of the Banach algebra
$L_1(G)$ is a topologically projective $L_1(G)$-module, then $\mu=p m_G$, for some
$p\in I$.
\end{proposition}
\begin{proof} Let $\phi:I\to L_1(G)$ be arbitrary morphism of left
$L_1(G)$-modules. Consider $L_1(G)$-morphism $\phi':L_1(G)\to
L_1(G):x\mapsto\phi(x\convol\mu)$. By Wendel's theorem [\cite{WendLeftCentrzrs},
theorem 1], there exists a measure $\nu\in M(G)$ such that
$\phi'(x)=x\convol\nu$ for all $x\in L_1(G)$. In particular,
$\phi(x)=\phi(x\convol\mu)=\phi'(x)=x\convol\nu$ for all $x\in I$. It is now
clear that $\psi:I\to I:x\mapsto\nu\convol x$ is a morphism of right $I$-modules
satisfying $\phi(x)y=x\psi(y)$ for all $x,y\in I$. By paragraph $(ii)$ of
lemma~\ref{GoodIdealMetTopProjIsUnital} the ideal $I$ has a right identity, say
$e\in I$. Then $x\convol\mu=x\convol\mu\convol e$ for all $x\in L_1(G)$. Two
measures are equal if their convolutions with all functions of $L_1(G)$ coincide
[\cite{DalBanAlgAutCont}, corollary 3.3.24], so $\mu=\mu\convol e m_G$. Since
$e\in I\subset L_1(G)$, then $\mu=\mu\convol e m_G\in M_a(G)$. 
Set $p=\mu\convol e\in I$, then $\mu=p m_G$.
\end{proof}

We conjecture that the left ideal $L_1(G)\convol \mu$ for an idempotent measure
$\mu\in M(G)$ is metrically projective $L_1(G)$-module iff $\mu=p m_G$ where $p\in I$
and $\Vert p\Vert=1$.

\begin{theorem}\label{L1ModL1MetTopProjCharac} Let $G$ be a locally compact
group. Then the following are equivalent:

\begin{enumerate}[label = (\roman*)]
    \item $G$ is discrete;

    \item $L_1(G)$ is a metrically projective $L_1(G)$-module;

    \item $L_1(G)$ is a topologically projective $L_1(G)$-module.
\end{enumerate}
\end{theorem}
\begin{proof} $(i)\implies (ii)$ If $G$ is discrete, then the algebra $L_1(G)$ 
is unital with unit of norm $1$. By  proposition~\ref{UnIdeallIsMetTopProj} 
we see that $L_1(G)$ is metrically projective as $L_1(G)$-module.

$(ii)\implies (iii)$ See
proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj}.

$(iii) \implies (i)$ Clearly, $\delta_{e_G}$ is an idempotent measure. Since
$L_1(G)=L_1(G)\convol \delta_{e_G}$ is topologically projective, then by
proposition~\ref{CommIdealByIdemMeasL1MetTopProjCharac} 
we have $\delta_{e_G}=f m_G$ for some $f\in L_1(G)$. This is possible only 
if $G$ is discrete.
\end{proof}

Note that $L_1(G)$-module $L_1(G)$ is relatively projective for any locally
compact group $G$ [\cite{HelBanLocConvAlg}, exercise 7.1.17].

\begin{proposition}\label{L1MetTopProjAndMetrFlatOfMeasAlg} Let $G$ be 
a locally compact group. Then the following are equivalent:

\begin{enumerate}[label = (\roman*)]
    \item $G$ is discrete;

    \item $M(G)$ is a metrically projective $L_1(G)$-module;

    \item $M(G)$ is a topologically projective $L_1(G)$-module;

    \item $M(G)$ is a metrically flat $L_1(G)$-module.
\end{enumerate}
\end{proposition}
\begin{proof} 
$(i)\implies (ii)$ We have $M(G)\isom{L_1(G)-\mathbf{mod}_1}L_1(G)$ for
discrete $G$, so the result follows from theorem~\ref{L1ModL1MetTopProjCharac}. 

$(ii)\implies (iii)$ See
proposition~\ref{MetProjIsTopProjAndTopProjIsRelProj}.

$(ii)\implies (iv)$ See proposition~\ref{MetTopProjIsMetTopFlat}.

$(iii)\implies (i)$ Note that $M(G)\isom{L_1(G)-\mathbf{mod}_1}
L_1(G)\bigoplus_1 M_s(G)$, so $M_s(G)$ is topologically projective by
proposition~\ref{MetTopProjModCoprod}. Note that $M_s(G)$ is an annihilator
$L_1(G)$-module, then by proposition~\ref{MetTopProjOfAnnihModCharac} the
algebra $L_1(G)$ has a right identity. Recall that $L_1(G)$ also has a two-sided
bounded approximate identity, so $L_1(G)$ is unital. The last is equivalent to
$G$ being discrete.

$(iv)\implies (i)$ Note that $M(G)\isom{L_1(G)-\mathbf{mod}_1}
L_1(G)\bigoplus_1 M_s(G)$, so $M_s(G)$ is metrically flat by
proposition~\ref{MetTopFlatModCoProd}. Note that $M_s(G)$ is an annihilator
$L_1(G)$-module, then by proposition~\ref{MetTopFlatAnnihModCharac} it is equal
to zero. The last is equivalent to $G$ being discrete.
\end{proof}

\begin{proposition}\label{MeasAlgIsL1TopFlat} Let $G$ be a locally compact
group. Then $M(G)$ is a topologically flat $L_1(G)$-module.
\end{proposition}
\begin{proof} Since $M(G)$ is an $L_1$-space it is a fortiori an
$\mathscr{L}_1^g$-space. Since $M_s(G)$ is complemented in $M(G)$, then $M_s(G)$
is an $\mathscr{L}_1^g$-space too [\cite{DefFloTensNorOpId}, corollary
23.2.1(2)]. As $M_s(G)$ is an annihilator $L_1(G)$-module, then from
proposition~\ref{MetTopFlatAnnihModCharac} we have that $M_s(G)$ is
topologically flat $L_1(G)$-module. The $L_1(G)$-module $L_1(G)$ is also
topologically flat by proposition~\ref{LInfIsL1MetrInj}. Since
$M(G)\isom{L_1(G)-\mathbf{mod}_1}L_1(G)\bigoplus_1 M_s(G)$, then $M(G)$ is
topologically flat $L_1(G)$-module by proposition~\ref{MetTopFlatModCoProd}.
\end{proof}

%-------------------------------------------------------------------------------
%	M(G)-modules
%-------------------------------------------------------------------------------

\subsection{
    \texorpdfstring{$M(G)$}{M(G)}-modules}\label{
SubSectionMGModules}

We turn to the study of standard $M(G)$-modules of harmonic analysis. As we
shall see most of the results can be derived from results on $L_1(G)$-modules.

\begin{proposition}\label{MGMetTopProjInjFlatRedToL1} Let $G$ be a locally
compact group, and $X$ be $\langle$~essential / faithful / essential~$\rangle$
$L_1(G)$-module. Then

\begin{enumerate}[label = (\roman*)]
    \item $X$ is a metrically $\langle$~projective / injective / flat~$\rangle$
    $M(G)$-module iff it is a metrically $\langle$~projective / injective /
    flat~$\rangle$ $L_1(G)$-module;

    \item $X$ is a topologically $\langle$~projective / injective / flat~$\rangle$
    $M(G)$-module iff it is a topologically $\langle$~projective / injective /
    flat~$\rangle$ $L_1(G)$-module.
\end{enumerate}
\end{proposition}
\begin{proof} Recall that $L_1(G)\isom{L_1(G)-\mathbf{mod}_1}M_a(G)$ is a
closed two-sided contractively complemented ideal of $M(G)$. Now $(i)$ and $(ii)$
follow from proposition $\langle$~\ref{MetTopProjUnderChangeOfAlg}
/~\ref{MetTopInjUnderChangeOfAlg}  /~\ref{MetTopFlatUnderChangeOfAlg}~$\rangle$.
\end{proof} 

It is worth mentioning here that the $L_1(G)$-modules $C_0(G)$, $L_p(G)$ for
$1\leq p<\infty$ and $\mathbb{C}_\gamma$ for $\gamma\in\widehat{G}$ are
essential and $L_1(G)$-modules $C_0(G)$, $M(G)$, $L_p(G)$ for $1\leq p\leq
\infty$ and $\mathbb{C}_\gamma$ for $\gamma\in\widehat{G}$ are faithful. 

\begin{proposition}\label{MGModMGMetTopProjFlatCharac} Let $G$ be a locally
compact group. Then $M(G)$ is metrically and topologically projective
$M(G)$-module. As a consequence it is metrically and topologically flat
$M(G)$-module.
\end{proposition} 
\begin{proof} Since $M(G)$ is a unital algebra, then metric and topological
projectivity of $M(G)$ follow from proposition~\ref{UnitalAlgIsMetTopProj}. It
remains to apply proposition~\ref{MetTopProjIsMetTopFlat}.
\end{proof}

%-------------------------------------------------------------------------------
%	Banach geometric constraints
%-------------------------------------------------------------------------------

\subsection{
    Banach geometric constraints}\label{
SubSectionBanachGeometricConstraints}

In this section we shall show that many modules of harmonic analysis are fail to
be metrically or topologically projective, injective or flat for purely Banach
geometric reasons. 

\begin{proposition}\label{StdModAreNotRetrOfL1LInf} Let $G$ be an infinite
locally compact group. Then

\begin{enumerate}[label = (\roman*)]
    \item $L_1(G)$, $C_0(G)$, $M(G)$, ${L_\infty(G)}^*$ are not 
    topologically injective Banach spaces;

    \item $C_0(G)$, $L_\infty(G)$ are not complemented in any $L_1$-space.
\end{enumerate}
\end{proposition}
\begin{proof}
Since $G$ is infinite all modules in question are infinite dimensional.

$(i)$ If an infinite dimensional Banach space is topologically injective, then it
contains a copy of $\ell_\infty(\mathbb{N})$ [\cite{RosOnRelDisjFamOfMeas},
corollary 1.1.4], and consequently a copy of $c_0(\mathbb{N})$. The Banach space
$L_1(G)$ is weakly sequentially complete [\cite{WojBanSpForAnalysts}, corollary
III.C.14], so by corollary 5.2.11 in~\cite{KalAlbTopicsBanSpTh} it cannot contain
a copy of $c_0(\mathbb{N})$. Therefore, $L_1(G)$ is not a topologically injective
Banach space.  If $M(G)$ is a topologically injective Banach space, then so is
its complemented subspace $M_a(G)\isom{\mathbf{Ban}_1}L_1(G)$. By previous
argument this is impossible. So $M(G)$ is not topologically injective as Banach
space. By corollary 3 of~\cite{LauMingComplSubspInLInfOfG} the space $C_0(G)$ is
not complemented in $L_\infty(G)$. Then $C_0(G)$ cannot be topologically
injective either. The Banach space $L_1(G)$ is complemented in
${L_\infty(G)}^*\isom{\mathbf{Ban}_1}{L_1(G)}^{**}$ [\cite{DefFloTensNorOpId},
proposition  B10]. Therefore, if ${L_\infty(G)}^*$ is topologically injective as
Banach space, then so is its retract $L_1(G)$. By previous arguments this is
impossible, so ${L_\infty(G)}^*$ is not topologically injective Banach space.

$(ii)$ If $C_0(G)$ is a retract of $L_1$-space, then
$M(G)\isom{\mathbf{Ban}_1}{C_0(G)}^*$ is a retract of $L_\infty$-space, 
so it must be a topologically injective Banach space. This contradicts 
paragraph $(i)$, so $C_0(G)$ is not a retract of $L_1$-space. 
Note that $\ell_\infty(\mathbb{N})$ embeds in $L_\infty(G)$, hence so 
is $c_0(\mathbb{N})$. Therefore, if $L_\infty(G)$ is
a retract of $L_1$-space, then there would exist an $L_1$-space containing a
copy of $c_0(\mathbb{N})$. This is impossible as already showed in paragraph
$(i)$.
\end{proof}

From now on by $A$ we denote either $L_1(G)$ or $M(G)$. Recall that $L_1(G)$ and
$M(G)$ are both $L_1$-spaces.

\begin{proposition}\label{StdModAreNotL1MGMetTopProjInjFlat} Let $G$ be an
infinite locally compact group. Then

\begin{enumerate}[label = (\roman*)]
    \item $C_0(G)$, $L_\infty(G)$ are neither topologically nor metrically 
    projective $A$-modules;

    \item $L_1(G)$, $C_0(G)$, $M(G)$, ${L_\infty(G)}^*$ are neither 
    topologically nor metrically injective $A$-modules;

    \item $L_\infty(G)$, $C_0(G)$ are neither topologically nor metrically flat
    $A$-modules.
\end{enumerate}
\end{proposition}

$(iv)$ $L_p(G)$ for $1<p<\infty$ are neither topologically nor metrically
projective, injective or flat $A$-flat.

\begin{proof} $(i)$ The result follows from
propositions~\ref{TopProjInjFlatModOverL1Charac} paragraph $(i)$ and
~\ref{StdModAreNotRetrOfL1LInf} paragraph $(ii)$.

$(ii)$ The result follows from propositions~\ref{TopProjInjFlatModOverL1Charac}
paragraph $(ii)$ and~\ref{StdModAreNotRetrOfL1LInf}.

$(iii)$ Note that ${C_0(G)}^*\isom{\mathbf{mod}_1-A}M(G)$. Now the result 
follows from paragraph $(i)$ and proposition~\ref{MetCTopFlatCharac}.

$(iv)$ Since $L_p(G)$ is reflexive for $1<p<\infty$ the result follows
from proposition~\ref{NoInfDimRefMetTopProjInjFlatModOverMthscrL1OrLInfty}.
\end{proof}

It remains to consider metric and topological homological properties of
$A$-modules when $G$ is finite.

\begin{proposition}\label{LpFinGrL1MGMetrInjProjCharac} Let $G$ be a non-trivial
finite group and $1\leq p\leq \infty$. Then the $A$-module $L_p(G)$ is
metrically $\langle$~projective / injective~$\rangle$ iff $\langle$~$p=1$ /
$p=\infty$~$\rangle$
\end{proposition}
\begin{proof} 
Assume $L_p(G)$ is metrically $\langle$~projective / injective~$\rangle$ as
$A$-module. Since $L_p(G)$ is finite dimensional, then by paragraphs $(i)$ and
$(ii)$ of proposition~\ref{TopProjInjFlatModOverL1Charac} we have 
identifications $\langle$~$L_p(G)\isom{\mathbf{Ban}_1}\ell_1(\mathbb{N}_n)$ /
$L_p(G)
\isom{\mathbf{Ban}_1}
C(\mathbb{N}_n)
\isom{\mathbf{Ban}_1}
\ell_\infty(\mathbb{N}_n)$~$\rangle$, 
where $n=\operatorname{Card}(G)>1$. Now we use the result of theorem
1 from~\cite{LyubIsomEmdbFinDimLp} for Banach spaces over field $\mathbb{C}$: if
for $2\leq m\leq k$ and $1\leq r,s\leq \infty$, there exists an isometric
embedding from $\ell_r(\mathbb{N}_m)$ into $\ell_s(\mathbb{N}_k)$, then either
$r=2$, $s\in 2\mathbb{N}$ or $r=s$. Therefore, $\langle$~$p=1$ /
$p=\infty$~$\rangle$. The converse easily follows from
$\langle$~theorem~\ref{L1ModL1MetTopProjCharac} /
proposition~\ref{LInfIsL1MetrInj}~$\rangle$
\end{proof}

\begin{proposition}\label{StdModFinGrL1MGMetrInjProjFlatCharac} Let $G$ be a
finite group. Then

\begin{enumerate}[label = (\roman*)]
    \item $C_0(G)$, $L_\infty(G)$ are metrically injective $A$-modules;

    \item $C_0(G)$, $L_p(G)$ for $1<p\leq\infty$ are metrically projective
    $A$-modules iff $G$ is trivial;

    \item $M(G)$, $L_p(G)$ for $1\leq p<\infty$ are metrically injective
    $A$-modules iff $G$ is trivial;

    \item $C_0(G)$, $L_p(G)$ for $1<p\leq\infty$ are metrically 
    flat $A$-modules iff $G$ is trivial.
\end{enumerate}
\end{proposition}
\begin{proof}
$(i)$ Since $G$ is finite then $C_0(G)=L_\infty(G)$. The result follows from
proposition~\ref{LInfIsL1MetrInj}.

$(ii)$ If $G$ is trivial, that is $G= \{e_G \}$, then $L_p(G)=C_0(G)=L_1(G)$ and
the result follows from paragraph $(i)$. If $G$ is non-trivial, then we recall
that $C_0(G)=L_\infty(G)$ and use
proposition~\ref{LpFinGrL1MGMetrInjProjCharac}.

$(iii)$ If $G$ is trivial, then $M(G)=L_p(G)=L_\infty(G)$ and the result follows
from paragraph $(i)$. If $G$ is non-trivial, then we note that $M(G)=L_1(G)$ and
use proposition~\ref{LpFinGrL1MGMetrInjProjCharac}.

$(iv)$ From paragraph $(iii)$ it follows that $L_p(G)$ for $1\leq p<\infty$ is a 
metrically injective $A$-module iff $G$ is trivial. Now the result follows from
proposition~\ref{MetCTopFlatCharac} and the facts that
${C_0(G)}^*\isom{\mathbf{mod}_1-L_1(G)}M(G)\isom{\mathbf{mod}_1-L_1(G)}L_1(G)$,
${L_p(G)}^*\isom{\mathbf{mod}_1-L_1(G)}L_{p^*}(G)$ for $1\leq p^*<\infty$.
\end{proof}

It is worth mentioning here that if we would consider all Banach spaces over the
field of real numbers, then the $L_1(G)$-modules $L_\infty(G)$ and $L_1(G)$ 
would be metrically projective and injective respectively, 
additionally for $G$ consisting of two elements, because
$$
L_\infty(\mathbb{Z}_2)
\isom{L_1(\mathbb{Z}_2)-\mathbf{mod}_1}
\mathbb{R}_{\gamma_0}\bigoplus\nolimits_1\mathbb{R}_{\gamma_1},
\qquad
L_1(\mathbb{Z}_2)
\isom{L_1(\mathbb{Z}_2)-\mathbf{mod}_1}
\mathbb{R}_{\gamma_0}\bigoplus\nolimits_\infty\mathbb{R}_{\gamma_1}
$$
for $\gamma_0,\gamma_1\in\widehat{\mathbb{Z}_2}$ defined by
$\gamma_0(0)=\gamma_0(1)=\gamma_1(0)=-\gamma_1(1)=1$. Here $\mathbb{Z}_2$
denotes the unique group of two elements.

\begin{proposition}\label{StdModFinGrL1MGTopInjProjFlatCharac} Let $G$ be a
finite group. Then the $A$-modules $C_0(G)$, $M(G)$, $L_p(G)$ 
for $1\leq p\leq \infty$ are both topologically projective, injective and flat.
\end{proposition} 
\begin{proof}
Since the group $G$ is finite, we have $M(G)=L_1(G)$ and $C_0(G)=L_\infty(G)$, 
so these modules do not require special considerations. As $M(G)=L_1(G)$, 
we can restrict our considerations to the case $A=L_1(G)$. The identity map
$i:L_1(G)\to L_p(G):f\mapsto f$ is a topological isomorphism of Banach spaces,
because $L_1(G)$ and $L_p(G)$ for $1\leq p<+\infty$ are of equal finite
dimension. Since $G$ is finite, it is unimodular. Therefore, the module actions
in $(L_1(G),\convol)$ and $(L_p(G),\convol_p)$ coincide for $1\leq p<+\infty$.
Therefore, $i$ is an isomorphism in $L_1(G)-\mathbf{mod}$ and $\mathbf{mod}-L_1(G)$.
Similarly, one can show that $(L_\infty(G),\cdot_\infty)$ and $(L_p(G),\cdot_p)$
for $1<p\leq+\infty$ are isomorphic in $L_1(G)-\mathbf{mod}$ and
$\mathbf{mod}-L_1(G)$. Finally, one can easily check that $(L_1(G),\convol)$ and
$(L_\infty(G),\cdot_\infty)$ are isomorphic in $L_1(G)-\mathbf{mod}$ and
$\mathbf{mod}-L_1(G)$ via the 
map $j:L_1(G)\to L_\infty(G):f\mapsto(s\mapsto f(s^{-1}))$. Therefore, all 
modules discussed above are pairwise isomorphic. It remains to
recall that $L_1(G)$ is topologically projective and flat by
theorem~\ref{L1ModL1MetTopProjCharac} and proposition~\ref{LInfIsL1MetrInj},
while $L_\infty(G)$ is topologically injective by
proposition~\ref{LInfIsL1MetrInj}.
\end{proof}

Now we can summarize results on homological properties of modules of harmonic
analysis into three tables. Each cell of the table contains a condition under
which the respective module has the respective property and propositions where this
result is proved. We shall mention that results for modules $L_p(G)$ are valid for both
module actions $\convol_p$ and $\cdot_p$. Characterization and proofs for
homologically trivial modules $\mathbb{C}_\gamma$ in case of relative theory is
the same as in
propositions~\ref{OneDimL1ModMetTopProjCharac},
~\ref{OneDimL1ModMetTopInjFlatCharac}
and~\ref{OneDimL1ModMetTopInjFlatCharac}. As usually, we use ${}^{*}$ to
indicate that only a necessary conditions is known. As we showed above even
topological theory is too restrictive for $L_1(G)$ to be projective as
$L_1(G)$-module. Similarly, a Banach space is topologically projective iff it is
an $L_1$-space, and the underlying measure space is atomic. This analogy
confirms important role of Banach geometry in metric and topological Banach
homology.

\begin{scriptsize}
    \begin{longtable}{|c|c|c|c|c|c|c|} 
    \multicolumn{7}{c}{
        \mbox{
            Homologically trivial $L_1(G)$- and $M(G)$-modules in metric theory
        }
    }                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                             \\
    \hline & 
        \multicolumn{3}{c|}{
            $L_1(G)$-modules
        } & 
        \multicolumn{3}{c|}{
            $M(G)$-modules
        } \\
    \hline & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} & 
        \mbox{Projectivity} &
        \mbox{Injectivity} & 
        \mbox{Flatness} \\ 
    \hline
        $L_1(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is discrete } \\
            \mbox{\ref{L1ModL1MetTopProjCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{LInfIsL1MetrInj}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is discrete } \\
            \mbox{\ref{L1ModL1MetTopProjCharac}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{LInfIsL1MetrInj}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} \\
    \hline 
        $L_p(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{LpFinGrL1MGMetrInjProjCharac}}
        \end{tabular} &
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{LpFinGrL1MGMetrInjProjCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{LpFinGrL1MGMetrInjProjCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{LpFinGrL1MGMetrInjProjCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} \\
    \hline
        $L_\infty(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{LpFinGrL1MGMetrInjProjCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{LInfIsL1MetrInj}}
        \end{tabular} &
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{LpFinGrL1MGMetrInjProjCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{LInfIsL1MetrInj}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} \\ 
    \hline
        $M(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is discrete } \\
            \mbox{\ref{L1MetTopProjAndMetrFlatOfMeasAlg}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is discrete } \\
            \mbox{\ref{MeasAlgIsL1TopFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{MGModMGMetTopProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{MGModMGMetTopProjFlatCharac}}
        \end{tabular} \\ 
    \hline
        $C_0(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G= \{e_G \}$ \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGMetrInjProjFlatCharac}}
        \end{tabular} \\ 
    \hline 
        $\mathbb{C}_\gamma$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is compact } \\
            \mbox{\ref{OneDimL1ModMetTopProjCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is compact } \\
            \mbox{\ref{OneDimL1ModMetTopProjCharac}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} \\ 
    \hline
        \multicolumn{7}{c}{
            \mbox{
                Homologically trivial $L_1(G)$- and $M(G)$-modules 
                in topological theory
            }
        } \\
    \hline & 
        \multicolumn{3}{c|}{
            $L_1(G)$-modules
        } & 
        \multicolumn{3}{c|}{
            $M(G)$-modules
        } \\
    \hline & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} \\ 
    \hline
        $L_1(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is discrete } \\
            \mbox{\ref{L1ModL1MetTopProjCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{LInfIsL1MetrInj}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is discrete } \\
            \mbox{\ref{L1ModL1MetTopProjCharac}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{LInfIsL1MetrInj}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} \\ 
    \hline
        $L_p(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} \\ 
    \hline
        $L_\infty(G)$ &
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{LInfIsL1MetrInj}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{LInfIsL1MetrInj}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} \\ 
    \hline
        $M(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is discrete } \\
            \mbox{\ref{L1MetTopProjAndMetrFlatOfMeasAlg}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{MeasAlgIsL1TopFlat}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{MGModMGMetTopProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\ref{MGModMGMetTopProjFlatCharac}}
        \end{tabular} \\ 
    \hline
        $C_0(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\ref{StdModAreNotL1MGMetTopProjInjFlat}},
            \mbox{\ref{StdModFinGrL1MGTopInjProjFlatCharac}}
        \end{tabular} \\ 
    \hline
        $\mathbb{C}_\gamma$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is compact } \\
            \mbox{\ref{OneDimL1ModMetTopProjCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}$G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is compact } \\
            \mbox{\ref{OneDimL1ModMetTopProjCharac}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} \\ 
    \hline
        \multicolumn{7}{c}{
            \mbox{
                Homologically trivial $L_1(G)$- and $M(G)$-modules 
                in relative theory
            }
        } \\
    \hline & 
    \multicolumn{3}{c|}{
        $L_1(G)$-modules
    } & 
    \multicolumn{3}{c|}{
        $M(G)$-modules
    } \\
    \hline & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} & 
        \mbox{Projectivity} & 
        \mbox{Injectivity} & 
        \mbox{Flatness} \\ 
    \hline 
        $L_1(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{ and discrete } \\
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} &
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} &
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{ and discrete } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} &
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} \\ 
    \hline
        $L_p(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is compact } \\
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\cite{RachInjModAndAmenGr}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\cite{RachInjModAndAmenGr}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is compact } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5},
            \mbox{\cite{RachInjModAndAmenGr}}
        \end{tabular} &
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} \\
    \hline
        $L_\infty(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\ 
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}${}^{*}$
        \end{tabular} \\ 
    \hline
        $M(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is discrete } \\
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable }\\
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\ 
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is any } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} \\ 
    \hline 
        $C_0(G)$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is compact } \\ 
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\ 
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\ 
            \mbox{\cite{DalPolHomolPropGrAlg}, \S 6}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is compact } \\ 
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is finite } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\cite{RamsHomPropSemgroupAlg}, \S 3.5}
        \end{tabular} \\ 
    \hline
        $\mathbb{C}_\gamma$ & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is compact } \\
            \mbox{\ref{OneDimL1ModMetTopProjCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is compact } \\
            \mbox{\ref{OneDimL1ModMetTopProjCharac}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} & 
        \begin{tabular}{@{}c@{}}
            $G$\mbox{ is amenable } \\
            \mbox{\ref{OneDimL1ModMetTopInjFlatCharac}},
            \mbox{\ref{MGMetTopProjInjFlatRedToL1}}
        \end{tabular} \\
    \hline
    \end{longtable}
\end{scriptsize}
