% Chapter Template

\chapter{General theory} % Main chapter title

\label{ChapterGeneralTheory} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Chapter 2. \emph{General theory}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------
%	Projectivity, injectivity and flatness
%----------------------------------------------------------------------------------------

\section{Projectivity, injectivity and flatness}
\label{SectionProjectivityInjectivityAndFlatness}


%----------------------------------------------------------------------------------------
%	Metric and topological projectivity
%----------------------------------------------------------------------------------------

\subsection{Metric and topological projectivity}
\label{SubSectionMetricAndTopologicalProjectivity}

In what follows $A$ denotes a not necessary unital Banach algebra. We immediately start from the most important definitions in this thesis.

\begin{definition}[\cite{HelMetrFrQMod}, definition 1.4]\label{MetProjMod} An $A$-module $P$ is called metrically projective if for any strictly coisometric $A$-morphism $\xi:X\to Y$ and for any $A$-morphism $\phi:P\to Y$ there exists an $A$-morphism $\psi:P\to X$ such that $\xi\psi=\phi$  and $\Vert\psi\Vert=\Vert\phi\Vert$.
\end{definition}

\begin{definition}[\cite{HelMetrFrQMod}, definition 1.2]\label{TopProjMod} An $A$-module $P$ is called  topologically projective if for any topologically surjective $A$-morphism $\xi:X\to Y$ and for any $A$-morphism $\phi:P\to Y$ there exists an $A$-morphism $\psi:P\to X$ such that $\xi\psi=\phi$.
\end{definition}

A short but more involved definition is the following: an $A$-module $P$ is called $\langle$~metrically / topologically~$\rangle$ projective, if the functor $\langle$~$\operatorname{Hom}_{A-\mathbf{mod}_1}(P,-):A-\mathbf{mod}_1\to\mathbf{Ban}_1$ / $\operatorname{Hom}_{A-\mathbf{mod}}(P,-):A-\mathbf{mod}\to\mathbf{Ban}$~$\rangle$ maps $\langle$~strictly coisometric / topologically surjective~$\rangle$ $A$-morphisms into $\langle$~strictly coisometric / surjective~$\rangle$ operators.

Now we are aiming to apply the general scheme of rigged categories to metric and topological projectivity. Before doing that we need to introduce the category of hemi normed spaces defined by Shteiner in \cite{ShtTopFrClassicQuantMod}. A hemi linear space over $\mathbb{C}$ is a set $E$, whose elements are called vectors, with a binary operation $\cdot:\mathbb{C}\times E\to E$ satisfying three axioms:

$i)$ $\alpha\cdot(\beta\cdot x)=\alpha\beta\cdot x$ for all $\alpha,\beta\in\mathbb{C}$ and $x\in E$; 

$ii)$ $1\cdot x=x$ for all $x\in E$; 

$iii)$ there exists a zero vector $0\in E$ such that $0\cdot x=0$ for all $x\in E$. 

A map $T:E\to F$ between hemi linear spaces is called a hemi linear operator if $T(\alpha\cdot x)=\alpha\cdot T(x)$ for all $\alpha\in\mathbb{C}$ and $x\in E$. A hemi normed space $E$ is a hemi linear space endowed with a function (called a norm) $\Vert\cdot\Vert:E\to\mathbb{R}_+$ such that

$i)$ $\Vert x\Vert=0$ iff $x=0$;

$ii)$ $\Vert\alpha\cdot x\Vert=|\alpha|\Vert x\Vert$ for all $\alpha\in\mathbb{C}$ and $x\in E$. 

A hemi linear operator $T:E\to F$ between hemi normed spaces $E$ and $F$ is called bounded if there exists $c\geq 0$ such that $\Vert\phi(x)\Vert\leq c\Vert x\Vert$ for all $x\in E$. The least such constant is called the norm of $\phi$ and denoted by $\Vert \phi\Vert$. Finally, we define the category of hemi normed spaces $\mathbf{HNor}$: its objects are hemi normed spaces, its morphisms are bounded hemi linear operators. In fact hemi normed spaces and bounded hemi linear operators are just leftovers of normed spaces and bounded linear operators if one erases  all axioms mentioning addition operation. Here is a typical example of hemi normed space. For a given non empty set $\Lambda$ we consider a bouquet $\mathbb{C}^\Lambda:=\bigvee \{\mathbb{C}:\lambda\in\Lambda\}$ of copies of $\mathbb{C}$ with common zero vector. Multiplication by scalars and norm in $\mathbb{C}^\Lambda$ are defined in a most natural fashion. We put by definition $\mathbb{C}^\varnothing=\{0\}$. Any hemi normed space is isomorphic in $\mathbf{HNor}$ to $\mathbb{C}^\Lambda$ for some set $\Lambda$ [\cite{ShtTopFrClassicQuantMod}, proposition 1.1.9].

In \cite{HelMetrFrQMod} and \cite{ShtTopFrClassicQuantMod} there were constructed two faithful functors 
$$
\square_{met}:A-\mathbf{mod}_1\to\mathbf{Set}:X\mapsto B_X,\phi\mapsto\phi|_{B_X}^{B_Y}
$$
$$
\square_{top}:A-\mathbf{mod}\to\mathbf{HNor}:X\mapsto X,\phi\mapsto\phi
$$
The first one sends a Banach $A$-module to its unit ball and any contractive $A$-morphism to the respective birestriction, while the second one ``forgets'' about module and additive structure.
In the same papers it was proved that an $A$-morphism $\xi$ is $\langle$~strictly coisometric / topologically surjective~$\rangle$ iff it is $\langle$~$\square_{met}$-admissible / $\square_{top}$-admissible~$\rangle$ epimorphism and an $A$-module $P$ is $\langle$~metrically / topologically~$\rangle$ projective iff it is $\langle$~$\square_{met}$-projective / $\square_{top}$-projective~$\rangle$. Thus we immediately get the following proposition.

\begin{proposition}\label{RetrMetTopProjIsMetTopProj} Any retract of $\langle$~metrically / topologically~$\rangle$ projective module in $\langle$~$A-\mathbf{mod}_1$ / $A-\mathbf{mod}$~$\rangle$ is again $\langle$~metrically / topologically~$\rangle$ projective.
\end{proposition}

It was also shown that the rigged category $\langle$~$(A-\mathbf{mod}_1,\square_{met})$ / $(A-\mathbf{mod},\square_{top})$~$\rangle$ is freedom loving and that $\langle$~$\square_{met}$-free / $\square_{top}$-free~$\rangle$ modules are isomorphic in $\langle$~$A-\mathbf{mod}_1$ / $A-\mathbf{mod}$~$\rangle$ to $A_+\projtens \ell_1(\Lambda)$ for some set $\Lambda$. Even more, for any $A$-module $X$ there exists a $\langle$~$\square_{met}$-admissible / $\square_{top}$-admissible~$\rangle$ epimorphism
$$
\pi_X^+:A_+\projtens \ell_1(B_X):a\projtens \delta_x\mapsto a\cdot x
$$
As the consequence of general result on rigged categories we get

\begin{proposition}\label{MetTopProjModViaCanonicMorph}
An $A$-module $P$ is $\langle$~metrically / topologically~$\rangle$ projective iff $\pi_P^+$ is a retraction in $\langle$~$A-\mathbf{mod}_1$ / $A-\mathbf{mod}$~$\rangle$.
\end{proposition}

Since $\langle$~$\square_{met}$-free / $\square_{top}$-free~$\rangle$ modules are the same up to isomorphisms in $A-\mathbf{mod}$ and any retraction in $A-\mathbf{mod}_1$ is a retraction in $A-\mathbf{mod}$, then from proposition \ref{RetrMetTopProjIsMetTopProj} we see that any metrically projective $A$-module is topologically projective. Recall that every relatively projective module is a retract in $A-\mathbf{mod}$ of $A_+\projtens E$ for some Banach space $E$, therefore every topologically projective $A$-module is relatively projective. We summarize all these in the following proposition.

\begin{proposition}\label{MetProjIsTopProjAndTopProjIsRelProj} Every metrically projective module is topologically projective and every topologically projective module is relatively projective.
\end{proposition}

A quantitative version of the definition of topological projectivity was given by White, though he used a somewhat different terminology.

\begin{definition}[\cite{WhiteInjmoduAlg}, definition 2.4]\label{CTopProjMod} An $A$-module $P$ is called  $C$-topologically projective if for any strictly $c$-topologically surjective $A$-morphism $\xi:X\to Y$ and for any $A$-morphism $\phi:P\to Y$ there exists an $A$-morphism $\psi:P\to X$ such that $\xi\psi=\phi$ and $\Vert \psi\Vert\leq c C\Vert\phi\Vert$.
\end{definition}

We shall need the following facts about this type of projectivity.

\begin{proposition}[\cite{WhiteInjmoduAlg}, lemma 2.7]\label{RetrCTopProjIsCTopProj} Any $c$-retract of $C$-topologically projective module is $cC$-topologically projective.
\end{proposition}

\begin{proposition}[\cite{WhiteInjmoduAlg}, proposition 2.10]\label{CTopProjModViaCanonicMorph} An $A$-module $P$ is $C$-topologically projective iff $\pi_P^+$ is a $C$-retraction in $A-\mathbf{mod}$.
\end{proposition}

As the consequence, a Banach module is topologically projective iff it is $C$-topologically projective for some $C$. One more important consequence of proposition \ref{CTopProjModViaCanonicMorph} is the following.

\begin{proposition}\label{MetProjIsOneTopProj} An $A$-module is metrically projective iff it is $1$-topologically projective.
\end{proposition}

We shall exploit both definitions \ref{TopProjMod} and \ref{CTopProjMod} without further reference for their equivalence. 

Let us proceed to examples. Note that the category of Banach spaces may be regarded as the category of left Banach modules over zero algebra. As the results we get the definition of $\langle$~metrically / topologically~$\rangle$ projective Banach space. All the results mentioned above hold for this type of projectivity. Both types of projective objects are described by now. In \cite{KotheTopProjBanSp} K{\"o}the proved that all topologically projective Banach spaces are topologically isomorphic to $\ell_1(\Lambda)$ for some index set $\Lambda$. Using result of Grothendieck from \cite{GrothMetrProjFlatBanSp} Helemskii showed that metrically projective Banach spaces are isometrically isomorphic to $\ell_1(\Lambda)$ for some index set $\Lambda$ [\cite{HelMetrFrQMod}, proposition 3.2]. Thus the zoo of projective Banach spaces is wide but conformed.

\begin{proposition}\label{UnitalAlgIsMetTopProj} The left $A$-module $A_\times$ is metrically and $1$-topologically projective.
\end{proposition} 
\begin{proof} Consider arbitrary $A$-morphism $\phi:A_\times\to Y$ and a strictly coisometric $A$-morphism $\xi:X\to Y$. From the definition of strictly coisometric operator it follows that there exists an $x_0\in X$ such that $\xi(x_0)=\phi(e_{A_\times})$ and $\Vert x_0\Vert=\Vert\phi(e_{A_\times})\Vert$. Consider $A$-morphism $\psi:A_\times\to X:a\mapsto a\cdot x_0$. Clearly, $\Vert\psi\Vert\leq\Vert x_0\Vert\leq\Vert\phi\Vert\Vert e_{A_\times}\Vert=\Vert\phi\Vert$. On the other hand $\xi\psi=\phi$, so $\Vert\phi\Vert\leq\Vert\xi\Vert\Vert\psi\Vert=\Vert\psi\Vert$. Thus $\Vert\phi\Vert=\Vert\psi\Vert$. Therefore we proved by definition, that $A_\times$ is metrically projective $A$-module. By proposition \ref{MetProjIsOneTopProj} it is $1$-topologically projective $A$-module.
\end{proof}

\begin{proposition}\label{NonDegenMetTopProjCharac}  Let $P$ be an essential $A$-module. Then $P$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective iff the map $\pi_P:A\projtens\ell_1(B_P):a\projtens\delta_x\mapsto a\cdot x$ is a $\langle$~$1$-retraction / $C$-retraction~$\rangle$ in $A-\mathbf{mod}$.
\end{proposition} 
\begin{proof}
If $P$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective, then by proposition $\langle$~\ref{MetTopProjModViaCanonicMorph} / \ref{CTopProjModViaCanonicMorph}~$\rangle$ the morphism $\pi_P^+$ has a right inverse morphism $\sigma^+$ of norm $\langle$~at most $1$ / at most $C$~$\rangle$. Then 
$$
	\sigma^+(P)=\sigma^+(\operatorname{cl}_{A_+\projtens\ell_1(B_P)}(AP))\subset \operatorname{cl}_{A_+\projtens\ell_1(B_P)}(A\cdot\sigma(P))=
$$
$$\operatorname{cl}_{A_+\projtens\ell_1(B_P)}(A\cdot(A_+\projtens\ell_1(B_P)))=A\projtens\ell_1(B_P).
$$ 
So we have well a defined corestriction $\sigma:P\to A\projtens\ell_1(B_P)$ which is also an $A$-morphism with norm $\langle$~at most $1$ / at most $C$~$\rangle$. Clearly, $\pi_P\sigma=1_P$, so $\pi_P$ is a $\langle$~$1$-retraction / $C$-retraction~$\rangle$ in $A-\mathbf{mod}$.

Conversely, assume $\pi_P$ has a right inverse morphism $\sigma$ of norm $\langle$~at most $1$ / at most $C$~$\rangle$. Then its coextension $\sigma^+$ also is a right inverse morphism to $\pi_P^+$ with the same norm. Again, by proposition $\langle$~\ref{MetTopProjModViaCanonicMorph} / \ref{CTopProjModViaCanonicMorph}~$\rangle$ the module $P$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective. 
\end{proof}

It is worth to mention that $\langle$~an arbitrary / only finite~$\rangle$ family of objects in $\langle$~$A-\mathbf{mod}_1$ / $A-\mathbf{mod}$~$\rangle$ have the categorical coproduct which is in fact their $\bigoplus_1$-sum. This is reason why we make additional assumption in the second paragraph of the next proposition.

\begin{proposition}\label{MetTopProjModCoprod} Let $(P_\lambda)_{\lambda\in\Lambda}$ be a family of $A$-modules. Then 

$i)$ $\bigoplus_1\{P_\lambda:\lambda\in\Lambda\}$ is metrically projective iff for all $\lambda\in\Lambda$ the $A$-module $P_\lambda$ is metrically projective;

$ii)$ $\bigoplus_1\{P_\lambda:\lambda\in\Lambda\}$ is $C$-topologically projective iff for all $\lambda\in\Lambda$ the $A$-module $P_\lambda$ is $C$-topologically projective.
\end{proposition}
\begin{proof} Denote $P:=\bigoplus_1\{P_\lambda:\lambda\in\Lambda\}$.

$i)$ The proof is literally the same as in paragraph $ii)$.

$ii)$ Assume that $P$ is $C$-topologically projective. Note that, for any $\lambda\in\Lambda$ the $A$-module $P_\lambda$ is a $1$-retract of $P$ via natural projection $p_\lambda:P\to P_\lambda$. By proposition \ref{RetrCTopProjIsCTopProj} the $A$-module $P_\lambda$ is $C$-topologically projective.

Conversely, let each $A$-module $P_\lambda$ be $C$-topologically projective. By proposition \ref{CTopProjModViaCanonicMorph} we have a family of $C$-retractions $\pi_\lambda:A_+\projtens\ell_1(S_\lambda)\to P_\lambda$. It follows that $\bigoplus_1\{\pi_\lambda:\lambda\in\Lambda\}$ is a $C$-retraction in $A-\mathbf{mod}$. As the result $P$ is a $C$-retract of 
$$
\bigoplus\nolimits_1\left\{A_+\projtens \ell_1(S_\lambda):\lambda\in\Lambda\right\}
\isom{A-\mathbf{mod}_1}
\bigoplus\nolimits_1\left\{\bigoplus\nolimits_1\{A_+:s\in S_\lambda\}:\lambda\in\Lambda\right\}
$$
$$
\isom{A-\mathbf{mod}_1}
\bigoplus\nolimits_1\{A_+:s\in S\}
$$
in $A-\mathbf{mod}$ where $S=\bigsqcup_{\lambda\in\Lambda}S_\lambda$. Clearly, the latter module is $1$-topologically projective, so by proposition \ref{RetrCTopProjIsCTopProj} the $A$-module $P$ is $C$-topologically projective.
\end{proof}

\begin{corollary}\label{MetTopProjTensProdWithl1} Let $P$ be an $A$-module and $\Lambda$ be an arbitrary set. Then $P\projtens \ell_1(\Lambda)$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective iff $P$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective.
\end{corollary}
\begin{proof} 
Note that $P\projtens \ell_1(\Lambda)\isom{A-\mathbf{mod}_1}\bigoplus_1\{P:\lambda\in\Lambda\}$. It remains to set $P_\lambda=P$ for all $\lambda\in\Lambda$ and apply proposition \ref{MetTopProjModCoprod}.
\end{proof}

%----------------------------------------------------------------------------------------
%	Metric and topological projectivity of ideals and cyclic modules
%----------------------------------------------------------------------------------------

\subsection{Metric and topological projectivity of ideals and cyclic modules}
\label{SubSectionMetricAndTopologicalProjectivityOfIdealsAndCyclicModules}

As we shall see idempotents plays a significant role in the study of metric and topological projectivity, so we shall recall one of the corollaries of Shilov's idempotent theorem [\cite{KaniBanAlg}, section 3.5]: every semisimple commutative Banach algebra with compact spectrum admits an identity, but not necessarily of norm 1. 

\begin{proposition}\label{UnIdeallIsMetTopProj}
Let $I$ be a left ideal of a Banach algebra $A$. Then

$i)$ if $I=Ap$ for some $\langle$~norm one idempotent / idempotent~$\rangle$ $p\in I$, then $I$ is $\langle$~metrically / $\Vert p\Vert$-topologically~$\rangle$ projective $A$-module;

$ii)$ if $I$ is commutative, semisimple and $\operatorname{Spec}(I)$ is compact then $I$ is topologically projective $A$-module.
\end{proposition}
\begin{proof} 
$i)$ For $A$-module maps $\pi:A_\times\to I:x\mapsto xp$ and $\sigma:I\to A_\times:x\mapsto x$ we clearly have $\pi\sigma=1_I$. Therefore $I$ is a $\langle$~$1$-retract / $\Vert p\Vert$-retract~$\rangle$ of $A_\times$. Now the result follows from propositions $\langle$~\ref{RetrMetTopProjIsMetTopProj} / \ref{RetrCTopProjIsCTopProj}~$\rangle$ and \ref{UnitalAlgIsMetTopProj}.

$ii)$ By Shilov's idempotent theorem the ideal $I$ is unital. In general the norm of this unit is not less than $1$. By paragraph $i)$ the ideal $I$ is topologically projective.
\end{proof}

The assumption of semisimplicity in \ref{UnIdeallIsMetTopProj} is not necessary.
From [\cite{DalesIntroBanAlgOpHarmAnal}, exercise 2.3.7] we know, that there exists a commutative non semisimple unital Banach algebra $A$. By proposition \ref{UnIdeallIsMetTopProj} it is topologically projective as $A$-module. 
To prove the main result of this section we need two preparatory lemmas.

\begin{lemma}\label{ImgOfAMorphFromBiIdToA} Let $I$ be a two-sided ideal of a Banach algebra $A$ which is essential as left $I$-module and let $\phi:I\to A$ be an $A$-morphism. Then $\operatorname{Im}(\phi)\subset I$.
\end{lemma}
\begin{proof} Since $I$ is a right ideal, then $\phi(ab)=a\phi(b)\in I$ for all $a,b\in I$. So $\phi(I\cdot I)\subset I$. Since $I$ is an essential left $I$-module then $I=\operatorname{cl}_A(\operatorname{span}(I\cdot I))$ and $\operatorname{Im}(\phi)\subset\operatorname{cl}_A(\operatorname{span}\phi(I\cdot I))=\operatorname{cl}_A(\operatorname{span}I)=I$.
\end{proof}

\begin{lemma}\label{GoodIdealMetTopProjIsUnital} Let $I$ be a left ideal of a Banach algebra $A$, which is $\langle$~metrically / $C$-topologically~$\rangle$ projective as $A$-module. Then the following holds:

$i)$ Assume $I$ has a left $\langle$~contractive / $c$-bounded~$\rangle$ approximate identity and for each  morphism $\phi:I\to A$ of left $A$-modules there exists a morphism $\psi:I\to I$ of right $I$-modules such that $\phi(x)y=x\psi(y)$ for all $x,y\in I$. Then $I$ has the identity of norm $\langle$~at most $1$ / at most $c$~$\rangle$;

$ii)$ Assume $I$ has a right $\langle$~contractive / $c$-bounded~$\rangle$ approximate identity and for $\langle$~$k=1$ / some $k\geq 1$~$\rangle$ and each morphism $\phi:I\to A$ of left $A$-modules there exists a morphism $\psi:I\to I$ of right $I$-modules such that $\Vert\psi\Vert\leq k\Vert\phi\Vert$ and $\phi(x)y=x\psi(y)$ for all $x,y\in I$. Then $I$ has a right identity of norm $\langle$~at most $1$ / at most $ckC$~$\rangle$.
\end{lemma} 
\begin{proof} If either $i)$ or $ii)$ holds then $I$ has a one-sided bounded approximate identity. So $I$ is an essential left $I$-module, and a fortiori an essential $A$-module. By proposition \ref{NonDegenMetTopProjCharac} we have a right inverse $A$-morphism $\sigma:I\to A\projtens \ell_1(B_I)$ of $\pi_I$ with norm  $\langle$~at most $1$ / at most $C$~$\rangle$. For each $d\in B_I$ consider $A$-morphisms $p_d:A\projtens \ell_1(B_I)\to A:a\projtens \delta_x\mapsto \delta_x(d)a$ and $\sigma_d=p_d\sigma$. Then $\sigma(x)=\sum_{d\in B_I}\sigma_d(x)\projtens \delta_d$ for all $x\in I$. From identification $A\projtens\ell_1(B_I)\isom{\mathbf{Ban}_1}\bigoplus_1\{A:d\in B_I\}$ we have $\Vert\sigma(x)\Vert=\sum_{d\in B_I} \Vert\sigma_d(x)\Vert$ for all $x\in I$. Since $\sigma$ is a right inverse morphism of $\pi_I$, then $x=\pi_I(\sigma(x))=\sum_{d\in B_I}\sigma_d(x)d$ for all $x\in I$. 

From assumption, for each $d\in B_I$ there exists a morphism of right $I$-modules $\tau_d:I\to I$ such that $\sigma_d(x)d=x\tau_d(d)$ for all $x\in I$. 

Assume $i)$ holds. From assumption, for each $d\in B_I$ there exists a morphism of right $I$-modules $\tau_d:I\to I$ such that $\sigma_d(x)d=x\tau_d(d)$ for all $x\in I$.  Let $(e_\nu)_{\nu\in N}$ be a left $\langle$~contractive / bounded~$\rangle$ approximate identity of $I$ bounded in norm by constant $\langle$~$D=1$ / $D=c$~$\rangle$. Since $\tau_d(d)\in I$ for all $d\in B_I$, then for all $S\in\mathcal{P}_0(B_I)$ holds
$$
\sum_{d\in S}\Vert \tau_d(d)\Vert
=\sum_{d\in S}\lim_{\nu}\Vert e_\nu \tau_d(d) \Vert
=\lim_{\nu}\sum_{d\in S}\Vert e_\nu \tau_d(d)\Vert
=\lim_{\nu}\sum_{d\in S}\Vert \sigma_d(e_\nu)d \Vert
$$
$$
\leq\liminf_{\nu}\sum_{d\in S}\Vert\sigma_d(e_\nu)\Vert\Vert d\Vert 
\leq\liminf_{\nu}\sum_{d\in S}\Vert\sigma_d(e_\nu)\Vert
\leq\liminf_{\nu}\sum_{d\in B_I}\Vert\sigma_d(e_\nu)\Vert
$$
$$
=\liminf_{\nu}\Vert\sigma(e_\nu)\Vert
\leq\Vert\sigma\Vert\liminf_{\nu}\Vert e_\nu\Vert
\leq D\Vert\sigma\Vert 
$$
Since $S\in \mathcal{P}_0(B_I)$ is arbitrary we have well defined element $p=\sum_{d\in B_I}\tau_d(d)$ with norm $\langle$ at most $1$ / at most $cC$~$\rangle$. For all $x\in I$ we have $x=\sum_{d\in B_I}\sigma_d(x)d=\sum_{d\in B_I}x\tau_d(d)=xp$, i.e. $p$ is a right identity for $I$. But $I$ admits a left $\langle$~contractive / $c$-bounded~$\rangle$ approximate identity, so $p$ is the identity of $I$ with $\Vert p\Vert=\lim_\nu\Vert e_\nu\Vert$. Therefore the norm of $p$ is $\langle$~at most $1$ / at most $c$~$\rangle$.

Assume $ii)$ holds. From assumption, for each $d\in B_I$ there exists a morphism of right $I$-modules $\tau_d:I\to I$ such that $\sigma_d(x)d=x\tau_d(d)$ for all $x\in I$ and $\Vert\tau_d\Vert\leq k\Vert\sigma_d\Vert$.  Let $(e_\nu)_{\nu\in N}$ be a right $\langle$~contractive / bounded~$\rangle$ approximate identity of $I$ bounded in norm by constant $\langle$~$D=1$ / $D=c$~$\rangle$. For all $x\in I$ we have
$$
\Vert\sigma_d(x)\Vert
=\Vert\sigma_d(\lim_\nu x e_\nu)\Vert
=\lim_\nu\Vert x\sigma_d(e_\nu)\Vert
\leq\Vert x\Vert\liminf_\nu\Vert\sigma_d(e_\nu)\Vert
$$
so $\Vert\sigma_d\Vert\leq \liminf_\nu\Vert\sigma_d(e_\nu)\Vert$. Then for all $S\in\mathcal{P}_0(B_I)$ holds
$$
\sum_{d\in S}\Vert \tau_d(d)\Vert
\leq \sum_{d\in S}\Vert \tau_d\Vert\Vert d\Vert
\leq k\sum_{d\in S}\Vert \sigma_d\Vert
\leq k\sum_{d\in S}\liminf_\nu \Vert \sigma_d(e_\nu)\Vert
\leq k\liminf_{\nu}\sum_{d\in S}\Vert \sigma_d(e_\nu) \Vert
$$
$$
\leq k\liminf_{\nu}\sum_{d\in B_I}\Vert \sigma_d(e_\nu) \Vert
=k\liminf_{\nu}\Vert\sigma(e_\nu)\Vert
\leq k\Vert\sigma\Vert\liminf_{\nu}\Vert e_\nu\Vert
\leq kD\Vert\sigma\Vert
$$
Since $S\in \mathcal{P}_0(B_I)$ is arbitrary we have well defined element $p=\sum_{d\in B_I}\tau_d(d)$ with norm $\langle$ at most $1$ / at most $ckC$~$\rangle$. For all $x\in I$ we have $x=\sum_{d\in B_I}\sigma_d(x)d=\sum_{d\in B_I}x\tau_d(d)=xp$, i.e. $p$ is a right identity for $I$.
\end{proof}

\begin{theorem}\label{GoodCommIdealMetTopProjIsUnital} Let $I$ be an ideal of a commutative Banach algebra $A$ and $I$ has a $\langle$~contractive / $c$-bounded~$\rangle$ approximate identity. Then $I$ is $\langle$~metrically / $c$-topologically~$\rangle$ projective as $A$-module iff $I$ has the identity of norm $\langle$~at most $1$ / at most $c$~$\rangle$.
\end{theorem} 
\begin{proof} Assume $I$ is $\langle$~metrically / $c$-topologically~$\rangle$ projective as $A$-module. Since $A$ is commutative, then for any $A$-morphism $\phi:I\to A$ and $x,y\in I$ we have $\phi(x)y=x\phi(y)$. Since $I$ has bounded approximate identity and $I$ is commutative we can apply lemma \ref{ImgOfAMorphFromBiIdToA} to get that $\phi(y)\in I$. Now by paragraph $i)$ of lemma \ref{GoodIdealMetTopProjIsUnital} we get that $I$ has the identity of norm $\langle$~at most $1$ / at most $c$~$\rangle$.

The converse immediately follows from proposition \ref{UnIdeallIsMetTopProj}.
\end{proof}

There is no analogous criterion of this theorem in relative theory. The most general result of this kind gives only a necessary condition: any ideal in a commutative Banach algebra $A$ which is relatively projective as $A$-module has a paracompact spectrum. This result is due to Helemskii [\cite{HelHomolBanTopAlg}, theorem IV.3.6]. 

Note that existence of bounded approximate identity is not necessary for the ideal of a commutative Banach algebra to be even topologically projective. Indeed, consider Banach algebra  $A_0(\mathbb{D})$ --- the ideal of disk algebra consisting of functions vanishing at zero. By combination of propositions 4.3.5  and 4.3.13 paragraph $iii)$ from \cite{DalBanAlgAutCont} we get that $A_0(\mathbb{D})$ has no bounded approximate identities. On the other hand, from [\cite{HelBanLocConvAlg}, example IV.2.2] we know that $A_0(\mathbb{D})\isom{A_0(\mathbb{D})-\mathbf{mod}} A_0(\mathbb{D})_+$, so $A_0(\mathbb{D})$ is topologically projective by proposition \ref{UnitalAlgIsMetTopProj}.

Next proposition is an obvious adaptation of purely algebraic argument on projective cyclic modules. It is almost identical to [\cite{WhiteInjmoduAlg}, proposition 2.11].

\begin{proposition}\label{MetTopProjCycModCharac} Let $I$ be a left ideal in $A_\times $. Assume the natural projection $\pi:A_\times\to A_\times/I$ is $\langle$~strictly coisometric / strictly $c$-topologically surjective~$\rangle$. Then the following holds:

$i)$ If $A_\times /I$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective as $A$-module, then there exists an idempotent $p\in I$ such that $I=Ap$ and $\Vert e_{A_\times}-p\Vert$ is $\langle$~at most $1$ / at most $cC$~$\rangle$;

$ii)$ If there exists an idempotent $p\in I$ such that $I=A_\times  p$ and $\Vert e_{A_\times }-p\Vert$ is $\langle$~at most $1$ / at most $C$~$\rangle$, then $A_\times/I$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective.
\end{proposition}
\begin{proof} $i)$ Since the natural quotient map $\pi$ is $\langle$~strictly coisometric / strictly $c$-topologically surjective~$\rangle$ and $A_\times /I$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective, then $\pi$ has a right inverse $A$-morphism $\sigma$ with norm $\langle$~at most $1$ / at most $cC$~$\rangle$. We set $e_{A_\times }-p=(\sigma\pi)(e_{A_\times })$, then $(\sigma\pi)(a)=a(e_{A_\times }-p)$. By construction, $\pi\sigma=1_{A_\times }$, so  
$$
e_{A_\times }-p=(\sigma\pi)(e_{A_\times })=(\sigma\pi)(\sigma\pi)(e_{A_\times })=(\sigma\pi)(e_{A_\times }-p)=(e_{A_\times }-p)(\sigma\pi)(e_{A_\times })=(e_{A_\times }-p)^2
$$
This equality shows that $p^2=p$. Therefore $A_\times p=\operatorname{Ker}(\sigma\pi)$ because $(\sigma\pi)(a)=a-ap$. Since $\sigma$ is injective this is equivalent to $A_\times p=\operatorname{Ker}(\pi)$ which equals to $I$. Finally, note that $\Vert e_{A_\times }-p\Vert=\Vert(\sigma\pi)(e_{A_\times})\Vert\leq\Vert\sigma\Vert\Vert\pi\Vert\Vert e_{A_\times }\Vert=\Vert\sigma\Vert$.

$ii)$ Since $p^2=p$, then we have a well defined left ideal $I=A_\times p$ and an $A$-module map $\sigma:A_\times /I\to A_\times:a+I\mapsto a-ap$. It is easy to check that  $\pi\sigma=1_{A_\times/I}$ and $\Vert\sigma\Vert\leq\Vert e_{A_\times }-p\Vert$. This means that $\pi:A_\times \to A_\times /I$ is a $\langle$~$1$-retraction / $C$-retraction~$\rangle$. From propositions \ref{UnitalAlgIsMetTopProj} and $\langle$~\ref{RetrMetTopProjIsMetTopProj} / \ref{RetrCTopProjIsCTopProj}~$\rangle$ it follows that $A_\times /I$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective.
\end{proof} 

In contrast with topological theory, there is no description of relatively projective cyclic modules. There are partial answers under additional assumptions. For example, if an ideal $I$ is complemented as Banach space in $A_\times$, then almost the same criterion as in previous proposition holds in relative theory [\cite{HelBanLocConvAlg}, proposition 7.1.29]. There are other characterizations of relatively projective cyclic modules under more mild assumptions on Banach geometry. For example, Selivanov proved that if $I$ is a two-sided ideal and either $A/I$ has the approximation property or all irreducible $A$-modules have the approximation property, then $A/I$ is relatively projective iff $A_\times\isom{A-\mathbf{mod}}I\bigoplus_1 I'$ for some left ideal $I'$ of $A$. For details see [\cite{HelHomolBanTopAlg}, chapter IV, \S 4].



%----------------------------------------------------------------------------------------
%	Metric and topological injectivity
%----------------------------------------------------------------------------------------

\subsection{Metric and topological injectivity}
\label{SubSectionMetricAndTopologicalInjectivity}

Unless otherwise stated we shall consider injectivity of right modules.

\begin{definition}[\cite{HelMetrFrQMod}, definition 4.3]\label{MetInjMod} An $A$-module $J$ is called metrically injective if for any isometric $A$-morphism $\xi:Y\to X$ and any $A$-morphism $\phi:Y\to J$ there exists an $A$-morphism $\psi:X\to J$ such that $\psi\xi=\phi$  and $\Vert\psi\Vert=\Vert\phi\Vert$.
\end{definition}

\begin{definition}[\cite{HelMetrFrQMod}, definition 4.3]\label{TopInjMod} An $A$-module $J$ is called  topologically injective if for any topologically injective $A$-morphism $\xi:Y\to X$ and any $A$-morphism $\phi:Y\to J$ there exists an $A$-morphism $\psi:X\to J$ such that $\psi\xi=\phi$.
\end{definition}

A short but more involved equivalent definition is the following: an $A$-module $J$ is called $\langle$~metrically / topologically~$\rangle$ injective, if the functor $\langle$~$\operatorname{Hom}_{\mathbf{mod}_1-A}(-,J):\mathbf{mod}_1-A\to\mathbf{Ban}_1$ / $\operatorname{Hom}_{\mathbf{mod}-A}(-,J):\mathbf{mod}-A\to\mathbf{Ban}$~$\rangle$ maps $\langle$~isometric / topologically injective~$\rangle$ $A$-morphisms into $\langle$~strictly coisometric / surjective~$\rangle$ operators.

In \cite{HelMetrFrQMod} and \cite{ShtTopFrClassicQuantMod} there were constructed two faithful functors:
$$
\square_{met}^d:A-\mathbf{mod}_1\to\mathbf{Set}:X\mapsto B_{X^*},\phi\mapsto\phi^*|_{B_{Y^*}}^{B_{X^*}},
$$
$$
\square_{top}^d:A-\mathbf{mod}\to\mathbf{HNor}:X\mapsto X^*,\phi\mapsto\phi^*
$$
The first one sends a Banach $A$-module to the unit ball of its dual and any contractive $A$-morphism to the respective birestriction of its adjoint, while the second one ``forgets'' about module and additive structure of the dual module and adjoint $A$-morphism.
In the same papers it was proved that an $A$-morphism $\xi$ is $\langle$~isometric / topologically injective~$\rangle$ iff it is $\langle$~$\square_{met}^d$-admissible / $\square_{top}^d$-admissible~$\rangle$ monomorphism and an $A$-module $J$ is $\langle$~metrically / topologically~$\rangle$ injective iff it is $\langle$~$\square_{met}^d$-injective / $\square_{top}^d$-injective~$\rangle$. Thus, from general categorical scheme we immediately get the following proposition.

\begin{proposition}\label{RetrMetTopInjIsMetTopInj} Any retract of $\langle$~metrically / topologically~$\rangle$ injective module in $\langle$~$A-\mathbf{mod}_1$ / $A-\mathbf{mod}$~$\rangle$ is again $\langle$~metrically / topologically~$\rangle$ injective.
\end{proposition}

It was also shown that the rigged category $\langle$~$(\mathbf{mod}_1-A,\square_{met}^d)$ / $(\mathbf{mod}-A,\square_{top}^d)$~$\rangle$ is cofreedom loving and that $\langle$~$\square_{met}^d$-cofree / $\square_{top}^d$-cofree~$\rangle$ modules are isomorphic in $\langle$~$\mathbf{mod}_1-A$ / $\mathbf{mod}-A$~$\rangle$ to $\mathcal{B}(A_+, \ell_\infty(\Lambda))$ for some set $\Lambda$. Even more, for any $A$-module $X$ there exists a $\langle$~$\square_{met}^d$-admissible / $\square_{top}^d$-admissible~$\rangle$ monomorphism
$$
\rho_X^+:X\to\mathcal{B}(A_+,\ell_\infty(B_{X^*})):x\mapsto(a\mapsto(f\mapsto f(x\cdot a)))
$$
As the consequence of general result on rigged categories we get

\begin{proposition}\label{MetTopInjModViaCanonicMorph}
The module $J$ is $\langle$~metrically / topologically~$\rangle$ injective iff $\rho_J^+$ is a coretraction in $\langle$~$\mathbf{mod}_1-A$ / $\mathbf{mod}-A$~$\rangle$.
\end{proposition}

Since $\langle$~$\square_{met}^d$-cofree / $\square_{top}^d$-cofree~$\rangle$ modules are the same up to isomorphisms in $\mathbf{mod}-A$ and any retraction in $\mathbf{mod}_1-A$ is a retraction in $\mathbf{mod}-A$, then from proposition \ref{RetrMetTopInjIsMetTopInj} we see that any metrically injective $A$-module is topologically injective. Recall that every relatively injective module is a retract in $\mathbf{mod}-A$ of $\mathcal{B}(A_+,E)$ for some Banach space $E$, therefore every topologically injective $A$-module is relatively injective. We summarize all these in the following proposition.

\begin{proposition}\label{MetInjIsTopInjAndTopInjIsRelInj} Every metrically injective module is topologically injective and every topologically injective module is relatively injective.
\end{proposition}

A quantitative version of the definition of topological injectivity was given by White,  though he used a somewhat different terminology.

\begin{definition}[\cite{WhiteInjmoduAlg}, definition 3.4]\label{CTopInjMod} An $A$-module $J$ is called  $C$-topologically injective if for any $c$-topologically injective $A$-morphism $\xi:Y\to X$ and any $A$-morphism $\phi:Y\to J$ there exists an $A$-morphism $\psi:X\to J$ such that $\psi\xi=\phi$ and $\Vert\psi\Vert\leq c C\Vert\phi\Vert$.
\end{definition}

We shall need the following facts about this type of injectivity.

\begin{proposition}[\cite{WhiteInjmoduAlg}, lemma 3.7]\label{RetrCTopInjIsCTopInj} Any $c$-retract of $C$-topologically injective module is $cC$-topologically injective.
\end{proposition}

\begin{proposition}[\cite{WhiteInjmoduAlg}, proposition 3.10]\label{CTopInjModViaCanonicMorph} An $A$-module $J$ is $C$-topologically injective iff $\rho_J^+$ is a $C$-coretraction in $\mathbf{mod}-A$.
\end{proposition}

As the consequence, a Banach module is topologically injective iff it is $C$-topologically injective for some $C$. One more important consequence of proposition \ref{CTopInjModViaCanonicMorph} is the following.

\begin{proposition}\label{MetInjIsOneTopInj} An $A$-module is metrically injective iff it is $1$-topologically injective.
\end{proposition}

We shall exploit both definitions \ref{TopInjMod} and \ref{CTopInjMod} without further reference for their equivalence. 

Let us proceed to examples. If we regard the category of Banach spaces as the category of right Banach modules over zero algebra, we may speak of $\langle$~metrically / topologically~$\rangle$ injective Banach spaces. All results mentioned above hold for this type of injectivity. An equivalent definition says that a Banach space is $\langle$~metrically / topologically~$\rangle$ injective if it is $\langle$~contractively complemented / complemented ~$\rangle$ in any ambient Banach space. The typical examples of metrically injective Banach spaces are $L_\infty$-spaces. Only metrically injective Banach spaces are completely understood --- these spaces are isometrically isomorphic to $C(K)$-space for some extremely disconnected compact Hausdorff space $K$ [\cite{LaceyIsomThOfClassicBanSp}, theorem 3.11.6]. Usually such topological spaces are referred to as Stonean spaces.  For the contemporary results on topologically injective Banach spaces see [\cite{JohnLinHandbookGeomBanSp}, chapter 40].

\begin{proposition}\label{DualOfUnitalAlgIsMetTopInj} The right $A$-module $A_\times^*$ is metrically and $1$-topologically injective.
\end{proposition}
\begin{proof} Consider arbitrary $A$-morphism $\phi:Y\to A_\times^*$ and isometric $A$-morphism $\xi:Y\to X$. Define a bounded linear functional $f:Y\to\mathbb{C}:y\mapsto \phi(y)(e_{A_\times})$. Since $\xi$ is an isometry, then by Hahn-Banach theorem we can extend $f$ to some bounded linear functional $g:X\to\mathbb{C}$ with the same norm. Consider $A$-morphism $\psi:X\to A_\times^*:x\mapsto (a\mapsto g(x\cdot a))$. Clearly, $\Vert\psi\Vert\leq\Vert g\Vert=\Vert f\Vert\leq\Vert\phi\Vert$. On the other hand $\psi\xi=\phi$, so $\Vert\phi\Vert\leq\Vert\psi\Vert\Vert\xi\Vert=\Vert\psi\Vert$. Thus $\Vert\phi\Vert=\Vert\psi\Vert$. Therefore we proved by definition, that $A_\times^*$ is metrically injective $A$-module. By proposition \ref{MetInjIsOneTopInj} it is $1$-topologically injective $A$-module.
\end{proof}

\begin{proposition}\label{NonDegenMetTopInjCharac}  Let $J$ be a faithful $A$-module. Then $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective iff the map $\rho_J:J\to\mathcal{B}(A,\ell_\infty(B_{J^*})):x\mapsto(a\mapsto(f\mapsto f(x\cdot a)))$ is a $\langle$~$1$-coretraction / $C$-coretraction~$\rangle$ in $\mathbf{mod}-A$.
\end{proposition} 
\begin{proof}
If $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective, then by proposition $\langle$~\ref{MetTopInjModViaCanonicMorph} / \ref{CTopInjModViaCanonicMorph}~$\rangle$ the $A$-morphism $\rho_J^+$ has right inverse morphism $\tau^+$, with norm $\langle$~at most $1$ / at most $C$~$\rangle$. Assume we are given an operator $T\in \mathcal{B}(A_+,\ell_\infty(B_{J^*}))$, such that $T|_A=0$. Fix $a\in A$, then $T\cdot a=0$, and so $\tau^+(T)\cdot a=\tau^+(T\cdot a)=0$. Since $J$ is faithful and $a\in A$ is arbitrary, then $\tau^+(T)=0$. Define $p:A_+\to A$ be the natural projection from $A_+$ onto $A$, then define $A$-morphisms $j=\mathcal{B}(p,\ell_\infty(B_{J^*}))$ and $\tau =\tau^+ j$. For any $a\in A$ and $T\in\mathcal{B}(A,\ell_\infty(B_{J^*}))$ we have $\tau (T\cdot a)-\tau (T)\cdot a=\tau^+(j(T\cdot a)-j(T)\cdot a)=0$, because $j(T\cdot a)-j(T)\cdot a|_A=0$. Therefore $\tau $ is an $A$-morphism. Note that $\Vert\tau \Vert\leq\Vert\tau^+\Vert\Vert j\Vert\leq \Vert\tau^+\Vert$. Therefore $\tau$ has norm $\langle$~at most $1$ / at most $C$~$\rangle$. Obviously, for all $x\in J$ we have $\rho_J^+(x)-j(\rho_J(x))|_A=0$, so $\tau^+(\rho_J^+(x)-j(\rho_J(x)))=0$. As a consequence $\tau (\rho_J(x))=\tau^+(j(\rho_J(x)))=\tau^+(\rho_J^+(x))=x$ for all $x\in J$. Since $\tau \rho_J=1_J$, then $\rho_J$ is a  $\langle$~$1$-coretraction / $C$-coretraction~$\rangle$  in $\mathbf{mod}-A$.

Conversely, assume $\rho_J$ is a $\langle$~$1$-coretraction / $C$-coretraction~$\rangle$, that is has a right inverse morphism $\tau $ with norm $\langle$~at most $1$ / at most $C$~$\rangle$. Define $i:A\to A_+$ to be the natural embedding of $A$ into $A_+$ and define $A$-morphism $q=\mathcal{B}(i,\ell_\infty(B_{J^*}))$. Obviously, $\rho_J=q\rho_J^+$. Consider $A$-morphism $\tau^+=\tau q$. Note that $\Vert\tau^+\Vert\leq\Vert\tau \Vert\Vert q\Vert\leq \Vert\tau \Vert$. Therefore $\tau^+$ has norm $\langle$~at most $1$ / at most $C$~$\rangle$. Clearly $\tau^+\rho_J^+=\tau q\rho_J^+=\tau \rho_J=1_J$. So $\rho_J^+$ is a $\langle$~$1$-coretraction / $C$-coretraction~$\rangle$ and by proposition $\langle$~\ref{MetTopInjModViaCanonicMorph} / \ref{CTopInjModViaCanonicMorph}~$\rangle$ the $A$-module $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective.
\end{proof}

It is worth to mention that $\langle$~arbitrary / only finite~$\rangle$ family of objects in $\langle$~$\mathbf{mod}_1-A$ / $\mathbf{mod}-A$~$\rangle$ have the categorical product which in fact is their $\bigoplus_\infty$-sum. This is the reason why we make additional assumption in the second paragraph of the next proposition.

\begin{proposition}\label{MetTopInjModProd} Let $(J_\lambda)_{\lambda\in\Lambda}$ be a family of $A$-modules. Then 

$i)$ $\bigoplus_\infty\{J_\lambda:\lambda\in\Lambda\}$ is metrically injective iff for all $\lambda\in\Lambda$ the $A$-module $J_\lambda$ is metrically injective;

$ii)$ $\bigoplus_\infty\{J_\lambda:\lambda\in\Lambda\}$ is $C$-topologically injective iff for all $\lambda\in\Lambda$ the $A$-module $J_\lambda$ is a $C$-topologically injective.
\end{proposition}
\begin{proof} Denote $J:=\bigoplus_\infty\{J_\lambda:\lambda\in\Lambda\}$.

$i)$ The proof is literally the same as in paragraph $ii)$.

$ii)$ Assume that $J$ is $C$-topologically injective. Note that, for any $\lambda\in\Lambda$ the $A$-module $J_\lambda$ is a $1$-retract of $J$ via natural projection $p_\lambda:J\to J_\lambda$. By proposition \ref{RetrCTopInjIsCTopInj} the $A$-module $J_\lambda$ is $C$-topologically injective.

Conversely, let each $A$-module $J_\lambda$ be $C$-topologically injective. By proposition \ref{CTopInjModViaCanonicMorph} we have a family of $C$-coretractions $\rho_\lambda:J_\lambda\to\mathcal{B}(A_+,\ell_\infty(S_\lambda))$. It follows that $\bigoplus_\infty\{\rho_\lambda:\lambda\in\Lambda\}$ is a $C$-coretraction in $A-\mathbf{mod}$. As the result $J$ is a $C$-retract of 
$$
\bigoplus\nolimits_\infty\{\mathcal{B}(A_+,\ell_\infty(S_\lambda)):\lambda\in\Lambda\}
\isom{\mathbf{mod}_1-A}
\bigoplus\nolimits_\infty\left\{\bigoplus\nolimits_\infty\{ A_+^*:s\in S_\lambda\}:\lambda\in\Lambda\right\}
\isom{\mathbf{mod}_1-A}
$$
$$
\bigoplus\nolimits_\infty\{A_+^*:s\in S\}
\isom{\mathbf{mod}_1-A}
\mathcal{B}(A_+,\ell_\infty(S))
$$
in $\mathbf{mod}-A$, where $S=\bigsqcup_{\lambda\in\Lambda}S_\lambda$. Clearly, the latter module is $1$-topologically injective, so by proposition \ref{RetrCTopInjIsCTopInj} the $A$-module $J$ is $C$-topologically injective.
\end{proof}

\begin{corollary}\label{MetTopInjlInftySum} Let $J$ be an $A$-module and $\Lambda$ be an arbitrary set. Then $\bigoplus_\infty\{J:\lambda\in\Lambda\}$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective iff $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective.
\end{corollary}
\begin{proof} The result immediately follows from proposition \ref{MetTopInjModProd} if one set $J_\lambda=J$ for all $\lambda\in\Lambda$.
\end{proof}

\begin{proposition}\label{MapsFroml1toMetTopInj} Let $J$ be an $A$-module and $\Lambda$ be an arbitrary set. Then $\mathcal{B}(\ell_1(\Lambda),J)$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective iff $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective.
\end{proposition}
\begin{proof} 
Assume $\mathcal{B}(\ell_1(\Lambda), J)$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective. Take any $\lambda\in\Lambda$ and consider contractive $A$-morphisms $i_\lambda:J\to\mathcal{B}(\ell_1(\Lambda),J):x\mapsto(f\mapsto f(\lambda)x)$ and $p_\lambda:\mathcal{B}(\ell_1(\Lambda),J)\to J:T\mapsto T(\delta_\lambda)$. Clearly, $p_\lambda i_\lambda=1_J$, so by proposition $\langle$~\ref{RetrMetTopInjIsMetTopInj} / \ref{RetrCTopInjIsCTopInj}~$\rangle$ the $A$-module $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective as $1$-retract of $\langle$~metrically / $1$-topologically~$\rangle$ injective $A$-module $\mathcal{B}(\ell_1(\Lambda),J)$.

Conversely, since $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective, by proposition $\langle$~\ref{MetTopInjModViaCanonicMorph} / \ref{CTopInjModViaCanonicMorph}~$\rangle$ the $A$-morphism $\rho_J^+$ is a $\langle$~$1$-coretraction / $C$-coretraction~$\rangle$. Apply the functor $\mathcal{B}(\ell_1(\Lambda),-)$ to this coretraction to get another $\langle$~$1$-coretraction / $C$-coretraction~$\rangle$ denoted by $\mathcal{B}(\ell_1(\Lambda),\rho_J^+)$. Note that 
$$
\mathcal{B}(\ell_1(\Lambda),\ell_\infty(B_{J^*}))\isom{\mathbf{Ban}_1}(\ell_1(\Lambda)\projtens \ell_1(B_{J^*}))^*\isom{\mathbf{Ban}_1}\ell_1(\Lambda\times B_{J^*})^*\isom{\mathbf{Ban}_1}\ell_\infty(\Lambda\times B_{J^*}),
$$ 
so we have isometric isomorphisms of Banach modules
$$
\mathcal{B}(\ell_1(\Lambda),\mathcal{B}(A_+,\ell_\infty(B_{J^*})))\isom{\mathbf{mod}_1-A}\mathcal{B}(A_+,\mathcal{B}(\ell_1(\Lambda),\ell_\infty(B_{J^*}))\isom{\mathbf{mod}_1-A}\mathcal{B}(A_+,\ell_\infty(\Lambda\times B_{J^*})).
$$ 
Therefore $\mathcal{B}(\ell_1(\Lambda),J)$ is a $\langle$~$1$-retract / $C$-retract~$\rangle$ of $\langle$~metrically / $1$-topologically~$\rangle$ injective $A$-module $\mathcal{B}(A_+,\ell_\infty(\Lambda\times B_{J^*}))$. By proposition $\langle$~\ref{RetrMetTopInjIsMetTopInj} / \ref{RetrCTopInjIsCTopInj}~$\rangle$ the $A$-module $\mathcal{B}(\ell_1(\Lambda), J)$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective.
\end{proof}

%----------------------------------------------------------------------------------------
%	Metric and topological flatness
%----------------------------------------------------------------------------------------

\subsection{Metric and topological flatness}
\label{SubSectionMetricAndTopologicalFlatness}

To save the homogeneity of notation we call metrically flat $A$-modules of \cite{HelMetrFlatNorMod} where they were named extremely flat.

\begin{definition}[\cite{HelMetrFlatNorMod}, I]\label{MetFlatMod} A left $A$-module $F$ is called metrically flat if for each isometric $A$-morphism $\xi:X\to Y$ of right $A$-modules the operator $\xi\projmodtens{A} 1_F:X\projmodtens{A} F\to Y\projmodtens{A} F$ is isometric.
\end{definition}

\begin{definition}[\cite{HelMetrFlatNorMod}, definition I]\label{TopFlatMod} A left $A$-module $F$ is called topologically flat if for each topologically injective $A$-morphism $\xi:X\to Y$ of right $A$-modules the operator $\xi\projmodtens{A} 1_F:X\projmodtens{A} F\to Y\projmodtens{A} F$ is topologically injective.
\end{definition}

A short but more involved definition is the following: an $A$-module $F$ is called $\langle$~metrically / topologically~$\rangle$ flat, if the functor $\langle$~$-\projmodtens{A}F:A-\mathbf{mod}_1\to\mathbf{Ban}_1$ / $-\projmodtens{A}F:A-\mathbf{mod}\to\mathbf{Ban}$~$\rangle$ maps $\langle$~isometric / topologically injective~$\rangle$ $A$-morphisms into $\langle$~isometric / topologically injective~$\rangle$ operators.

Again, regard the category of Banach spaces as the category of left Banach modules over zero algebra, then we get the definition of $\langle$~metrically / topologically~$\rangle$ flat Banach space. From Grothendieck's paper \cite{GrothMetrProjFlatBanSp} it follows that any metrically flat Banach space is isometrically isomorphic to $L_1(\Omega,\mu)$ for some measure space $(\Omega,\Sigma,\mu)$. For topologically flat Banach spaces, in contrast with topologically injective ones, we also have a criterion [\cite{DefFloTensNorOpId}, corollary 23.5(1)]: a Banach space is topologically flat iff it is an $\mathscr{L}_1^g$-space.


It is well known that an $A$-module $F$ is relatively flat iff $F^*$ is relatively injective [\cite{HelBanLocConvAlg}, theorem 7.1.42]. Next proposition is an obvious analog of this result.

\begin{proposition}\label{MetTopFlatCharac} The $A$-module $F$ is $\langle$~metrically / topologically~$\rangle$ flat iff $F^*$ is $\langle$~metrically / topologically~$\rangle$ injective.
\end{proposition}
\begin{proof} Consider any $\langle$~isometric / topologically injective~$\rangle$ morphism of right $A$-modules, call it $\xi:X\to Y$. The operator $\xi\projmodtens{A} 1_F$ is $\langle$~isometric / topologically injective~$\rangle$ iff the adjoint operator $(\xi\projmodtens{A} 1_F)^*$ is $\langle$~strictly coisometric / topologically surjective~$\rangle$  [\cite{HelLectAndExOnFuncAn}, exercises 4.4.6, 4.4.7]. Since operators $(\xi\projmodtens{A} 1_F)^*$ and $\mathcal{B}_A(\xi,F^*)$ are equivalent in $\mathbf{Ban}_1$ via universal property of projective module tensor product, then we get that $\xi\projmodtens{A} 1_F$ is $\langle$~isometric / topologically injective~$\rangle$ iff $\mathcal{B}_A(\xi,F^*)$ is $\langle$~strictly coisometric / topologically surjective~$\rangle$. Since $\xi$ is arbitrary we conclude that $F$ is  $\langle$~metrically / topologically~$\rangle$ flat iff $F^*$ is $\langle$~metrically / topologically~$\rangle$ injective.
\end{proof}

Combining proposition \ref{MetTopFlatCharac} with propositions  \ref{RetrMetTopInjIsMetTopInj} and \ref{MetInjIsTopInjAndTopInjIsRelInj} we get the following.

\begin{proposition}\label{RetrMetTopFlatIsMetTopFlat} Any retract of $\langle$~metrically / topologically~$\rangle$ flat module in $\langle$~$A-\mathbf{mod}_1$ / $A-\mathbf{mod}$~$\rangle$ is again $\langle$~metrically / topologically~$\rangle$ flat.
\end{proposition}

\begin{proposition}\label{MetFlatIsTopFlatAndTopFlatIsRelFlat} Every metrically flat module is topologically flat and every topologically flat module is relatively flat.
\end{proposition}

A quantitative version of the definition of topological flatness was given by White, though he used a somewhat different terminology. Unfortunately, his definition was erroneous, meanwhile the results were correct. So we take responsibility to fix the definition.

\begin{definition}[\cite{WhiteInjmoduAlg}, definition 4.8]\label{CTopFlatMod} A left $A$-module $F$ is called $C$-topologically flat if for each $c$-topologically injective $A$-morphism $\xi:X\to Y$ of right $A$-modules the operator $\xi\projmodtens{A} 1_F:X\projmodtens{A} F\to Y\projmodtens{A} F$ is $cC$-topologically injective.
\end{definition}

The key result in the study of this type of flatness is the following.

\begin{proposition}[\cite{WhiteInjmoduAlg}, lemma 4.10]\label{CTopFlatCharac} An $A$-module $F$ is $C$-topologically flat iff $F^*$ is $C$-topologically injective.
\end{proposition}

As the consequence, a Banach module is topologically flat iff it is $C$-topologically flat for some $C$. One more important consequence of propositions \ref{MetInjIsOneTopInj} and \ref{CTopFlatCharac} is the following.

\begin{proposition}\label{MetFlatIsOneTopFlat} An $A$-module is metrically flat iff it is $1$-topologically flat.
\end{proposition}


We shall exploit both definitions \ref{TopInjMod} and \ref{CTopInjMod} without further reference for their equivalence. From propositions \ref{CTopFlatCharac} and \ref{RetrCTopInjIsCTopInj} we also get the following.

\begin{proposition}\label{RetrCTopFlatIsCTopFlat} Any $c$-retract of $C$-topologically flat module is $cC$-topologically flat.
\end{proposition}

\begin{proposition}\label{DualMetTopProjIsMetrInj} Let $P$ be a $\langle$~metrically / $C$-topologically~$\rangle$ projective $A$-module, and $\Lambda$ be an arbitrary set. Then $\mathcal{B}(P,\ell_\infty(\Lambda))$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective $A$-module. In particular, $P^*$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective $A$-module.
\end{proposition}
\begin{proof} From proposition $\langle$~\ref{MetTopProjModViaCanonicMorph} / \ref{RetrCTopProjIsCTopProj}~$\rangle$ we know that $\pi_P^+$ is a $\langle$~$1$-retraction / $C$-retraction~$\rangle$. Then the $A$-morphism $\rho^+=\mathcal{B}(\pi_P^+,\ell_\infty(\Lambda))$ is a $\langle$~$1$-coretraction / $C$-coretraction~$\rangle$. Note that, 
$$
\mathcal{B}(A_+\projtens\ell_1(B_P),\ell_\infty(\Lambda))\isom{\mathbf{mod}_1-A}\mathcal{B}(A_+,\mathcal{B}(\ell_1(B_P),\ell_\infty(\Lambda)))\isom{\mathbf{mod}_1-A}\mathcal{B}(A_+,\ell_\infty(B_P\times\Lambda)).
$$ 
Thus we showed that $\rho^+$ is a $\langle$~$1$-coretraction / $C$-coretraction~$\rangle$ from $\mathcal{B}(P,\ell_\infty(\Lambda))$ into $\langle$~metrically / $1$-topologically~$\rangle$ injective $A$-module. By proposition $\langle$~\ref{RetrMetTopInjIsMetTopInj} / \ref{RetrCTopInjIsCTopInj}~$\rangle$ the $A$-module $\mathcal{B}(P,\ell_\infty(\Lambda))$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective. To prove the last claim, just set $\Lambda=\mathbb{N}_1$.
\end{proof}

As the consequence of propositions \ref{CTopFlatCharac} and \ref{DualMetTopProjIsMetrInj} we get

\begin{proposition}\label{MetTopProjIsMetTopFlat} Every $\langle$~metrically / $C$-topologically~$\rangle$ projective module is $\langle$~metrically / $C$-topologically~$\rangle$ flat.
\end{proposition}

As we shall see later $\langle$~metric / topological~$\rangle$ flatness is a weaker property than $\langle$~metric / topological~$\rangle$ projectivity.

\begin{proposition}\label{MetTopFlatModCoProd} Let $(F_\lambda)_{\lambda\in\Lambda}$ be family of $A$-modules. Then 

$i)$ $\bigoplus_1\{F_\lambda:\lambda\in\Lambda\}$ is metrically flat iff for all $\lambda\in\Lambda$ the $A$-module $F_\lambda$ is metrically flat;

$ii)$ $\bigoplus_1\{F_\lambda:\lambda\in\Lambda\}$ is $C$-topologically flat iff for all $\lambda\in\Lambda$ the $A$-module $F_\lambda$ is $C$-topologically flat.
\end{proposition}
\begin{proof} By proposition $\langle$~\ref{MetTopFlatCharac} / \ref{CTopFlatCharac}~$\rangle$ an $A$-module $F$ is $\langle$~metrically / $C$-topologically~$\rangle$ flat iff $F^*$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective. It is remains to apply proposition \ref{MetTopInjModProd} with $J_\lambda=F_\lambda^*$ for all $\lambda\in\Lambda$ and recall that $\left(\bigoplus_1\{ F_\lambda:\lambda\in\Lambda\}\right)^*\isom{\mathbf{mod}_1-A}\bigoplus_\infty\{ F_\lambda^*:\lambda\in\Lambda\}$.
\end{proof}

As we have seen flatness is a weakened version of projectivity. Loosely speaking flatness is ``projectivity with respect to second duals''. We can give this statement a precise meaning.

\begin{proposition}\label{MetTopFlatSecondDualCharac} Let $F$ be a left Banach $A$-module. Then the following are equivalent:

$i)$ $F$ is $\langle$~metrically / $C$-topologically~$\rangle$ flat;

$ii)$ for any $\langle$~strictly coisometric / strictly $c$-topologically surjective~$\rangle$ $A$-morphism $\xi:X\to Y$ and for any $A$-morphism $\phi:F\to Y$ there exists an $A$-morphism $\psi:P\to X^{**}$ such that $\xi^{**}\psi=\iota_Y\phi$ and $\langle$~$\Vert\psi\Vert=\Vert\phi\Vert$ / $\Vert\psi\Vert\leq cC\Vert\phi\Vert$~$\rangle$;

$iii)$ there exists an $A$-morphism $\rho:F\to (A_+\projtens \ell_1(B_F))^{**}$ with norm $\langle$~at most $1$ / at most $C$~$\rangle$ such that $(\pi_F^+)^{**}\rho=\iota_F$.
\end{proposition}
\begin{proof} $i)\implies ii)$ Again, consider arbitrary $\langle$~strictly coisometric / strictly $c$-topologically surjective~$\rangle$ $A$-morphism $\xi:X\to Y$ and arbitrary $A$-morphism $\phi:F\to Y$. By [\cite{HelLectAndExOnFuncAn}, exercise 4.4.6] we know that $\xi^*$ is $\langle$~isometric / $c$-topologically injective~$\rangle$. Since $F$ is $\langle$~metrically / $C$-topologically~$\rangle$ flat then $(\xi^*\projmodtens{A}1_F)$ is $\langle$~isometric / $cC$-topologically injective~$\rangle$ too. Therefore $(\xi^*\projmodtens{A}1_F)^*$ is $\langle$~strictly coisometric / strictly $cC$-topologically surjective~$\rangle$ by [\cite{HelLectAndExOnFuncAn}, exercise 4.4.7]. Note that $(\xi^*\projmodtens{A}1_F)^*$ and $\mathcal{B}_A(F,\xi^{**})$ are equivalent in $\mathbf{Ban}_1$ thanks to the law of adjoint associativity. So $\mathcal{B}_A(F,\xi^{**})$ is $\langle$~strictly coisometric / strictly $cC$-topologically surjective~$\rangle$ too. The latter implies that for the operator $\iota_Y\phi$ we can find an $A$-morphism $\psi:Y\to X^{**}$ such that $\xi^{**}\psi=\iota_Y\phi$ and  $\langle$~$\Vert\psi\Vert=\Vert\iota_Y\phi\Vert=\Vert\phi\Vert$ / $\Vert\psi\Vert\leq cC\Vert\iota_Y\phi\Vert=cC\Vert\phi\Vert$~$\rangle$

$ii)\implies iii)$ Set $\xi=\pi_F^+$ and $\phi=1_F$. Since $\xi$ is $\langle$~strictly coisometric/ strictly $1$-topologically surjective~$\rangle$, then from assumption we get an $A$-morphism $\rho:F\to (A_+\projtens\ell_1(B_F))^{**}$ such that $(\pi_F^+)^{**}\rho=\iota_F 1_F=\iota_F$ and $\langle$~$\Vert\rho\Vert\leq \Vert\phi\Vert=1$ / $\Vert\rho\Vert\leq 1\cdot C\Vert\phi\Vert=C$~$\rangle$.

$iii)\implies i)$ Let $\rho$ be a right inverse $A$-morphism for $(\pi_F^+)^{**}$ with norm $\langle$~at most $1$ / at most $C$~$\rangle$. Consider $A$-morphism $\tau=\rho^*\iota_{(A_+\projtens\ell_1(B_F))^*}$. Clearly, its norm is $\langle$~at most $1$ / at most $C$~$\rangle$. For any $f\in F^*$ and $x\in F$ we have
$$
(\tau(\pi_F^+)^*)(f)(x)
=\rho^*(\iota_{(A_+\projtens\ell_1(B_F))^*}((\pi_F^+)^*(f)))(x)
=\iota_{(A_+\projtens\ell_1(B_F))^*}((\pi_F^+)^*(f))(\rho(x))
$$
$$
=\rho(x)((\pi_F^+)^*(f))
=(\pi_F^+)^{**}(\rho(x)))(f)
=\iota_F(x)(f)
=f(x)
$$
So $\tau(\pi_F^+)^*=1_{F^*}$, which means $F^*$ is a with norm $\langle$~$1$-retract / $C$-retract~$\rangle$ of $(A_+\projtens\ell_1(B_F))^*$. The latter module is $\langle$~metrically / $1$-topologically~$\rangle$ injective, because $(A_+\projtens\ell_1(B_F))^*\isom{\mathbf{mod}_1-A}\mathcal{B}(A_+,\ell_\infty(B_F))$. By proposition $\langle$~\ref{RetrMetTopInjIsMetTopInj} / \ref{RetrCTopInjIsCTopInj}~$\rangle$ the $A$-module $F^*$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective. By proposition $\langle$~\ref{MetTopFlatCharac} / \ref{CTopFlatCharac}~$\rangle$ this is equivalent to $\langle$~metric / $C$-topological~$\rangle$ flatness of $F$.
\end{proof}


%----------------------------------------------------------------------------------------
%	Metric and topological flatness of ideals and cyclic modules
%----------------------------------------------------------------------------------------

\subsection{Metric and topological flatness of ideals and cyclic modules}
\label{SubSectionMetricAndTopologicalFlatnessOfIdealsAndCyclicModules}

In this section we study conditions under which ideals and cyclic modules are metrically or topologically flat. The proofs are somewhat similar to those used in the study of relative flatness of ideals and cyclic modules.

\begin{proposition}\label{MetTopFlatIdealsInUnitalAlg} Let $I$ be a left ideal of $A_\times $ and $I$ has a right $\langle$~contractive / $c$-bounded~$\rangle$ approximate identity. Then $I$ is $\langle$~metrically / $c$-topologically~$\rangle$ flat.
\end{proposition}
\begin{proof} Let $\mathfrak{F}$ be the section filter on $N$ and let $\mathfrak{U}$ be an ultrafilter dominating $\mathfrak{F}$. For a fixed $f\in I^*$ and $a\in A_\times $ we have $|f(a e_\nu)|\leq\Vert f\Vert\Vert a\Vert\Vert e_\nu\Vert\leq c\Vert f\Vert\Vert a\Vert$ i.e. $(f(ae_\nu))_{\nu\in N}$ is a bounded net of complex numbers. Therefore we have a well defined limit $\lim_{\mathfrak{U}}f(ae_\nu)$ along ultrafilter $\mathfrak{U}$. Now it is routine to check that $\sigma:A_\times ^*\to I^*:f\mapsto (a\mapsto \lim_{\mathfrak{U}}f(ae_\nu))$ is an $A$-morphism with norm $\langle$~at most $1$ / at most $c$~$\rangle$. Let $\rho:I\to A_\times$ be the natural embedding, then for all $f\in A_\times^*$ and $a\in I$ holds
$$
\rho^*(\sigma(f))(a)
=\sigma(f)(\rho(a))
=\sigma(f)(a)
=\lim_{\mathfrak{U}}f(a e_\nu)
=\lim_{\nu}f(a e_\nu)
=f(\lim_{\nu}a e_\nu)
=f(a)
$$
i.e. $\sigma:I^*\to A_\times^*$ is a $\langle$~$1$-coretraction / $c$-coretraction~$\rangle$. The right $A$-module $A_\times ^*$ is $\langle$~metrically / $1$-topologically~$\rangle$ injective by proposition \ref{DualOfUnitalAlgIsMetTopInj}, hence its $\langle$~$1$-retract / $c$-retract~$\rangle$ $I^*$ is $\langle$~metrically / $c$-topologically~$\rangle$ injective. Now from proposition $\langle$~\ref{MetTopFlatCharac} / \ref{CTopFlatCharac}~$\rangle$ we conclude that the $A$-module $I$ is $\langle$~metrically / $c$-topologically~$\rangle$ flat.
\end{proof}

Note that the same sufficient condition holds for relative flatness for ideals of $A_\times$ [\cite{HelBanLocConvAlg}, proposition 7.1.45]. Now we are able to give an example of a metrically flat module which is not even topologically projective. Clearly $\ell_\infty(\mathbb{N})$-module $c_0(\mathbb{N})$ is not unital as ideal but admits a contractive approximate identity. By theorem \ref{GoodCommIdealMetTopProjIsUnital} it is not topologically projective, but it is metrically flat by proposition \ref{MetTopFlatIdealsInUnitalAlg}.

The ``metric'' part of the following proposition is a slight modification of [\cite{WhiteInjmoduAlg}, proposition 4.11]. The case of topological flatness was solved by Helemskii in [\cite{HelHomolBanTopAlg}, theorem VI.1.20].

\begin{proposition}\label{MetTopFlatCycModCharac} Let $I$ be a left proper ideal of $A_\times $. Then the following are equivalent:

$i)$ $A_\times /I$ is $\langle$~metrically / $C$-topologically~$\rangle$ flat $A$-module;

$ii)$ $I$ has a right bounded approximate identity $(e_\nu)_{\nu\in N}$ with $\sup_{\nu\in N}\Vert e_{A_\times }-e_\nu\Vert$ $\langle$~at most $1$ / at most $C$~$\rangle$
\end{proposition}
\begin{proof} $i)$$\implies$$ ii)$  Since $A_\times /I$ is $\langle$~metrically / $C$-topologically~$\rangle$ flat, then by proposition $\langle$~\ref{MetTopFlatCharac} / \ref{CTopFlatCharac}~$\rangle$ the right $A$-module $(A_\times /I)^*$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective. Let $\pi:A_\times \to A_\times /I$ be the natural quotient map, then $\pi^*:(A_\times /I)^*\to A_\times ^*$ is an isometry. Since $(A_\times /I)^*$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective, then $\pi^*$ is a coretraction, i.e. there exists a $\langle$~strictly coisometric / topologically surjective~$\rangle$ $A$-morphism $\tau:A_\times ^*\to (A_\times /I)^*$ of norm $\langle$~at most $1$ / at most $C$~$\rangle$ such that $\tau\pi^*=1_{(A_\times /I)^*}$. Consider $p\in A^{**}$ such that $\iota_{A_\times }(e_{A_\times })-p=\tau^*(\pi^{**}(\iota_{A_\times }(e_{A_\times })))$. Fix $f\in I^\perp$. Since $I^\perp=\pi^*((A_\times /I)^*)$, then there exists $g\in (A_\times /I)^*$ such that $f=\pi^*(g)$. Thus,
$$
(\iota_{A_\times }(e_{A_\times })-p)(f)
=\tau^*(\pi^{**}(\iota_{A_\times }(e_{A_\times })))(\pi^*(g))
=\pi^{**}(\iota_{A_\times }(e_{A_\times }))(\tau(\pi^*(g)))
$$
$$
=\pi^{**}(\iota_{A_\times }(e_{A_\times }))(g)
=\iota_{A_\times }(e_{A_\times })(\pi^*(g))
=\iota_{A_\times }(e_{A_\times })(f).
$$
Therefore $p(f)=0$ for all $f\in I^\perp$, i.e. $p\in I^{\perp\perp}$. Recall that $I^{\perp\perp}$ is the weak${}^*$ closure of $I$ in $A^{**}$, so we can choose a net $(e_\nu'')_{\nu\in N''}\subset I$ such that $(\iota_I(e_\nu''))_{\nu\in N''}$ converges to $p$ in weak${}^*$ topology. Clearly $(\iota_{A_\times }(e_{A_\times }-e_\nu''))_{\nu\in N''}$ converges to $\iota_{A_\times }(e_{A_\times })-p$ in the same topology. By [\cite{PosAndApproxIdinBanAlg}, lemma 1.1] there exists a net in the convex hull $\operatorname{conv}(\iota_{A_\times }(e_{A_\times }-e_\nu''))_{\nu\in N''}=\iota_{A_\times }(e_{A_\times })-\operatorname{conv}(\iota_{A_\times }(e_\nu''))_{\nu\in N''}$ that weak${}^*$ converges to $\iota_{A_\times }(e_{A_\times })-p$ with norm bound $\Vert \iota_{A_\times }(e_{A_\times })-p\Vert$. Denote this net as $(\iota_{A_\times }(e_{A_\times })-\iota_{A_\times }(e_\nu'))_{\nu\in N'}$, then $(\iota_{A_\times }(e_\nu'))_{\nu\in N'}$ weak${}^*$ converges to $p$. For any $a\in I$ and $f\in I^*$ we have
$$
\lim_{\nu}f(ae_\nu')
=\lim_{\nu}\iota_{A_\times }(e_\nu')(f\cdot a)
=p(f\cdot a)
=\iota_{A_\times }(e_{A_\times })(f\cdot a)-\tau^*(\pi^{**}(\iota_{A_\times }(e_{A_\times })))(f\cdot a)
$$
$$
=f(a)-\iota_{A_\times }(e_{A_\times })(\pi^*(\tau(f\cdot a)))
=f(a)-\pi^*(\tau(f)\cdot a)(e_{A_\times })
=f(a)-\tau(f)(\pi(a))
=f(a)
$$
hence $(e_\nu')_{\nu\in N'}$ is a weak right bounded approximate identity for $I$. By [\cite{AppIdAndFactorInBanAlg}, proposition 33.2] there is a net $(e_\nu)_{\nu\in N}\subset\operatorname{conv}(e_\nu')_{\nu\in N'}$ which is a right bounded approximate identity for $I$. For any $\nu\in N$ we have $e_{A_\times }-e_\nu\in\operatorname{conv}(e_{A_\times }-e_\nu')_{\nu\in N'}$, so taking into account the norm bound on $(\iota_{A_\times }(e_{A_\times }-e_\nu'))_{\nu\in N'}$ we get 
$$
\sup_{\nu\in N}\Vert e_{A_\times }-e_\nu\Vert
\leq\Vert \iota_{A_\times }(e_{A_\times })-p\Vert
\leq\Vert\tau^*(\pi^{**}(\iota_{A_\times }(e_{A_\times })))\Vert
\leq\Vert\tau^*\Vert\Vert\pi^{**}\Vert\Vert\iota_{A_\times }(e_{A_\times })\Vert=\Vert\tau\Vert
$$
Since $\tau$ has norm $\langle$~at most $1$ / at most $C$~$\rangle$ we get the desired bound. By construction, $(e_\nu)_{\nu\in N}$ is a right bounded approximate identity for $I$.

$ii)$$\implies$$ i)$ Denote $D=\sup_{\nu\in N}\Vert e_{A_\times }-e_\nu\Vert$. Let $\mathfrak{F}$ be the section filter on $N$ and let $\mathfrak{U}$ be an ultrafilter dominating $\mathfrak{F}$. For a fixed $f\in A_\times ^*$ and $a\in A_\times $ we have $|f(a-a e_\nu)|=|f(a(e_{A_\times }-e_\nu))|\leq\Vert f\Vert\Vert a\Vert\Vert e_{A_\times }-e_\nu\Vert\leq D\Vert f\Vert\Vert a\Vert$ i.e. $(f(a-ae_\nu))_{\nu\in N}$ is a bounded net of complex numbers. Therefore we have a well defined limit $\lim_{\mathfrak{U}}f(a-ae_\nu)$ along ultrafilter $\mathfrak{U}$. Since $(e_\nu)_{\nu\in N}$ is a right approximate identity for $I$ and $\mathfrak{U}$ contains section filter then for all $a\in I$ we have $\lim_{\mathfrak{U}}f(a-ae_\nu)=\lim_{\nu}f(a-ae_\nu)=0$. Therefore for each $f\in A_\times ^*$ we have well a defined map $\tau(f):A_\times /I\to \mathbb{C}:a+I\mapsto \lim_{\mathfrak{U}} f(a-ae_\nu)$. Clearly, this is a linear functional and from inequalities above we see its norm bounded by $D\Vert f\Vert$. Now it is routine to check that $\tau:A_\times ^*\to (A_\times /I)^*:f\mapsto \tau(f)$ is an $A$-morphism with norm $\langle$~at most $1$ / at most $C$~$\rangle$. For all $g\in(A_\times /I)^*$ and $a+I\in A_\times /I$ holds
$$
\tau(\pi^*(g))(a+I)
=\lim_{\mathfrak{U}}\pi^*(g)(a-ae_\nu)
=\lim_{\mathfrak{U}} g(\pi(a-ae_\nu))
=\lim_{\mathfrak{U}} g(a+I)
=g(a+I)
$$
i.e. $\tau:A_\times ^*\to (A_\times /I)^*$ is a retraction. The right $A$-module $A_\times ^*$ is $\langle$~metrically / $1$-topologically~$\rangle$ injective by proposition \ref{DualOfUnitalAlgIsMetTopInj}, hence its $\langle$~$1$-retract / $C$-retract~$\rangle$ $(A_\times /I)^*$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective. Proposition $\langle$~\ref{MetTopFlatCharac} / \ref{CTopFlatCharac}~$\rangle$ gives that the module $A_\times /I$ is $\langle$~metrically / $C$-topologically~$\rangle$ flat.
\end{proof}

It is worth to mention that every operator algebra $A$ (not necessary self adjoint) with contractive approximate identity has a contractive approximate identity $(e_\nu)_{\nu\in N}$ such that $\sup_{\nu\in N}\Vert e_{A_\#}-e_\nu\Vert\leq 1$ and even $\sup_{\nu\in N}\Vert e_{A_\#}-2e_\nu\Vert\leq 1$. Here $A_\#$ is a unitization of $A$ as operator algebra. For details see \cite{PosAndApproxIdinBanAlg}, \cite{BleContrAppIdInOpAlg}.

Again we shall compare our result on metric and topological flatness of cyclic modules with their relative counterpart. Helemeskii and Sheinberg showed [\cite{HelHomolBanTopAlg}, theorem VII.1.20] that a cyclic module is relatively flat if $I$ admits a right bounded approximate identity. In case when $I^\perp$ is complemented in $A_\times^*$ the converse is also true. In topological theory we don't need this assumption, so we have a criterion. Metric flatness of cyclic modules is a much stronger property due to specific restriction on the norm of approximate identity. As we shall see in the next section, it is so restrictive that it doesn't allow to construct any non zero annihilator metrically projective, injective or flat module over a non zero Banach algebra.

%----------------------------------------------------------------------------------------
%	The impact of Banach geometry
%----------------------------------------------------------------------------------------

\section{The impact of Banach geometry}
\label{SectionTheImpactOfBanachGeometry}


%----------------------------------------------------------------------------------------
%	Homologically trivial annihilator modules
%----------------------------------------------------------------------------------------

\subsection{Homologically trivial annihilator modules}
\label{SubSectionHomoligicallyTrivialAnnihilatorModules}

In this section we concentrate on the study of metrically and topologically projective, injective and flat annihilator modules. Unless otherwise stated, all Banach spaces in this section are regarded as annihilator modules. Note the obvious fact that we shall often use in this section: any bounded linear operator between annihilator $A$-modules is an $A$-morphism.

\begin{proposition}\label{AnnihCModIsRetAnnihMod} Let $X$ be a non zero annihilator $A$-module. Then $\mathbb{C}$ is a $1$-retract of $X$ in $A-\mathbf{mod}_1$.
\end{proposition}
\begin{proof} Take any $x_0\in X$ with $\Vert x_0\Vert=1$ and using Hahn-Banach theorem choose $f_0\in X^*$ such that $\Vert f_0\Vert=f_0(x_0)=1$. Consider contractive linear operators $\pi:X\to \mathbb{C}:x\mapsto f_0(x)$, $\sigma:\mathbb{C}\to X:z\mapsto zx_0$. It is easy to check that $\pi$ and $\sigma$ are contractive $A$-morphisms and what is more $\pi\sigma=1_\mathbb{C}$. In other words $\mathbb{C}$ is a $1$-retract of $X$ in $A-\mathbf{mod}_1$.
\end{proof}

Now it is time to recall that any Banach algebra $A$ can always be regarded as proper maximal ideal of $A_+$, and what is more $\mathbb{C}\isom{A-\mathbf{mod}_1} A_+/A$. If we regard $\mathbb{C}$ as a right annihilator $A$-module we also have $\mathbb{C}\isom{\mathbf{mod}_1-A}(A_+/A)^*$. 

\begin{proposition}\label{MetTopProjModCCharac} An annihilator $A$-module $\mathbb{C}$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective iff $\langle$~$A=\{0\}$ / $A$ has a right identity of norm at most $C-1$~$\rangle$.
\end{proposition}
\begin{proof} 
It is enough to study $\langle$~metric / $C$-topological~$\rangle$ projectivity of $A_+/A$. Since the natural quotient map $\pi:A_+\to A_+/A$ is a strict coisometry, then by proposition \ref{MetTopProjCycModCharac} $\langle$~metric / $C$-topological~$\rangle$ projectivity of $A_+/A$ is equivalent to existence of idempotent $p\in A$ such that $A=A_+p$ and $e_{A_+}-p$ has norm $\langle$~at most $1$ / at most $C$~$\rangle$. It remains to note that this norm bound holds iff $\langle$~$p=0$ and therefore $A=A_+p=\{0\}$ / $p$ has norm at most $C-1$~$\rangle$.
\end{proof}

\begin{proposition}\label{MetTopProjOfAnnihModCharac} Let $P$ be a non zero  annihilator $A$-module. Then the following are equivalent:

$i)$ $P$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective $A$-module;

$ii)$ $\langle$~$A=\{0\}$ / $A$ has a right identity of norm at most $C-1$~$\rangle$ and $P$ is a $\langle$~metrically / $C$-topologically~$\rangle$ projective Banach space. As the consequence $\langle$~$P\isom{\mathbf{Ban}_1}\ell_1(\Lambda)$ / $P\isom{\mathbf{Ban}}\ell_1(\Lambda)$~$\rangle$ for some set $\Lambda$.
\end{proposition}
\begin{proof} $i)$$\implies$$ ii)$ By propositions $\langle$~\ref{RetrMetTopProjIsMetTopProj} / \ref{RetrCTopProjIsCTopProj}~$\rangle$ and \ref{AnnihCModIsRetAnnihMod} the $A$-module $\mathbb{C}$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective as $1$-retract of $\langle$~metrically / $C$-topologically~$\rangle$ projective module $P$. Proposition \ref{MetTopProjModCCharac} gives that $\langle$~$A=\{0\}$ / $A$ has right identity of norm at most $C-1$~$\rangle$.  By corollary \ref{MetTopProjTensProdWithl1} the annihilator $A$-module $\mathbb{C}\projtens\ell_1(B_P)\isom{A-\mathbf{mod}_1}\ell_1(B_P)$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective. Consider strict coisometry $\pi:\ell_1(B_P)\to P$ well defined by equality $\pi(\delta_x)=x$. Since $P$ and $\ell_1(B_P)$ are annihilator modules, then $\pi$ is also an $A$-module map. Since $P$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective, then the $A$-morphism $\pi$ has a right inverse morphism $\sigma$ of norm  $\langle$~at most $1$ / at most $C-1$~$\rangle$. Therefore $P$ is a $\langle$~$1$-retract / $C$-retract~$\rangle$ of $\langle$~metrically / $1$-topologically~$\rangle$ projective Banach space $\ell_1(B_P)$. By proposition $\langle$~\ref{RetrMetTopProjIsMetTopProj} / \ref{RetrCTopProjIsCTopProj}~$\rangle$ the Banach space $P$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective. Now from $\langle$~[\cite{HelMetrFrQMod}, proposition 3.2] / results of \cite{KotheTopProjBanSp}~$\rangle$ we get that $P$ is isomorphic to $\ell_1(\Lambda)$ in $\langle$~$\mathbf{Ban}_1$ / $\mathbf{Ban}$~$\rangle$ for some set $\Lambda$. 

$ii)$$\implies$$ i)$ By proposition \ref{MetTopProjModCCharac} the annihilator $A$-module $\mathbb{C}$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective. Therefore by corollary \ref{MetTopProjTensProdWithl1} the annihilator $A$-module $\mathbb{C}\projtens\ell_1(\Lambda)\isom{A-\mathbf{mod}_1}\ell_1(\Lambda)$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective too.
\end{proof}

\begin{proposition}\label{MetTopInjModCCharac} A right annihilator $A$-module $\mathbb{C}$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective iff $\langle$~$A=\{0\}$ / $A$ has right $(C-1)$-bounded approximate identity~$\rangle$.
\end{proposition}
\begin{proof} Because of proposition $\langle$~\ref{MetTopFlatCharac} / \ref{CTopFlatCharac}~$\rangle$ it is enough to study $\langle$~metric / $C$-topological~$\rangle$ flatness of $A_+/A$. By proposition \ref{MetTopFlatCycModCharac} this is equivalent to existence of right bounded approximate identity $(e_\nu)_{\nu\in N}$ in $A$ with $\langle$~$\sup_{\nu\in N}\Vert e_{A_+}-e_\nu\Vert\leq 1$ / $\sup_{\nu\in N}\Vert e_{A_+}-e_\nu\Vert\leq C$~$\rangle$. It remains to note that the latter inequality holds iff $\langle$~iff $e_\nu=0$ and therefore $A=\{0\}$. / $(e_\nu)_{n\in N}$ is a right $C-1$-bounded approximate identity~$\rangle$.
\end{proof}

\begin{proposition}\label{MetTopInjOfAnnihModCharac} Let $J$ be a non zero right annihilator $A$-module. Then the following are equivalent:

$i)$ $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective $A$-module;

$ii)$ $\langle$~$A=\{0\}$ / $A$ has a right $(C-1)$-bounded approximate identity~$\rangle$ and $J$ is a $\langle$~metrically / $C$-topologically~$\rangle$ injective Banach space. $\langle$~As the consequence $J\isom{\mathbf{Ban}_1}C(K)$ for some Stonean space $K$ /~$\rangle$.
\end{proposition}
\begin{proof} $i)$$\implies$$ ii)$  By propositions $\langle$~\ref{RetrMetTopInjIsMetTopInj} / \ref{RetrCTopInjIsCTopInj}~$\rangle$ and \ref{AnnihCModIsRetAnnihMod} the $A$-module $\mathbb{C}$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective as $1$-retract of $\langle$~metrically / $C$-topologically~$\rangle$ injective module $J$. Proposition \ref{MetTopInjModCCharac} gives that $\langle$~$A=\{0\}$ / $A$ has a right $(C-1)$-bounded approximate identity~$\rangle$. By proposition \ref{MapsFroml1toMetTopInj} the annihilator $A$-module $\mathcal{B}(\ell_1(B_{J^*}),\mathbb{C})\isom{\mathbf{mod}_1-A}\ell_\infty(B_{J^*})$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective. Consider isometry $\rho:J\to\ell_\infty(B_{J^*})$ well defined by $\rho(x)(f)=f(x)$. Since $J$ and $\ell_\infty(B_{J^*})$ are annihilator modules, then $\rho$ is also an $A$-module map. Since $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective, then the $A$-morphism $\rho$ has a left inverse morphism $\tau$ with norm $\langle$~at most $1$ / at most $C$~$\rangle$. Therefore $J$ is $\langle$~$1$-retract / $C$-retract~$\rangle$ of $\langle$~metrically / $1$-topologically~$\rangle$ injective Banach space $\ell_\infty(B_{J^*})$. By proposition $\langle$~\ref{RetrMetTopInjIsMetTopInj} / \ref{RetrCTopInjIsCTopInj}~$\rangle$ the Banach space $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective. $\langle$~From  [\cite{LaceyIsomThOfClassicBanSp}, theorem 3.11.6] the Banach space $J$ is isometrically isomorphic to $C(K)$ for some Stonean space $K$. /~$\rangle$ 

$ii)$$\implies$$ i)$ By proposition \ref{MetTopInjModCCharac} the annihilator $A$-module $\mathbb{C}$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective. By proposition \ref{MapsFroml1toMetTopInj} the annihilator $A$-module $\mathcal{B}(\ell_1(B_{J^*}),\mathbb{C})\isom{\mathbf{mod}_1-A}\ell_\infty(B_{J^*})$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective too. Since $J$ is a $\langle$~metrically / $C$-topologically~$\rangle$ injective Banach space and there an isometric embedding $\rho:J\to \ell_\infty(B_{J^*})$, then as Banach space $J$ is a $\langle$~$1$-retract / $C$-retract~$\rangle$ of $\ell_\infty(B_{J^*})$. Recall, that $J$ and $\ell_\infty(B_{J^*})$ are annihilator modules, so in fact we have a retraction in $\langle$~$\mathbf{mod}_1-A$ / $\mathbf{mod}-A$~$\rangle$. By proposition $\langle$~\ref{RetrMetTopInjIsMetTopInj} / \ref{RetrCTopInjIsCTopInj}~$\rangle$ the $A$-module $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective.
\end{proof}

\begin{proposition}\label{MetTopFlatAnnihModCharac} Let $F$ be a non zero annihilator $A$-module. Then the following are equivalent:

$i)$ $F$ is $\langle$~metrically / $C$-topologically~$\rangle$ flat $A$-module;

$ii)$ $\langle$~$A=\{0\}$ / $A$ has a right $(C-1)$-bounded approximate identity~$\rangle$ and $F$ is a $\langle$~metrically / $C$-topologically~$\rangle$ flat Banach space, that is $\langle$~$F\isom{\mathbf{Ban}_1}L_1(\Omega,\mu)$ for some measure space $(\Omega, \Sigma, \mu)$ / $F$ is an $\mathscr{L}_{1,C}^g$-space~$\rangle$.
\end{proposition}
\begin{proof} By $\langle$~[\cite{GrothMetrProjFlatBanSp}, theorem 1] / [\cite{DefFloTensNorOpId}, corollary 23.5(1)]~$\rangle$ the Banach space $F$ is $\langle$~metrically / $C$-topologically~$\rangle$ flat iff $\langle$~$F\isom{\mathbf{Ban}_1}L_1(\Omega,\mu)$ for some measure space $(\Omega, \Sigma, \mu)$ / $F$ is an $\mathscr{L}_{1,C}^g$-space~$\rangle$. Now the equivalence follows from propositions \ref{MetTopInjOfAnnihModCharac} and \ref{MetTopFlatCharac}.
\end{proof}

We obliged to compare these results with similar ones in relative theory. From $\langle$~[\cite{RamsHomPropSemgroupAlg}, proposition 2.1.7] / [\cite{RamsHomPropSemgroupAlg}, proposition 2.1.10]~$\rangle$ we know that an annihilator $A$-module over Banach algebra $A$ is relatively $\langle$~projective / flat~$\rangle$ iff $A$ has $\langle$~a right identity / a right bounded approximate identity~$\rangle$.   
In metric and topological theory, in comparison with relative one, homological triviality of annihilator modules puts restrictions not only on the algebra itself but on the geometry of the module too. These geometric restrictions forbid existence of certain homologically excellent algebras. One of the most important properties of relatively $\langle$~contractible / amenable~$\rangle$ Banach algebra is $\langle$~projectivity / flatness~$\rangle$ of all (and in particular of all annihilator) left Banach modules over it. In a sharp contrast in metric and topological theories such algebras can't exist.

\begin{proposition} There is no Banach algebra $A$ such that all $A$-modules are  $\langle$~metrically / topologically~$\rangle$ flat. A fortiori, there is no such Banach algebras that all $A$-modules are $\langle$~metrically / topologically~$\rangle$ projective.
\end{proposition}
\begin{proof} Consider any infinite dimensional $\mathscr{L}_\infty^g$-space $X$ (say $\ell_\infty(\mathbb{N})$) as an annihilator $A$-module. From remark right after [\cite{DefFloTensNorOpId}, corollary 23.3] we know that $X$ is not an $\mathscr{L}_1^g$-space. Therefore by proposition \ref{MetTopFlatAnnihModCharac} the $A$-module $X$ is not topologically flat. By proposition \ref{MetFlatIsTopFlatAndTopFlatIsRelFlat} it is not metrically flat. Now from proposition \ref{MetTopProjIsMetTopFlat} we see that $X$ is neither metrically nor topologically projective.
\end{proof}

%----------------------------------------------------------------------------------------
%	Homologically trivial modules over Banach algebras with specific geometry
%----------------------------------------------------------------------------------------

\subsection{Homologically trivial modules over Banach algebras with specific geometry}
\label{SubSectionHomologicallyTrivialModulesOverBanachAlgebrasWithSpecificGeometry}

The purpose of this section is to convince our reader that homologically trivial modules over certain Banach algebras have similar geometric structure of those algebras. For the case of metric theory the following proposition was proved by Graven in \cite{GravInjProjBanMod}.

\begin{proposition}\label{TopProjInjFlatModOverL1Charac} Let $A$ be a Banach algebra which is as Banach space isometrically isomorphic to $L_1(\Theta,\nu)$ for some measure space $(\Theta,\Sigma,\nu)$. Then

$i)$ if $P$ is a $\langle$~metrically / topologically~$\rangle$ projective $A$-module, then $P$ is $\langle$~an $L_1$-space / complemented in some $L_1$-space~$\rangle$.

$ii)$ if $J$ is a $\langle$~metrically / topologically~$\rangle$ injective $A$-module, then  $J$ is a $\langle$~$C(K)$-space for some Stonean space $K$ / topologically injective Banach space~$\rangle$.

$iii)$ if $F$ is a $\langle$~metrically / topologically~$\rangle$ flat $A$-module, then $F$ is an $\langle$~$L_1$-space / $\mathscr{L}_1^g$-space~$\rangle$.
\end{proposition}
\begin{proof} 

Denote by $(\Theta',\Sigma',\nu')$ the measure space $(\Theta,\Sigma,\nu)$ with singleton atom adjoined, then $A_+\isom{\mathbf{Ban}_1} L_1(\Theta',\nu')$.

$i)$ Since $P$ is a $\langle$~metrically / topologically~$\rangle$ projective $A$-module, then by proposition \ref{MetTopProjModViaCanonicMorph} it is a retract of $A_+\projtens \ell_1(B_P)$ in $\langle$~$A-\mathbf{mod}_1$ / $A-\mathbf{mod}$~$\rangle$. Let $\mu_c$ be the counting measure on $B_P$, then by Grothendieck's theorem [\cite{HelLectAndExOnFuncAn}, theorem 2.7.5]
$$
A_+\projtens\ell_1(B_P)
\isom{\mathbf{Ban}_1}L_1(\Theta',\nu')\projtens L_1(B_P,\mu_c)
\isom{\mathbf{Ban}_1}L_1(\Theta'\times B_P,\nu'\times \mu_c)
$$
Therefore $P$ is $\langle$~$1$-complemented / complemented~$\rangle$ in some $L_1$-space. It remains to recall that any $1$-complemented subspace of $L_1$-space is again an $L_1$-space [\cite{LaceyIsomThOfClassicBanSp}, theorem 6.17.3].

$ii)$ Since $J$ is $\langle$~metrically / topologically~$\rangle$ injective $A$-module, then by proposition \ref{MetTopInjModViaCanonicMorph} it is a retract of $\mathcal{B}(A_+,\ell_\infty(B_{J^*}))$ in $\langle$~$\mathbf{mod}_1-A$ / $\mathbf{mod}-A$~$\rangle$. Let $\mu_c$ be the counting measure on $B_{J^*}$, then by Grothendieck's theorem [\cite{HelLectAndExOnFuncAn}, theorem 2.7.5]
$$
\mathcal{B}(A_+,\ell_\infty(B_{J^*}))
\isom{\mathbf{Ban}_1}(A_+\projtens \ell_1(B_{J^*}))^*
\isom{\mathbf{Ban}_1}(L_1(\Theta',\nu')\projtens L_1(B_P,\mu_c))^*
$$
$$
\isom{\mathbf{Ban}_1}L_1(\Theta'\times B_P,\nu'\times \mu_c)^*
\isom{\mathbf{Ban}_1}L_\infty(\Theta'\times B_P,\nu'\times \mu_c)
$$
Therefore $J$ is $\langle$~$1$-complemented / complemented~$\rangle$ in some $L_\infty$-space. Since $L_\infty$-space is $\langle$~metrically / topologically~$\rangle$ injective Banach space, then so does $J$. It remains to recall that every metrically injective Banach space is a $C(K)$-space for some Stonean space $K$ [\cite{LaceyIsomThOfClassicBanSp}, theorem 3.11.6].

$iii)$  By $\langle$~[\cite{GrothMetrProjFlatBanSp}, theorem 1] / remark after [\cite{DefFloTensNorOpId}, corollary 23.5(1)]~$\rangle$ the Banach space $F^*$ is $\langle$~metrically / topologically~$\rangle$ injective iff $F$ is an $\langle$~$L_1$-space / $\mathscr{L}_1^g$-space~$\rangle$. Now the implication follows from paragraph $ii)$ and proposition \ref{MetTopFlatCharac}.
\end{proof}

\begin{proposition}\label{TopProjInjFlatModOverMthscrL1SpCharac} Let $A$ be a Banach algebra which is topologically isomorphic as Banach space to some $\mathscr{L}_1^g$-space. Then any topologically $\langle$~projective / injective / flat~$\rangle$ $A$-module is an $\langle$~$\mathscr{L}_1^g$-space / $\mathscr{L}_\infty^g$-space / $\mathscr{L}_1^g$-space~$\rangle$.
\end{proposition}
\begin{proof} If $A$ is an $\mathscr{L}_1^g$-space, then so does $A_+$. 

Let $P$ be a topologically projective $A$-module. Then by proposition \ref{MetTopProjModViaCanonicMorph} it is a retract of $A_+\projtens \ell_1(B_P)$ in $A-\mathbf{mod}$ and a fortiori in $\mathbf{Ban}$. Since $\ell_1(B_P)$ is an $\mathscr{L}_1^g$-space, then so does $A_+\projtens\ell_1(B_P)$ as projective tensor product of $\mathscr{L}_1^g$-spaces [\cite{DefFloTensNorOpId}, exercise 23.17(c)]. Therefore $P$ is an $\mathscr{L}_1^g$-space as complemented subspace of $\mathscr{L}_1^g$-space [\cite{DefFloTensNorOpId}, corollary 23.2.1(2)].

Let $J$ be a topologically injective $A$-module, then by proposition \ref{MetTopInjModViaCanonicMorph} it is a retract of $\mathcal{B}(A_+,\ell_\infty(B_{J^*}))\isom{\mathbf{mod}_1-A}(A_+\projtens\ell_1(B_{J^*}))^*$ in $\mathbf{mod}-A$ and a fortiori in $\mathbf{Ban}$. As we showed in the previous paragraph $A_+\projtens\ell_1(B_{J^*})$ is an $\mathscr{L}_1^g$-space, therefore its dual $\mathcal{B}(A_+,\ell_\infty(B_{J^*}))$ is an $\mathscr{L}_\infty^g$-space [\cite{DefFloTensNorOpId}, corollary 23.2.1(1)]. It remains to recall that any complemented subspace of $\mathscr{L}_\infty^g$-space is again an $\mathscr{L}_\infty^g$-space [\cite{DefFloTensNorOpId}, corollary 23.2.1(2)].

Finally, let $F$ be a topologically flat $A$-module, then $F^*$ is topologically injective $A$-module by proposition \ref{MetTopFlatCharac}. From previous paragraph it follows that $F^*$ is an $\mathscr{L}_\infty^g$-space. By [\cite{DefFloTensNorOpId}, corollary 23.5(1)] we get that $F$ is an $\mathscr{L}_1^g$-space.
\end{proof}

We proceed to the discussion of the Dunford-Pettis property for homologically trivial modules.   

\begin{proposition}\label{C0SumOfL1SpHaveDPP} Let $(\Omega, \Sigma, \mu)$ be a measure spaces and $\Lambda$ be an arbitrary set. Then the Banach space $\bigoplus_0\{L_1(\Omega,\mu):\lambda\in\Lambda\}$ and all its duals has the Dunford-Pettis property.
In particular, $\bigoplus_1\{L_\infty(\Omega,\mu):\lambda\in\Lambda\}$ and $\bigoplus_\infty\{L_1(\Omega,\mu):\lambda\in\Lambda\}$ have this property.
\end{proposition}
\begin{proof} Consider one point compactification $\alpha\Lambda:=\Lambda\cup\{\Lambda\}$ of the set $\Lambda$ with discrete topology. From [\cite{BourgOnTheDPP}, corollary 7] we know that $C(\alpha\Lambda, L_1(\Omega, \mu))$ and all its duals have the Dunford-Pettis property. Since $c_0(\Lambda)$ is complemented in $C(\alpha\Lambda)$ via projection $P:C(\alpha\Lambda)\to C(\alpha\Lambda):x\mapsto x(\lambda)-x(\{\Lambda\})$, then $E:=c_0(\Lambda, L_1(\Omega,\mu))$ is complemented in $C(\alpha\Lambda, L_1(\Omega, \mu))$. The same statement holds for any $n$-th dual of $E$, because we can take $n$-th adjoint of $P$ in the role of projection. Now it remains to note that $E=\bigoplus_0\{L_1(\Omega,\mu):\lambda\in\Lambda\}$ and that the Dunford-Pettis property is inherited by complemented subspaces [\cite{FabHabBanSpTh}, proposition 13.44]. 

As the consequence of previous paragraph the Banach spaces $E^*\isom{\mathbf{Ban}_1}\bigoplus_1\{L_
\infty(\Omega,\mu):\lambda\in\Lambda\}$ and $E^{**}\isom{\mathbf{Ban}_1}\bigoplus_\infty\{L_1(\Omega,\mu)^{**}:\lambda\in\Lambda\}$ have the Dunford-Pettis property. From [\cite{DefFloTensNorOpId}, proposition B10] we know that any $L_1$-space is contractively complemented in its second dual. By $Q$ we denote the respective projection. Therefore the Banach space $\bigoplus_\infty\{L_1(\Omega,\mu):\lambda\in\Lambda\}$ is contractively complemented in $E^{**}$ via projection $\bigoplus_\infty \{Q:\lambda\in\Lambda\}$. Since $E^{**}$ has the Dunford-Pettis property, then by [\cite{FabHabBanSpTh}, proposition 13.44] so does its complemented subspace $\bigoplus_\infty\{L_1(\Omega,\mu):\lambda\in\Lambda\}$.
\end{proof}

\begin{proposition}\label{ProdOfL1SpHaveDPP} Let $\{(\Omega_\lambda,\Sigma_\lambda,\mu_\lambda):\lambda\in\Lambda\}$ be a family of measure spaces. Then $\bigoplus_0\{L_1(\Omega_\lambda, \mu_\lambda):\lambda\in\Lambda\}$, $\bigoplus_1\{L_\infty(\Omega_\lambda, \mu_\lambda):\lambda\in\Lambda\}$ and $\bigoplus_\infty\{L_1(\Omega_\lambda,\mu_\lambda):\lambda\in\Lambda\}$ have the Dunford-Pettis property.
\end{proposition}
\begin{proof} Let $(\Omega, \Sigma, \mu)$ be a direct sum of $\{(\Omega_\lambda,\Sigma_\lambda,\mu_\lambda):\lambda\in\Lambda\}$. By construction each Banach space $L_1(\Omega_\lambda,\mu_\lambda)$ for $\lambda\in\Lambda$ is $1$-complemented in $L_1(\Omega, \mu)$. Therefore, their $\bigoplus_0$-, $\bigoplus_1$- and $\bigoplus_\infty$-sums are contractively complemented in $\bigoplus_0\{L_1(\Omega, \mu):\lambda\in\Lambda\}$, $\bigoplus_1\{L_\infty(\Omega, \mu):\lambda\in\Lambda\}$ and $\bigoplus_\infty\{L_1(\Omega,\mu):\lambda\in\Lambda\}$ respectively. It remains to combine proposition \ref{C0SumOfL1SpHaveDPP} and the fact that the Dunford-Pettis property is preserved by complemented subspaces [\cite{FabHabBanSpTh}, proposition 13.44].
\end{proof}

\begin{proposition}\label{ProdOfDualsOfMthscrLInftySpHaveDPP} Let $E$ be an $\mathscr{L}_\infty^g$-space and $\Lambda$ be an arbitrary set. Then $\bigoplus_\infty\{E^*:\lambda\in\Lambda\}$ has the Dunford-Pettis property.
\end{proposition}
\begin{proof} Since $E$ is an $\mathscr{L}_\infty^g$-space, then $E^*$ is a $\mathscr{L}_{1}^g$-space [\cite{DefFloTensNorOpId}, corollary 23.2.1(1)]. Then from [\cite{DefFloTensNorOpId}, corollary 23.2.1(3)] it follows that $E^{***}$ is a retract of $L_1$-space. Recall that $E^*$ is complemented in $E^{***}$ via Dixmier projection, so $E^*$ is complemented in some $L_1$-space too. Thus we have a bounded linear projection $P:L_1(\Omega,\mu)\to L_1(\Omega,\mu)$ with image topologically isomorphic to $E$. In this case $\bigoplus_\infty\{ E^*:\lambda\in\Lambda\}$ is complemented in $\bigoplus_\infty\{ L_1(\Omega,\mu):\lambda\in\Lambda\}$ via projection $\bigoplus_\infty\{P:\lambda\in\Lambda\}$. The space $\bigoplus_\infty\{ L_1(\Omega,\mu):\lambda\in\Lambda\}$ has the Dunford-Pettis property by proposition \ref{ProdOfL1SpHaveDPP}. By proposition 13.44 in \cite{FabHabBanSpTh} so does $\bigoplus_\infty\{ E^*:\lambda\in\Lambda\}$ as complemented subspace of $\bigoplus_\infty\{ L_1(\Omega,\mu):\lambda\in\Lambda\}$.
\end{proof}

\begin{proposition}\label{MthscrL1LInftyHaveDPP} Any $\langle$~$\mathscr{L}_1^g$-space / $\mathscr{L}_\infty^g$-space~$\rangle$ admits the Dunford-Pettis property.
\end{proposition}
\begin{proof} Assume $E$ is an $\langle$~$\mathscr{L}_1^g$-space / $\mathscr{L}_\infty^g$-space~$\rangle$. Then $E^{**}$ is complemented in some $\langle$~$L_1$-space / $L_\infty$-space~$\rangle$ [\cite{DefFloTensNorOpId}, corollary 23.2.1(3)]. Since any $\langle$~$L_1$-space / $L_\infty$-space~$\rangle$ admits the Dunford-Pettis property \cite{GrothApllFaiblCompSpCK}, then so does $E^{**}$ as complemented subspace [\cite{FabHabBanSpTh}, proposition 13.44]. It remains to recall that a Banach space have the Dunford-Pettis property whenever so does its dual.
\end{proof}

\begin{theorem}\label{TopProjInjFlatModOverMthscrL1OrLInftySpHaveDPP} Let $A$ be a Banach algebra which is an $\mathscr{L}_1^g$-space or $\mathscr{L}_\infty^g$-space as Banach space. Then any topologically projective, injective or flat $A$-module has the Dunford-Pettis property.
\end{theorem}
\begin{proof} If $A$ is an $\mathscr{L}_1^g$-space, we just need to combine propositions \ref{MthscrL1LInftyHaveDPP} and \ref{TopProjInjFlatModOverMthscrL1SpCharac}. 

Assume $A$ is an $\mathscr{L}_\infty^g$-space, then so does $A_+$. Let $J$ be a topologically injective $A$-module, then by proposition \ref{MetTopInjModViaCanonicMorph} it is a retract of 
$$
\mathcal{B}(A_+,\ell_\infty(B_{J^*}))\isom{\mathbf{mod}_1-A}(A_+\projtens\ell_1(B_{J^*}))^*\isom{\mathbf{mod}_1-A}
\left(\bigoplus\nolimits_1\{ A_+:\lambda\in B_{J^*}\}\right)^*\isom{\mathbf{mod}_1-A}
$$
$$
\bigoplus\nolimits_\infty\{ A_+^*:\lambda\in B_{J^*}\}
$$ 
in $\mathbf{mod}-A$ and a fortiori in $\mathbf{Ban}$. By proposition \ref{ProdOfDualsOfMthscrLInftySpHaveDPP} this space has the Dunford-Pettis property. As $J$ is its retract, then $J$ also has this property [\cite{FabHabBanSpTh}, proposition 13.44]. 

If $F$ is a topologically flat $A$-module, then $F^*$ is a topologically injective $A$-module by proposition \ref{MetTopFlatCharac}. By previous paragraph $F^*$ has the Dunford-Pettis property and so does $F$.

If $P$ is a topologically projective $A$-module, it is also topologically flat by proposition \ref{MetTopProjIsMetTopFlat}. From previous paragraph it follows that $P$ has the Dunford-Pettis property.
\end{proof}

\begin{corollary}\label{NoInfDimRefMetTopProjInjFlatModOverMthscrL1OrLInfty} Let $A$ be a Banach algebra which $\mathscr{L}_1^g$-space or $\mathscr{L}_\infty^g$-space as Banach space. Then there is no topologically projective, injective or flat infinite dimensional reflexive $A$-modules. A fortiori there is no metrically projective, injective or flat infinite dimensional reflexive $A$-modules.
\end{corollary}
\begin{proof} From theorem \ref{TopProjInjFlatModOverMthscrL1OrLInftySpHaveDPP} we know that any topologically injective $A$-module has the Dunford-Pettis property. On the other hand there is no infinite dimensional reflexive Banach spaces with the Dunford-Pettis property. Thus we get the desired result regarding topological injectivity. Since dual of reflexive module is reflexive, from proposition \ref{MetTopFlatCharac} we get the result for topological flatness. It remains to recall that by proposition \ref{MetTopProjIsMetTopFlat}  every topologically projective module is topologically flat. To prove the last claim note that metric $\langle$~projectivity / injectivity / flatness~$\rangle$ implies topological $\langle$~projectivity / injectivity / flatness~$\rangle$ by proposition $\langle$~\ref{MetProjIsTopProjAndTopProjIsRelProj} / \ref{MetInjIsTopInjAndTopInjIsRelInj} / \ref{MetFlatIsTopFlatAndTopFlatIsRelFlat}~$\rangle$.
\end{proof}

Note that in relative theory there are examples of infinite dimensional relatively projective injective and flat reflexive modules over Banach algebras that are $\mathscr{L}_1^g$- or $\mathscr{L}_\infty^g$-spaces. Here are two examples. The first one is about convolution algebra $L_1(G)$ on a locally compact group $G$ with Haar measure. It is an $\mathscr{L}_1^g$-space. In [\cite{DalPolHomolPropGrAlg}, \S6] and \cite{RachInjModAndAmenGr} it was proved that for $1<p<+\infty$ the $L_1(G)$-module $L_p(G)$ is relatively $\langle$~projective / injective / flat~$\rangle$ iff $G$ is $\langle$~compact / amenable / amenable~$\rangle$. Note that any compact group is amenable [\cite{PierAmenLCA}, proposition 3.12.1], so in case $G$ is compact $L_p(G)$ is relatively projective injective and flat for all $1<p<+\infty$.  The second example is about $\mathscr{L}_\infty^g$-spaces $c_0(\Lambda)$ and $\ell_\infty(\Lambda)$ for an infinite set $\Lambda$. In proposition \ref{c0AndlInftyModsRelTh} we shall show that $\ell_p(\Lambda)$ for $1<p<\infty$ is relatively projective injective and flat as $c_0(\Lambda)$- or $\ell_\infty(\Lambda)$-module. 

We finalize this lengthy section by short remark on the l.u.st. property of topologically projective, injective and flat modules. 

\begin{proposition} Let $A$ be a Banach algebra which as Banach space has the l.u.st. property. Then any topologically projective, injective or flat $A$-module has the l.u.st. property.
\end{proposition}
\begin{proof} 

If $J$ is topologically injective $A$-module, then by proposition \ref{MetTopInjModViaCanonicMorph} it is a retract of $\mathcal{B}(A_+,\ell_\infty(B_{J^*}))\isom{\mathbf{mod}_1-A}\bigoplus_\infty\{ A_+^*:\lambda\in B_{J^*}\}$ in $\mathbf{mod}-A$ and a fortiori in $\mathbf{Ban}$. If $A$ has the l.u.st. property, then $A^{**}$ is complemented in some Banach lattice $E$ [\cite{DiestAbsSumOps}, theorem 17.5]. As the consequence $A_+^{***}$ is complemented in the Banach lattice $F:=\left(E\bigoplus_1\mathbb{C}\right)^*$ via some bounded projection $P:F\to F$. Thus $\bigoplus_\infty\{A_+^{***}:\lambda\in B_{J^*}\}$ is complemented in the Banach lattice $\bigoplus_\infty\{F:\lambda\in B_{J^*}\}$ via projection $\bigoplus_\infty\{ P:\lambda\in B_{J^*}\}$. Any Banach lattice has the l.u.st. property [\cite{DiestAbsSumOps}, theorem 17.1]. This property is inherited by complemented subspaces, so $\bigoplus_\infty\{A_+^{***}:\lambda\in B_{J^*}\}$ has the l.u.st. property too. Note that $A_+^*$ is contractively complemented in $A_+^{***}$ by Dixmier projection $Q$, therefore $\bigoplus_\infty\{A_+^*:\lambda\in B_{J^*}\}$ is complemented in $\bigoplus_\infty\{A_+^{***}:\lambda\in B_{J^*}\}$ via contractive projection $\bigoplus_\infty\{Q:\lambda\in B_{J^*}\}$. Since the latter space has the l.u.st. property, then so does its retract $\bigoplus_\infty\{A_+^*:\lambda\in B_{J^*}\}$. Finally $J$ is a retract of the $\bigoplus_\infty\{A_+^*:\lambda\in B_{J^*}\}$, therefore also has this property.

If $F$ is topologically flat $A$-module, then $F^*$ is topologically injective by proposition \ref{MetTopFlatCharac}. By previous paragraph $F^*$ has the l.u.st. property. Corollary 17.6 from \cite{DiestAbsSumOps} gives that $F$ has this property too.

If $P$ is topologically projective $A$-module, it is topologically flat by proposition \ref{MetTopProjIsMetTopFlat}. So $P$ has the l.u.st. property by previous paragraph.
\end{proof}

%----------------------------------------------------------------------------------------
%	Further properties of projective injective and flat modules
%----------------------------------------------------------------------------------------

\section{Further properties of projective injective and flat modules}
\label{SectionFurtherPropertiesOfProjectiveInjectiveAndFlatModules}

%----------------------------------------------------------------------------------------
%	Homological triviality of modules under change of algebra
%----------------------------------------------------------------------------------------

\subsection{Homological triviality of modules under change of algebra}
\label{SubSectionHomologicalTrivialityOfModulesUnderChangeOfAlgebra}

The following three propositions are metric and topological versions of propositions 2.3.2, 2.3.3 and 2.3.4 in \cite{RamsHomPropSemgroupAlg}.

\begin{proposition}\label{MorphCoincide} Let $X$ and $Y$ be $\langle$~left / right~$\rangle$ $A$-modules. Assume one of the following holds

$i)$ $I$ is a $\langle$~left / right~$\rangle$ ideal of $A$ and $X$ is an essential $I$-module;

$ii)$ $I$ is a $\langle$~right / left~$\rangle$ ideal of $A$ and $Y$ is a faithful $I$-module. 

Then $\langle$~${}_A\mathcal{B}(X,Y)={}_I\mathcal{B}(X,Y)$ / $\mathcal{B}_A(X,Y)=\mathcal{B}_I(X,Y)$~$\rangle$.
\end{proposition}
\begin{proof} We shall prove both statements only for left modules, since their right counterparts are proved with minimal modifications. Fix $\phi\in {}_I\mathcal{B}(X,Y)$.

$i)$ Take $x\in I\cdot X$, then $x=a'\cdot x'$ for some $a'\in I$, $x'\in X$. For any $a\in A$ we have $\phi(a\cdot x)=\phi(aa'\cdot x')=aa'\cdot\phi(x')=a\cdot\phi(a'\cdot x')=a\cdot\phi(x)$. Therefore $\phi(a\cdot x)=a\cdot\phi(x)$ for all $a\in A$ and $x\in \operatorname{cl}_X(IX)=X$. Hence $\phi\in {}_A\mathcal{B}(X,Y)$.

$ii)$ For any $a\in I$ and $a'\in A$, $x\in X$ we have $a\cdot(\phi(a'\cdot x)-a'\cdot\phi(x))=\phi(aa'\cdot x)-aa'\cdot\phi(x)=0$. Since $Y$ is faithful $I$-module we have $\phi(a'\cdot x)=a'\cdot \phi(x)$ for all $x\in X$, $a'\in A$. Hence $\phi\in{}_A\mathcal{B}(X,Y)$.

In both cases we proved that $\phi\in{}_A\mathcal{B}(X,Y)$ for any $\phi\in{}_I\mathcal{B}(X,Y)$, therefore ${}_I\mathcal{B}(X,Y)\subset {}_A\mathcal{B}(X,Y)$. The reverse inclusion is obvious.
\end{proof}

\begin{proposition}\label{MetTopProjUnderChangeOfAlg} Let $I$ be a closed subalgebra of $A$ and $P$ be an $A$-module which is essential as $I$-module. Then

$i)$ if $I$ is a left ideal of $A$ and $P$ is $\langle$~metrically / $C$-topologically~$\rangle$  projective $I$-module, then $P$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective $A$-module;

$ii)$ if $I$ is a $\langle$~$1$-complemented / $c$-complemented~$\rangle$ right ideal of $A$ and $P$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective $A$-module, then $P$ is $\langle$~metrically / $cC$-topologically~$\rangle$ projective $I$-module.
\end{proposition}
\begin{proof} By $\widetilde{\pi}_P: I\projtens \ell_1(B_P)\to P$ and $\pi_P:A\projtens \ell_1(B_P)\to P$ we will denote the standard epimorphisms.

$i)$ By proposition \ref{NonDegenMetTopProjCharac} the morphism $\widetilde{\pi}_P$ has a right inverse morphism in $\langle$~$I-\mathbf{mod}_1$ / $I-\mathbf{mod}$~$\rangle$, say $\widetilde{\sigma}$ of norm $\langle$~at most $1$ / at most $C$~$\rangle$. Let $i:I\to A$ be the natural embedding, then consider $\langle$~contractive / bounded~$\rangle$ $I$-morphism $\sigma=(i\projtens 1_{\ell_1(B_P)})\widetilde{\sigma}$. By paragraph $i)$ of proposition \ref{MorphCoincide} we have that $\sigma$ is an $A$-morphism. Clearly, $\sigma$ has norm $\langle$~at most $1$ / at most $C$~$\rangle$. For $\pi_P:A\projtens \ell_1(B_P)\to P$ we obviously have $\pi_P(i\projtens 1_{\ell_1(B_P)})=\widetilde{\pi}_P$, hence $\pi_P\sigma=\pi_P(i\projtens 1_{\ell_1(B_P)})\widetilde{\sigma}=\widetilde{\pi}_P\widetilde{\sigma}=1_P$. Thus $\pi_P$ is a $\langle$~$1$-retraction / $C$-retraction~$\rangle$ in $\langle$~$A-\mathbf{mod}_1$ / $A-\mathbf{mod}$~$\rangle$. So by proposition \ref{NonDegenMetTopProjCharac} the $A$-module $P$ is $\langle$~metrically / $C$-topologically~$\rangle$ projective.

$ii)$ Since $P$ is an essential $I$-module it is a fortiori an essential $A$-module. By proposition \ref{NonDegenMetTopProjCharac} the morphism $\pi_P$ has a right inverse morphism $\sigma$ in $\langle$~$A-\mathbf{mod}_1$ / $A-\mathbf{mod}$~$\rangle$ with norm $\langle$~at most $1$ / at most $C$~$\rangle$. Obviously $\sigma$ is a right inverse for $\pi_P$ in $\langle$~$I-\mathbf{mod}_1$ / $I-\mathbf{mod}$~$\rangle$ too. By $i:I\to A$ we denote the natural embedding, and by $r:A\to I$ the $\langle$~contractive / bounded~$\rangle$ left inverse. By assumption $\Vert r\Vert\leq c$. Consider $\langle$~contractive / bounded~$\rangle$ linear operator $\widetilde{\sigma}=(r\projtens 1_{\ell_1(B_P)})\sigma$. Clearly, its norm is $\langle$~at most $1$ / at most $cC$~$\rangle$. Since $I$ is a right ideal of $A$ and $P$ is an essential $I$-module then $\sigma(P)=\sigma(\operatorname{cl}_P(IP))=\operatorname{cl}_{A\projtens \ell_1(B_P)}(I\cdot (A\projtens \ell_1(B_P)))=I\projtens \ell_1(B_P)$, so $\sigma=(ir\projtens 1_{\ell_1(B_P)})\sigma$. Even more, since $\sigma(P)\subset I\projtens\ell_1(B_P)$ and $r|_I=1_I$, then $\sigma$ is an $I$-morphism. Clearly, $\pi_P(i\projtens 1_{\ell_1(B_P)})=\widetilde{\pi}_P$, so $\widetilde{\pi}_P\widetilde{\sigma}=\pi_P(i\projtens 1_{\ell_1(B_P)})(r\projtens 1_{\ell_1(B_P)})\sigma=\pi_P(ir\projtens 1_{\ell_1(B_P)})\sigma=\pi_P\sigma=1_P$. Thus $\widetilde{\pi}_P$ is a $\langle$~$1$-retraction / $cC$-retraction~$\rangle$ in $\langle$~$I-\mathbf{mod}_1$ / $I-\mathbf{mod}$~$\rangle$, so by proposition \ref{NonDegenMetTopProjCharac} the $I$-module $P$ is $\langle$~metrically / $cC$-topologically~$\rangle$ projective.
\end{proof}

\begin{proposition}\label{MetTopInjUnderChangeOfAlg} Let $I$ be a closed subalgebra of $A$ and $J$ be a right $A$-module which is faithful as $I$-module. Then

$i)$ if $I$ is a left ideal of $A$ and $J$ is $\langle$~metrically / $C$-topologically~$\rangle$  injective $I$-module, then $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective $A$-module;

$ii)$ if $I$ is a $\langle$~$1$-complemented / $c$-complemented~$\rangle$ right ideal of $A$ and $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective $A$-module, then $J$ is $\langle$~metrically / $cC$-topologically~$\rangle$ injective $I$-module.
\end{proposition}
\begin{proof} By $\widetilde{\rho}_J:J\to\mathcal{B}(I,\ell_\infty(B_{J^*}))$ and $\rho_J:J\to\mathcal{B}(A,\ell_\infty(B_{J^*}))$ we will denote the standard monomorphisms.

$i)$ By proposition \ref{NonDegenMetTopInjCharac} the morphism $\widetilde{\rho}_J: J\to\mathcal{B}(I,\ell_\infty(B_{J^*}))$ has a left inverse morphism in $\langle$~$\mathbf{mod}_1-I$ / $\mathbf{mod}-I$~$\rangle$, say $\widetilde{\tau}$ of norm $\langle$~at most $1$ / at most $C$~$\rangle$. Let $i:I\to A$ be the natural embedding, and define $I$-morphism $q=\mathcal{B}(i,\ell_\infty(B_{J^*}))$. Obviously  $\widetilde{\rho}_J=q\rho_J$. Consider $I$-morphism $\tau =\widetilde{\tau} q$. By paragraph $ii)$ of proposition \ref{MorphCoincide} it is also an $A$-morphism. Note that $\Vert\tau \Vert\leq\Vert\widetilde{\tau}\Vert\Vert q\Vert\leq\Vert\widetilde{\tau}\Vert$, so $\tau$ has norm $\langle$~at most $1$ / at most $C$~$\rangle$. Clearly, $\tau \rho_J=\widetilde{\tau} q\rho_J=\widetilde{\tau}\widetilde{\rho}_J=1_J$. Thus $\rho_J$ is a $\langle$~$1$-coretraction / $C$-coretraction~$\rangle$, so by proposition \ref{NonDegenMetTopInjCharac} the $A$-module $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective.

$ii)$ If $J$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective as $A$-module, then by proposition \ref{NonDegenMetTopInjCharac} the $A$-morphism $\rho_J$ has a left inverse in $\langle$~$\mathbf{mod}_1-A$ / $\mathbf{mod}-A$~$\rangle$, say $\tau $ of norm $\langle$~at most $1$ / at most $C$~$\rangle$. Assume we are given an operator $T\in \mathcal{B}(A,\ell_\infty(B_{J^*}))$, such that $T|_I=0$. Fix $a\in I$, then $T\cdot a=0$, and so $\tau (T)\cdot a=\tau (T\cdot a)=0$. Since $J$ is faithful $I$-module and $a\in I$ is arbitrary, then $\tau (T)=0$. By $r:A\to I$  we denote the left inverse of $i$. By assumption $\Vert r\Vert\leq c$. Define bounded linear operators $j=\mathcal{B}(r,\ell_\infty(B_{J^*}))$ and $\widetilde{\tau}=\tau  j$. For any $a\in I$ and $T\in\mathcal{B}(I,\ell_\infty(B_{J^*}))$ we have $\widetilde{\tau}(T\cdot a)-\widetilde{\tau}(T)\cdot a=\tau (j(T\cdot a)-j(T)\cdot a)=0$, because $j(T\cdot a)-j(T)\cdot a|_I=0$. Therefore $\widetilde{\tau}$ is an $I$-morphism. Note that $\Vert\widetilde{\tau}\Vert\leq\Vert\tau \Vert\Vert j\Vert$, so $\widetilde{\tau}$ has norm $\langle$~at most $1$ / at most $cC$~$\rangle$. Obviously, for all $x\in J$ we have $\rho_J(x)-j(\widetilde{\rho}_J(x))|_I=0$, so $\tau (\rho_J(x)-j(\widetilde{\rho}_J(x)))=0$. As a consequence $\widetilde{\tau}(\widetilde{\rho}_J(x))=\tau (j(\widetilde{\rho}_J(x)))=\tau (\rho_J(x))=x$ for all $x\in J$. Since $\widetilde{\tau}\widetilde{\rho}_J=1_J$, then $\widetilde{\rho}_J$ is a  $\langle$~$1$-coretraction / $cC$-coretraction~$\rangle$ in $\langle$~$\mathbf{mod}_1-I$ / $\mathbf{mod}-I$~$\rangle$, so by proposition \ref{NonDegenMetTopInjCharac} the $I$-module $J$ is $\langle$~metrically / $cC$-topologically~$\rangle$ injective.
\end{proof}


\begin{proposition}\label{MetTopFlatUnderChangeOfAlg} Let $I$ be a closed subalgebra of $A$ and $F$ be an $A$-module which is essential as $I$-module. Then

$i)$ if $I$ is a left ideal of $A$ and $F$ is $\langle$~metrically / $C$-topologically~$\rangle$  flat $I$-module, then $F$ is $\langle$~metrically / $C$-topologically~$\rangle$ flat $A$-module;

$ii)$ if $I$ is a $\langle$~$1$-complemented / $c$-complemented~$\rangle$ right ideal of $A$ and $F$ is $\langle$~metrically / $C$-topologically~$\rangle$ flat $A$-module, then $F$ is $\langle$~metrically / $cC$-topologically~$\rangle$ flat $I$-module.
\end{proposition}
\begin{proof} Note that the dual of essential module is faithful. Now the result follows from propositions $\langle$~\ref{MetTopFlatCharac} / \ref{CTopFlatCharac}~$\rangle$ and \ref{MetTopInjUnderChangeOfAlg}.
\end{proof}	

\begin{proposition}\label{MetTopProjInjFlatUnderSumOfAlg} Let $(A_\lambda)_{\lambda\in\Lambda}$ be a family of Banach algebras and for each $\lambda\in\Lambda$ let $X_\lambda$ be $\langle$~an essential / a faithful / an essential~$\rangle$ $A_\lambda$-module. Denote $A=\bigoplus_p\{A_\lambda:\lambda\in\Lambda\}$ for $1\leq p\leq +\infty$ or $p=0$. Let $X$ denote $\langle$~$\bigoplus_1\{X_\lambda:\lambda\in\Lambda\}$ / $\bigoplus_\infty\{X_\lambda:\lambda\in\Lambda\}$ / $\bigoplus_1\{X_\lambda:\lambda\in\Lambda\}$~$\rangle$. Then

$i)$ $X$ is metrically $\langle$~projective / injective / flat~$\rangle$ $A$-module iff for all $\lambda\in\Lambda$ the $A_\lambda$-module $X_\lambda$ is metrically $\langle$~projective / injective / flat~$\rangle$;

$ii)$ $X$ is $C$-topologically $\langle$~projective / injective / flat~$\rangle$ $A$-module iff for all $\lambda\in\Lambda$ the $A_\lambda$-module $X_\lambda$ is $C$-topologically $\langle$~projective / injective / flat~$\rangle$.
\end{proposition}
\begin{proof} Note that for each $\lambda\in\Lambda$ the natural embedding $i_\lambda:A_\lambda\to A$ allows to regard $A_\lambda$ as complemented in $\mathbf{Ban}_1$ two sided ideal of $A$.

$i)$ The proof is literally the same as in paragraph $ii)$.

$ii)$ Assume $X_\lambda$ is $C$-topologically $\langle$~projective / injective / flat~$\rangle$ $A_\lambda$-module for all $\lambda\in\Lambda$, then by paragraph $i)$ of proposition $\langle$~\ref{MetTopProjUnderChangeOfAlg} / \ref{MetTopInjUnderChangeOfAlg} / \ref{MetTopFlatUnderChangeOfAlg}~$\rangle$ it is $C$-topologically $\langle$~projective / injective / flat~$\rangle$ as $A$-module. It is remains to apply the proposition $\langle$~\ref{MetTopProjModCoprod} / \ref{MetTopInjModProd} / \ref{MetTopFlatModCoProd}~$\rangle$. 

Conversely, assume that $X$ is $C$-topologically $\langle$~projective / injective / flat~$\rangle$ as $A$-module. Fix arbitrary $\lambda\in\Lambda$. Clearly, we may regard $X_\lambda$ as $A$-module and even more $X_\lambda$ is a $1$-retract of $X$ in $\langle$~$A-\mathbf{mod}_1$ / $\mathbf{mod}_1-A$ / $A-\mathbf{mod}_1$~$\rangle$. By proposition $\langle$~\ref{RetrMetTopProjIsMetTopProj} / \ref{RetrMetTopInjIsMetTopInj} / \ref{RetrMetTopFlatIsMetTopFlat}~$\rangle$ we get that $X_\lambda$ is $C$-topologically $\langle$~projective / injective / flat~$\rangle$ as $A$-module. It is remains to apply paragraph $ii)$ of proposition $\langle$~\ref{MetTopProjUnderChangeOfAlg} / \ref{MetTopInjUnderChangeOfAlg} / \ref{MetTopFlatUnderChangeOfAlg}~$\rangle$.
\end{proof} 

%----------------------------------------------------------------------------------------
%	Further properties of flat modules
%----------------------------------------------------------------------------------------

\subsection{Further properties of flat modules}
\label{SubSectionFurtherPropertiesOfFlatModules}

Based on results obtained above, we collect more interesting facts on metric and topological injectivity and flatness of Banach modules.

\begin{proposition}\label{DualBanModDecomp} Let $B$ be a unital Banach algebra, $A$ be its subalgebra with two-sided bounded approximate identity $(e_\nu)_{\nu\in N}$ and $X$ be a left $B$-module. Denote $c_1=\sup_{\nu\in N}\Vert e_\nu\Vert$, $c_2=\sup_{\nu\in N}\Vert e_B-e_\nu\Vert$ and $X_{ess}=\operatorname{cl}_X(AX)$. Then 

$i)$ $X^*$ is $c_2(c_1+1)$-isomorphic as a right $A$-module to $X_{ess}^*\bigoplus_\infty (X/X_{ess})^*$;

$ii)$ $\langle$~$X_{ess}^*$ / $(X/X_{ess})^*$~$\rangle$ is a $\langle$ $c_1$-retract / $c_2$-retract~$\rangle$ of $A$-module $X^*$;

$iii)$ if $X$ is an $\mathscr{L}_{1,C}^g$-space, then $\langle$~$X_{ess}$ / $X/X_{ess}$~$\rangle$ is an $\langle$~$\mathscr{L}_{1,c_1C}^g$-space / $\mathscr{L}_{1,c_2C}^g$-space~$\rangle$.

\end{proposition}
\begin{proof} $i)$ Define the natural embedding $\rho:X_{ess}\to X:x\mapsto x$ and the quotient map  $\pi:X\to X/X_{ess}:x\mapsto x+X_{ess}$. Let $\mathfrak{F}$ be the section filter on $N$ and let $\mathfrak{U}$ be an ultrafilter dominating $\mathfrak{F}$. For a fixed $f\in X ^*$ and $x\in X $ we have $|f(x-e_\nu\cdot x)|\leq\Vert f\Vert\Vert e_B - e_\nu\Vert\Vert x\Vert\leq c_2\Vert f\Vert\Vert x\Vert$ i.e. $(f(x-e_\nu\cdot x))_{\nu\in N}$ is a bounded net of complex numbers. Therefore we have a well defined limit $\lim_{\mathfrak{U}}f(x-e_\nu\cdot x)$ along ultrafilter $\mathfrak{U}$. Since $(e_\nu)_{\nu\in N}$ is a two-sided approximate identity for $A$ and $\mathfrak{U}$ contains section filter then for all $x\in X_{ess}$ we have $\lim_{\mathfrak{U}}f(x-e_\nu\cdot x)=\lim_{\nu}f(x-e_\nu\cdot x)=0$. Therefore for each $f\in X ^*$ we have a well defined map $\tau(f):X /X_{ess}\to \mathbb{C}:x+X_{ess}\mapsto \lim_{\mathfrak{U}} f(x-e_\nu\cdot x)$. Clearly this is a linear functional, and from inequalities above we see its norm is bounded by $c_2\Vert f\Vert$. Now it is routine to check that $\tau:X^*\to (X/ X_{ess})^*:f\mapsto \tau(f)$ is an $A$-morphism with norm not greater than $c_2$. Similarly, one can show that $\sigma:X_{ess}^*\to X^*:h\mapsto(x\mapsto \lim_{\mathfrak{U}}h(e_\nu\cdot x))$ is an $A$-morphism with norm not greater than $c_1$. For any $f\in X^*$, $g\in (X/X_{ess})^*$, $h\in X_{ess}^*$ and $x\in X$, $y\in X_{ess}$ we have
$$
\sigma(h)(y)
=\lim_{\mathfrak{U}}h(e_\nu\cdot y)
=\lim_{\nu}h(e_\nu\cdot y)
=h(y),
\qquad
(\rho^*\sigma)(h)(y)
=\sigma(h)(\rho(y))
\sigma(h)(y)
=h(y),
$$
$$
(\tau\pi^*)(g)(x+X_{ess})
=\lim_{\mathfrak{U}}\pi^*(g)(x-e_\nu\cdot x)
=\lim_{\mathfrak{U}}g(x+X_{ess})
=g(x+X_{ess}),
$$
$$
(\tau\sigma)(h)(x+X_{ess})
=\lim_{\mathfrak{U}}\sigma(h)(x-e_\nu\cdot x)
=\lim_{\mathfrak{U}}(\sigma(h)(x)-h(e_\nu\cdot x))
=\sigma(h)(x)-\lim_{\mathfrak{U}}h(e_\nu\cdot x)=0,
$$
$$
(\pi^*\tau + \sigma\rho^*)(f)(x)
=\tau(f)(x+X_{ess})+\lim_{\mathfrak{U}}\rho^*(f)(e_\nu\cdot x)
=\lim_{\mathfrak{U}}f(x - e_\nu\cdot x)+\lim_{\mathfrak{U}}f(e_\nu\cdot x)
=f(x).
$$
Therefore $\tau \pi^*=1_{(X/X_{ess})^*}$, $\rho^*\sigma=1_{X_{ess}^*}$ and  $\pi^*\tau+\sigma\rho^*=1_{X^*}$. Now it is easy to check that the linear maps
$$
\xi:X^*\to X_{ess}^*\bigoplus{}_\infty (X/X_{ess})^*:f\mapsto \rho^*(f)\bigoplus{}_\infty \tau(f)
$$
$$
\eta:X_{ess}^*\bigoplus{}_\infty (X/X_{ess})^*\to X^*:h\bigoplus{}_\infty g\mapsto \pi^*(h)+\sigma(g)
$$
are isomorphism of right $A$-modules with $\Vert\xi \Vert\leq c_2$ and $\Vert \eta\Vert\leq c_1+1$. Hence $X^*$ is $c_2(c_1+1)$-isomorphic in $\mathbf{mod}-A$ to $X_{ess}^*\bigoplus_\infty (X/X_{ess})^*$.

$ii)$ Both results immediately follow from equalities $\rho^*\sigma=1_{X_{ess}^*}$, $\tau \pi^*=1_{(X/X_{ess})^*}$ and estimates $\Vert \rho^*\Vert\Vert \sigma\Vert\leq c_1$, $\Vert\tau\Vert\Vert \pi^*\Vert\leq c_2$.

$iii)$ Now consider case when $X$ is an $\mathscr{L}_{1,C}^g$-space. Then $X^*$ is an $\mathscr{L}_{\infty,C}^g$-space [\cite{DefFloTensNorOpId}, corollary 23.2.1(1)]. As $\langle$~$X_{ess}^*$ / $(X/X_{ess})^*$~$\rangle$ is $\langle$~$c_1$-complemented / $c_2$-complemented~$\rangle$ in $X^*$ it is an $\langle$~$\mathscr{L}_{\infty,c_1C}^g$-space / $\mathscr{L}_{\infty,c_2C}^g$-space~$\rangle$ by [\cite{DefFloTensNorOpId}, corollary 23.2.1(1)]. Again we apply [\cite{DefFloTensNorOpId}, corollary 23.2.1(1)] to conclude that $\langle$~$X_{ess}$  / $X/X_{ess}$~$\rangle$ is an $\langle$~$\mathscr{L}_{1,c_1C}^g$-space / $\mathscr{L}_{1,c_2C}^g$-space~$\rangle$.
\end{proof}

The following proposition is an analog of [\cite{RamsHomPropSemgroupAlg}, proposition 2.1.11].

\begin{proposition}\label{TopFlatModCharac} Let $A$ be a Banach algebra with two-sided $c$-bounded approximate identity, and $F$ be a left $A$-module. Then

$i)$ if $F$ is $C$-topologically flat $A$-module, then $F_{ess}$ is $(1+c)C$-topologically flat $A$-module and $F/F_{ess}$ is an $\mathscr{L}_{1,(1+c)C}^g$-space;

$ii)$ if $F_{ess}$ is $C_1$-topologically flat $A$-module and $F/F_{ess}$ is an $\mathscr{L}_{1,C_1}^g$-space, then $F$ is $(1+c)^2\max(C_1, C_2)$-topologically flat $A$-module.

$iii)$ $F$ is topologically flat $A$-module iff $F_{ess}$  is topologically flat $A$-module and $F/F_{ess}$ is an $\mathscr{L}_1^g$-space.
\end{proposition}
\begin{proof} We regard $A$ as closed subalgebra of unital Banach algebra $B:=A_+$. Then $F$ is unital left $B$-module. Using notation of proposition \ref{DualBanModDecomp} we may say that $c_1=c$ and $c_2=1+c$, so the right $A$-modules $F_{ess}^*$ and $(F/F_{ess})^*$ are $(1+c)$-retracts of $F^*$.

$i)$ By proposition \ref{CTopFlatCharac} the right $A$-module $F^*$ is $C$-topologically injective. Therefore from propositions \ref{RetrCTopInjIsCTopInj}, \ref{CTopFlatCharac} the modules $F_{ess}$ and $F/F_{ess}$ are $(1+c)C$-topologically flat. It remains to note that $F/F_{ess}$ is an annihilator $A$-module, so by proposition \ref{MetTopFlatAnnihModCharac} it is an $\mathscr{L}_{1,(1+c)C}^g$-space.

$ii)$ Again, by proposition \ref{CTopFlatCharac} the right $A$-modules $F_{ess}^*$ and $(F/F_{ess})^*$ are $C_1$- and $C_2$-topologically injective respectively. So from proposition \ref{MetTopInjModProd} their product is $\max(C_1,C_2)$-topologically injective. By proposition \ref{DualBanModDecomp} this product is $(1+c)^2$-isomorphic to $F^*$ in $\mathbf{mod}-A$. Therefore $F^*$ is $(1+c)^2\max(C_1, C_2)$-topologically injective $A$-module. Now the result follows from proposition \ref{CTopFlatCharac}.

$iii)$ The result immediately follows from paragraphs $i)$ and $ii)$.
\end{proof}

\begin{proposition}\label{MetTopEssL1FlatModAoverAmenBanAlg} Let $A$ be a relatively $\langle$~$1$-amenable / $c$-amenable~$\rangle$ Banach algebra and $F$ be an essential Banach $A$-module which is an $\langle$~$L_1$-space / $\mathscr{L}_{1,C}^g$-space~$\rangle$. Then $F$ is a $\langle$~metrically / $c^2C$-topologically~$\rangle$ flat $A$-module.
\end{proposition}
\begin{proof} We may assume that $A$ is relatively $c$-amenable for $\langle$~$c=1$ / $c\geq 1$~$\rangle$. Let $(d_\nu)_{\nu\in N}$ be an approximate diagonal for $A$ with norm bound at most $c$. Recall, that $(\Pi_A(d_\nu))_{\nu\in N}$ is a two-sided $\langle$~contractive / bounded~$\rangle$ approximate identity for $A$. Since $F$ is essential left $A$-module, then $\lim_{\nu}\Pi_A(d_\nu)\cdot x=x$ for all $x\in F$ [\cite{HelHomolBanTopAlg}, proposition 0.3.15]. As the consequence $c\pi_F(B_{A\projtens\ell_1(B_F)})$ is dense in $B_F$. Then for all $f\in F^*$ we have
$$
\Vert\pi_F^*(f)\Vert
=\sup\{|f(\pi_F(u))|:u\in B_{A\projtens\ell_1(B_F)}\}
=\sup\{|f(x)|:x\in \operatorname{cl}_F(\pi_F(B_{A\projtens\ell_1(B_F)}))\}
$$
$$
\geq\sup\{c^{-1}|f(x)|:x\in B_F\}=c^{-1}\Vert f\Vert
$$
This means, that $\pi_F^*$ is $c$-topologically injective. By assumption $F$ is an $\langle$~$L_1$-space / $\mathscr{L}_{1,C}^g$-space~$\rangle$, then by $\langle$~[\cite{GrothMetrProjFlatBanSp}, theorem 1] / remark after [\cite{DefFloTensNorOpId}, corollary 23.5(1)]~$\rangle$ the Banach space $F^*$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective. Since operator $\pi_F^*$ is $\langle$~isometric / $c$-topologically injective~$\rangle$, then there exists a linear operator $R:(A\projtens\ell_1(B_F))^*\to F^*$ of norm $\langle$~at most $1$ / at most $cC$~$\rangle$ such that $R\pi_F^*=1_{F^*}$.

Fix $h\in (A\projtens\ell_1(B_F))^*$ and $x\in F$. Consider bilinear functional $M_{h,x}:A\times A\to\mathbb{C}:(a,b)\mapsto R(h\cdot a)(b\cdot x)$. Clearly, $\Vert M_{h,x}\Vert\leq\Vert R\Vert\Vert h\Vert\Vert x\Vert$. By universal property of projective tensor product we have a bounded linear functional $m_{h,x}:A\projtens A\to\mathbb{C}:a\projtens b\mapsto R(h\cdot a)(b\cdot x)$. Note that $m_{h,x}$ is linear in $h$ and $x$. Even more, for any $u\in A\projtens A$, $a\in A$ and $f\in F^*$ we have $m_{\pi_F^*(f),x}(u)=f(\Pi_A(u)\cdot x)$, $m_{h\cdot a,x}(u)=m_{h,x}(a\cdot u)$, $m_{h,a\cdot x}(u)=m_{h,x}(u\cdot a)$. It easily checked for elementary tensors. Then it is enough to recall that their linear span is dense in $A\projtens A$.

Let $\mathfrak{F}$ be the section filter on $N$ and let $\mathfrak{U}$ be an ultrafilter dominating $\mathfrak{F}$. For any $h\in (A\projtens\ell_1(B_F))^*$ and $x\in F$ we have $|m_{h,x}(d_\nu)|\leq c\Vert R\Vert\Vert h\Vert\Vert x\Vert$, i.e. $(m_{h,x}(d_\nu))_{\nu\in N}$ is a bounded net of complex numbers. Therefore we have a well defined limit $\lim_{\mathfrak{U}}m_{h,x}(d_\nu)$ along ultrafilter $\mathfrak{U}$. Consider linear operator $\tau:(A\projtens\ell_1(B_F))^*\to F^*:h\mapsto(x\mapsto\lim_{\mathfrak{U}}m_{h,x}(d_\nu))$. From norm estimates for $m_{h,x}$ it follows that $\tau$ is bounded with $\Vert\tau\Vert\leq c\Vert R\Vert$. For all $a\in A$, $x\in F$ and $h\in (A\projtens\ell_1(B_F))^*$ we have
$$
\tau(h\cdot a)(x)-(\tau(h)\cdot a)(x)
=\tau(h\cdot a)(x)-\tau(h)(a\cdot x)
=\lim_{\mathfrak{U}}m_{h\cdot a,x}(d_\nu)-\lim_{\mathfrak{U}}m_{h,a\cdot x}(d_\nu).
$$
$$
=\lim_{\mathfrak{U}}m_{h,x}(a\cdot d_\nu)-m_{h,x}(d_\nu\cdot a)
=m_{h,x}\left(\lim_{\mathfrak{U}}(a\cdot d_\nu-d_\nu\cdot a)\right)
$$
$$
=m_{h,x}\left(\lim_{\nu}(a\cdot d_\nu-d_\nu\cdot a)\right)
=m_{h,x}(0)
=0.
$$
Therefore $\tau$ is a morphism of right $A$-modules. Now for all $f\in F^*$ and $x\in F$ we have
$$
(\tau(\pi_F^*)(f))(x)
=\lim_{\mathfrak{U}}m_{\pi_F^*(f),x}(d_\nu)
=\lim_{\mathfrak{U}}f(\Pi_A(d_\nu)\cdot x)
=\lim_{\nu}f(\Pi_A(d_\nu)\cdot x)
$$
$$
=f\left(\lim_{\nu}\Pi_A(d_\nu)\cdot x\right)
=f(x).
$$
So $\tau\pi_F^*=1_{F^*}$. This means that $F^*$ is a $\langle$~$1$-retract / $c^2 C$-retract~$\rangle$ of $(A\projtens\ell_1(B_F))^*$
 in $\langle$~$\mathbf{mod}_1-A$ / $\mathbf{mod}-A$~$\rangle$. The latter $A$-module is $\langle$~metrically / topologically~$\rangle$ injective, because $(A_+\projtens\ell_1(B_F))^*\isom{\mathbf{mod}_1-A}\mathcal{B}(A_+,\ell_\infty(B_F))$ and by proposition $\langle$~\ref{RetrMetTopInjIsMetTopInj} / \ref{RetrCTopInjIsCTopInj}~$\rangle$ so does its retract $F^*$. By proposition $\langle$~\ref{MetTopFlatCharac} / \ref{CTopFlatCharac}~$\rangle$ this is equivalent to $\langle$~metric / $c^2 C$-topological~$\rangle$ flatness of $F$.
\end{proof}

\begin{theorem}\label{TopL1FlatModAoverAmenBanAlg} Let $A$ be a relatively $c$-amenable Banach algebra and $F$ be a left Banach $A$-module which as Banach space is an $\mathscr{L}_{1, C}^g$-space. Then $F$ is a $(1+c)^2C\max(c^2,(1+c))$-topologically flat $A$-module.
\end{theorem}
\begin{proof} Since $A$ is amenable it admits a two-sided $c$-bounded approximate identity. By proposition \ref{DualBanModDecomp} the annihilator $A$-module $F/F_{ess}$ is an $\mathscr{L}_{1,1+c}^g$-space. From proposition \ref{MetTopEssL1FlatModAoverAmenBanAlg} we get that the essential $A$-module $F_{ess}$ is $c^2 C$-topologically flat. Now the result follows from proposition \ref{TopFlatModCharac}.
\end{proof}

We must point out here that in relative Banach homology any left Banach module over relatively amenable Banach algebra is relatively flat [\cite{HelBanLocConvAlg}, theorem 7.1.60]. Even topological theory is so restrictive that in some cases, as the following proposition shows, we can obtain complete characterization of all flat modules.

\begin{proposition}\label{TopFlatModAoverAmenL1BanAlgCharac} Let $A$ be a relatively amenable Banach algebra which as Banach space is an $\mathscr{L}_1^g$-space. Then for a Banach $A$-module $F$ the following are equivalent:

$i)$ $F$ is topologically flat $A$-module; 

$ii)$ $F$ is an $\mathscr{L}_1^g$-space.
\end{proposition}
\begin{proof} The equivalence follows from proposition \ref{TopProjInjFlatModOverMthscrL1SpCharac} and theorem \ref{TopL1FlatModAoverAmenBanAlg}.
\end{proof}

Finally we are able to give an example of relatively flat, but not topologically flat ideal in a Banach algebra. Consider $A=L_1(\mathbb{T})$. It is known, that $A$ has a translation invariant infinite dimensional closed subspace $I$ isomorphic to a Hilbert space [\cite{RosProjTransInvSbspLpG}, p.52]. By [\cite{KaniBanAlg}, proposition 1.4.7] we have that $I$ is a two-sided ideal of $A$, as any translation invariant subspace of $A$. By [\cite{DefFloTensNorOpId}, section 23.3] this ideal is not an $\mathscr{L}_1^g$-space. So from proposition \ref{TopFlatModAoverAmenL1BanAlgCharac} we get that $I$ is not topologically flat as $A$-module. We claim it is still relatively flat. Since $\mathbb{T}$ is a compact group, then it is amenable [\cite{PierAmenLCA}, proposition 3.12.1]. Thus $A$ is relatively amenable [\cite{HelBanLocConvAlg}, proposition VII.1.86], so all left ideals of $A$ are relatively flat [\cite{HelBanLocConvAlg}, proposition VII.1.60(I)]. In particular, $I$ is relatively flat.

%----------------------------------------------------------------------------------------
%	Injectivity of ideals
%----------------------------------------------------------------------------------------

\subsection{Injectivity of ideals}
\label{SubSectionInjectivityOfIdeals}

Injective ideals are rare creatures but we need to say a few words about them. Results of this section needed for the study of metric and topological injectivity of $C^*$-algebras.

\begin{proposition}\label{MetTopInjOfId} Let $I$ be a right ideal of a Banach algebra $A$. Assume $I$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective $A$-module. Then $I$ has a left identity of norm $\langle$~at most $1$ / at most $C$~$\rangle$ and is a $\langle$~$1$-retract / $C$-retract~$\rangle$ of $A$ in $\mathbf{mod}-A$.
\end{proposition}
\begin{proof} Consider isometric embedding $\rho^+:I\to A_+$ of $I$ into $A_+$. Clearly, this is an $A$-morphism. Since $I$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective, then $\rho^+$ has left inverse $A$-morphism $\tau^+:A_+\to I$ with norm $\langle$~at most $1$ / at most $C$~$\rangle$. Now for all $x\in I$ we have $x=\tau^+(\rho^+(x))=\tau^+(e_{A_+}\rho^+(x))=\tau(e_{A_+})\rho^+(x)=\tau^+(e_{A_+})x$. In other words $p=\tau^+(e_{A_+})\in I$ is a left unit for $I$. Clearly, $\Vert p\Vert\leq\Vert\tau^+\Vert\Vert e_{A_+}\Vert\leq\Vert\tau^+\Vert$. Consider maps $\rho:I\to A:x\mapsto x$ and $\tau:A\to I:x\mapsto p x$. Clearly, they are morphisms of right $A$-modules and $\tau\rho=1_I$. Hence $I$ is a $\langle$~$1$-retract / $C$-retract~$\rangle$ of $A$ in $\mathbf{mod}-A$.
\end{proof}

\begin{proposition}\label{ReduceInjIdToInjAlg} Let $I$ be a two-sided ideal of Banach algebra $A$, which is faithful as right $I$-module. Then

$i)$ if $I$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective $I$-module, then $I$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective $A$-module; 

$ii)$ if $I$ is $\langle$~metrically / $C$-topologically~$\rangle$ injective $A$-module, then $I$ is $\langle$~metrically / $C^2$-topologically~$\rangle$ injective $I$-module.
\end{proposition}
\begin{proof} $i)$ The result immediately follows from paragraph $i)$ of proposition \ref{MetTopInjUnderChangeOfAlg}.

$ii)$ By proposition \ref{MetTopInjOfId} the $A$-module $I$ is $\langle$~$1$-complemented / $C$-complemented~$\rangle$ in $A$. By paragraph $ii)$ of proposition \ref{MetTopInjUnderChangeOfAlg} the $I$-module $I$ is $\langle$~metrically / $C^2$-topologically~$\rangle$ injective.
\end{proof}
